### 2015-07-07 abstract.tex
initial commit of soro paper on automous grasping

This paper presents the development of an autonomous motion planning algorithm for a soft planar grasping manipulator capable of grasp-and-place operations by encapsulation.
The gripping end of the soft manipulator is fabricated without weakening seams using lost-wax casting instead of the commonly used multi-layer lamination process.
The soft manipulation system can grasp randomly positioned objects within its reachable envelope and move them to a desired location without human intervention.
The autonomous planning system leverages the compliance and continuum bending of the soft grasping manipulator to achieve repeatable grasps in the presence of uncertainty.
Modeling uncertainties arise from a simplifying constant-curvature assumption, unrepresented manipulator dynamics, stick-slip friction, and  non-linear fluidic control. 
These uncertainties are compensated by the inherent compliance of the soft gripper design and the motion planning strategy.
Additionally, when fully actuated, the manipulator remains compliant allowing it to conform to un-modeled object geometries.
A suite of experiments is presented that demonstrates the system's capabilities.

### 2015-07-07 conclusion.tex
initial commit of soro paper on automous grasping

\section{Conclusion}
\label{sec:conclusion}
This work introduced a new manufacturing approach for a soft manipulator and demonstrated its capabilities through autonomously grasping-and-placing a randomly positioned object.
To produce the complete soft manipulator used, an entirely soft gripper was designed and fabricated and then combined with a previously developed soft robotic arm.
It was then shown that a minimal strain and collision-free approach to an object of interest can be achieved by posing the grasp motion plan as a series of constrained nonlinear optimization problems.

The fabrication approach presented has potential to generalize beyond just the fabrication of a gripper.
The new approach is advantageous because it allows for arbitrary designs of internal fluidic cavities and the casting of a homogeneous soft segment. It removes the need for laminating several separately casted parts together.
Such a homogeneous soft segment is less prone to rupture and to manufacturing inconsistencies, and would therefore allow for better robot performance.

The results presented in this paper suggest that despite their extreme compliance, soft robots are capable of repeatable object manipulation while simultaneously providing inherently safe interactions with their environment.
\rkk{The manipulator is suitable to perform delicate tasks with low payloads, for example grasping objects that should not be squeezed and/or should not break during manipulation.}
We demonstrated the ability of an entirely soft manipulator to autonomously grasp an object, which leads to many potential applications.
In a manufacturing setting, this could resemble a soft robot executing tasks requiring high dexterity when handling delicate objects.
In a human-centric environment, soft arm grasping manipulation may enable soft robots to interact safely with humans.
Furthermore, in a surgical setting, highly compliant soft robots with grippers may assist with operations in sensitive environments \rkk{during tasks where no high level of precision is required.}

### 2015-07-07 experimental_results.tex
initial commit of soro paper on automous grasping

\section{Experimental Results}
\label{sec:experimental_results}
\subsection{\rkk{Grasping Delicate Objects}}
\rkk{The soft manipulator can pick up hollowed-out eggs and other delicate objects without breaking them. 
Figure~\ref{fig:egg_approach_sequence} shows how the manipulator approaches and grasps an egg.
Delicate objects can be manipulated without requiring a shape or a force sensor within its structure, since the compliant gripper body conforms to the object.
Rigid-bodied grippers usually rely on force sensing or another type of sensory feedback to avoid damage caused to the object.}

%\subsection{\rkk{Allowable Grasping Uncertainty}}
%
%\rkk{We experimentally characterized the allowable grasping region of the soft gripper to show that despite positioning inaccuracies, the gripper can still successfully perform a grasp of an object. 
%The evaluation of this allowable grasping region is performed similarly to a method described in Dogar and Srinivasa\cite{dogar2010push} work on determining capture regions for a push-grasp of a classical robotic gripper.}
%

\subsection{\rkk{Repeated Grasp Experiments}}
We performed 25 experimental grasp-and-place trials at various positions to demonstrate the capabilities and repeatability of our system.
The results of all the trials are shown in Figure~\ref{fig:allTestsOverlaid}.
One representative approach, grasp, and retract move is shown in Figure~\ref{fig:oneTrialVsTime}.
In 23 of 25 experimental trials, the manipulator successfully achieved the task of grasping an object and bringing it to a bin \rkk{location shown in red}.
The object was placed five times on each of the five points marked on the board.
\rkk{The markers only serve as a reference point for the user to place the object roughly at the same point at every repetition.
The user's placing accuracy is not important to the algorithm, the tracking system newly registers every single time the position of the placed object.}
The five points were chosen to approximately represent the major portion of the manipulator's reachable workspace.
\rkk{As long as the root of the gripper stops so that the object is located within the capture region, the gripper will pick it up through its sweeping closing motion. The capture region is shown in grey in Figure~\ref{fig:grasp_uncertainty}.
\begin{figure}[htb]
\centering
   \includegraphics[width=0.8\columnwidth]{Figures/experimental_results/uncertainty}
   \caption{\rkk{Experimental characterization of the gripper's capture region: the allowable positioning uncertainty is determined through repeated placements of the center of a cylindrical object at different points on a grid relative to the gripper. Blue dots indicate all object center positions for which a grasp could be performed successfully, red crosses show the positions where a grasp failed. The grey line outlines an area for the object to be positioned within so the gripper can grasp it. The evaluation of the capture region was performed similarly to a method described in \cite{dogar2010push}.}}
   \label{fig:grasp_uncertainty}
\end{figure} 
When the arm reaches the red bin location, it drops the object.}

\begin{figure*}[htbp]
\begin{centering}
  \includegraphics[width=0.5\textwidth]{Figures/experimental_results/allTestsOverlaid.eps}
\includegraphics[width=0.385\textwidth]{figures/experimental_results/five_grasps.jpg}
\caption[Left: All 25 experimental grasping trials.]{Complete set of experimental grasp-and-place trials. In these experiments, the arm moves from an initial straightened configuration to grasp a round object placed in one of five locations (A-E). The arm then returns the object to a bin location shown in red. For each trial, a seven degrees of freedom manipulator representation is generated at both the \emph{grasped} and \emph{released} state using experimental data and is shown in blue. The corresponding 1 degree-of-freedom end-effector representation is shown in black. The round object's measured position at each state is shown in green. Right: Overlaid photographs of the manipulator grasping an object placed at each of the five locations. }\label{fig:allTestsOverlaid}
\end{centering}
\end{figure*}

\rkk{The unsuccessful trials happened due to stick-slip friction between the roller bearings and the table surface.
Our kinematic modeling does not account for this non-linear behavior, which acts as a disturbance and can lead to failure to arrive at the next waypoint.
To be more specific, in one of the trials, the robot slowed down too much before it almost reached its next waypoint and because of friction the arm got to a full stop. 
The proportional gain of the curvature controller was not able to compensate for that small positional delta and since the relatively low saturation level of the integrator portion of the controller was saturated, the arm did not move to the next waypoint pose. 
It is to note, that the saturation level for the integrator is defined by a safety limit on the maximal inflation of the robotic arm.
In the other unsuccesful trial, the stick-slip friction also caused the arm to halt before a waypoint. The controller built up enough forcing due to inflation, so that the arm slipped over the close waypoint without having all of its single arm segment curvature within an acceptable epsilon.
The controller then tried to swing back to fulfill the missed waypoint, missed it again and that finally caused the whole arm to oscillate back-and-forth and eventually push the object off the table.
In one of the other trials, the grasp and return was successfully performed, but a small overshoot over the final bin location at the end of the return caused the arm to drop off the table, which could have been avoided if the table would have not been too small towards the right.
This outlier is shown in Figure~\ref{fig:allTestsOverlaid}.
Overall, the experiments show that the system was repeatably able to autonomously locate a randomly placed object within its workspace, plan the arm motions, and perform the task of grasping and placing the object.}

\subsection{\rkk{Experimental Insights and Limitations}}
The system can drag payloads of less than 40\unit{g}, higher payloads cause the cylindrical arm segments to stall and possibly lift off the table without moving the payload.
There is a trade-off between the reachable workspace and the maximum payload.
As the length of the arm increases, more workspace can be reached while less payload can be manipulated. 
Most of the payload capability is already used up by the attached gripper itself.
A smaller gripper would allow for larger payloads to get picked up, but consequently only smaller objects can be grasped.
The workspace of the manipulator is limited to the top and left by the maximal extension length of the arm, and to the bottom by the maximum bending curvature, which the arm can achieve without over-actuating a single segment.
Objects were only grasped within the left quadrant of the arm, because of the gripper orientation and an upright initial starting pose.

\begin{figure*}[htbp]
\begin{centering}
  \includegraphics[width=0.375\textwidth]{Figures/experimental_results/oneTrialVsTime.eps}
\includegraphics[width=0.30\textwidth]{figures/experimental_results/exp5a-4_sweep_to_object.jpg}
\includegraphics[width=0.31\textwidth]{figures/experimental_results/exp5a-4_sweep_to_bin.jpg}
  \caption{Left: A time series representation of an experimental grasp-and-place trial for an object located at point E. Here, the locally optimal planned manipulator configurations as well as planned sequential approach circles are shown as black dotted curves. The arm and gripper are shown in their experimentally determined configuration representations at 1 second intervals. The cyan configurations represent the manipulator prior to grasping the object, that is moving from its initial configuration to the object's location. The magenta configurations represent the manipulator after grasping the object, that is moving from the object's location back to the bin location shown in red. Right: A photograph of the arm moving from its initial pose to the object and from the object to the release location, respectively. }
\label{fig:oneTrialVsTime}
\end{centering}
\end{figure*}

### 2015-07-07 introduction.tex
initial commit of soro paper on automous grasping

\section{Introduction}

%High Level Vision
\rkk{
Soft robots exhibit continuum body motion, large scale deformation, high compliance and adjustable impedance  compared to traditional rigid-bodied robots with high impedance \cite{trivedi2008soft}. 
% whereas humans and animals have extremities with variable impedance.
%Soft robots won't necessarily replace existing rigid robot technologies, but complement it, because they can enable static and dynamic manipulations systems in nature are capable of.
%A further motivating factor for this work is that soft robots are inherently safer for interaction with humans and the environment due to their structural compliance and they can be lighter, one of the reasons why we research on that path.
%Fluidic robots have uses in scenarios where a classical robot would cause sparks and are dangerous. Why do we need accuracy if we have compliance. A 3DOF gripper is inherently not soft. A rigid gripper can not manipulate delicate objects without a lot of sensing.
}
Such characteristics make this class of robots well-suited for highly dexterous tasks and interactions that require conformation to environmental uncertainty.

Our goal is to develop a soft planar fluid-powered gripper and a motion planning algorithm that leverages a soft morphology to robustly grasp, drag and place objects. 
%By utilizing softness in the design of our robot, we gain the ability to adapt to environmental variation \cite{mcmahan2006field}, harmlessly collide with the environment \cite{marchese2014whole}, and build resilience to unexpected external loads \cite{tolley2014resilient};

\begin{figure}[htb]
\centering
   \includegraphics[width=0.9\columnwidth]{Figures/experimental_results/egg_approach/egg_approach_sequence}
   \caption{\rkk{The soft manipulator is grasping a hollowed-out egg. The robot repeatably approached, grasped and moved this delicate object without breaking it.}}
   \label{fig:egg_approach_sequence}
\end{figure}

%Challenges 
Our manipulator is highly compliant and its motion is not as precise as more traditional rigid-bodied robots. 
The control of its configuration is not only limited by the compliance of its low-pressure actuation, but also by its inherent elasticity.
%Additionally, the manipulator's compliant nature complicates the process of determining and sensing the forward kinematics.
Despite the constraints on accurate positioning introduced by the softness of the arm, we can still robustly execute autonomous grasping tasks.

%\begin{figure}[htp]
%   \centering
%   \includegraphics[width=0.7\columnwidth]{Figures/introduction/ExperimentalSetup}
%   \caption{A soft robotic arm with gripper autonomously approaching and grasping an object on a plane.}
%   \label{fig:intro}
%\end{figure}

%Our Approach
%To address these challenges, 
%\rkk{We developed planning and control algorithms for a soft robotic arm with gripper.}
\rkk{
The fluid-powered gripper at the end of the arm can grasp an object through an open-loop controlled bending motion, even if the gripper is positioned relatively inaccurately in relation to the object to be grasped.
%The gripper can conform due to his compliance to variations in object geometry, allowing it to successfully grasp.
}
The design of the gripper itself is inspired by work of Polygerinos et al.~\cite{polygerinos2013towards}
The design is advantageous for grasping, because it exhibits high curvature, minimal radial expansion, and remains compliant during actuation. 
We can repeatably fabricate the gripper using a lost-wax casting process instead of the commonly used soft lithography technique, a multi-layer lamination process.
Without weakening seams, the gripper is not prone to de-lamination under high deformations. 
By abandoning the need for a lamination process, arbitrary shaped internal channels can be achieved. 
The gripper was used as a manually actuated single finger with a bend sensor as part of a 3-fingered-hand in \cite{homberg2015haptic}.

We attach the gripper to a multi-segment soft manipulator to enable autonomous grasp-and-place capabilities on a plane. 
Positional feedback is provided in real-time from a camera system.
%and actuation of the gripper and manipulator is driven by an external fluidic cylinder array.
We present a planning algorithm that advances the arm through all necessary states of the grasp-and-place operation.
A minimal strain, collision-free approach to the object of interest is found by posing the plan as a series of constrained nonlinear optimization problems.
The system first plans concentric approach circles shrinking from the initial end-effector pose down to the object diameter.
Next, the system searches for locally optimal manipulator configurations that constrain the end-effector to lie on these approach circles, so that the manipulator does not collide with the object. 
The manipulator is then moved between these plans using closed-loop trajectories. 
After successfully approaching the object, the gripper encapsulates it.
We experimentally validate the system's ability to repeatably and autonomously grasp-and-place a randomly placed object.

\subsection{Related Work}
There are several examples of soft grippers described in recent literature, \rkk{we will mainly focus on fluidic-based systems.} 
Deimel and Brock \cite{deimel2013compliant} developed a pneumatically actuated three-fingered hand made of reinforced silicone that is mounted to a hard robot and capable of grasping.
More recently, they have developed an anthropomorphic soft pneumatic hand capable of dexterous grasps, which is not mounted to a robot, but instead just held by a human\cite{deimel2014novel}. 
Ilievski et al. \cite{ilievski2011soft} create \rkk{through a soft-lithography fabrication} a pneumatic starfish-like gripper composed of \rkk{an array of silicone chambers and a PDMS membrane.} 
\rkk{
The gripper is hanging on a string and grasps objects like an egg or a mouse in an open-loop controlled manner.
} 
Stokes et al. \cite{Stokes2014hybrid} use a soft elastomer quadrupedal robot to grasp objects in a hard-soft hybrid robotic platform. 
A puncture resistant soft pneumatic gripper is developed by Shepherd et al. in \cite{shepherd2013soft}. 
An alternative to positive pressure actuated soft grippers is a robotic gripper that makes use of granular material jamming developed by Brown et al. and detailed in \cite{brown2010universal}.
\rkk{The soft octopus-inspired arms developed in \cite{calisti2010study} and \cite{calisti2011octopus} are not fluidic powered, but instead use cables to pull rigid fixtures embedded within an elastomer body. 
The arms were capable of grasping objects like pens or screws.}
A soft robotic tentacle developed in \cite{martinez2013robotic} was able to hold a flower and a horseshoe-shaped object.
The closest related soft pneumatic actuator design to our current work is the fast Pneu-net designs by Mosadegh et al. detailed in \cite{mosadegh2014pneumatic} and by Polygerinos et al. detailed in \cite{polygerinos2013towards}.
These finger-like actuators deform with minimal volume change and can bend to high curvatures.
\rkk{None of the above described grippers were controlled autonomously to perform their tasks and accordingly no statement on repeatability of the autonomous execution was given.}

\rkk{Cho et al. \cite{cho2009review} review several manufacturing processes for soft biomimetic robots. 
The vast majority of soft elastomer robots rely on the processes of soft lithography \cite{xia1998soft} and/or shape deposition manufacturing \cite{cham2002fast}. 
Especially noteworthy is the use of lost-wax fabrication for jammable skin chambers, which get vacuumed to stiffen up \cite{steltz2009soft}. 
The gripper presented here also uses a lost-wax molding technique, but with a different type of actuation in mind: the obtained cavity structures are inflated to cause the gripper to bend.}

%More generally, the literature has several examples of soft pneumatic elastomer robots. 
%Many of these robots use open-loop controllers. 
%There are soft fluid-powered rolling robots \cite{correll2010soft, onal2011soft, marchese2011soft}. 
%Also, there are soft-bodied robotic fish powered by pneumatics \cite{marchese2014autonomous} and hydraulics \cite{katzschmann2014hydraulic}. 
%There are soft legged pneumatic walkers \cite{shepherd2011multigait, tolley2014resilient}, explosive jumpers \cite{shepherd2013using}, and 
More recently, Marchese et al. demonstrated closed-loop position control of multi-segment soft planar fluidic elastomer manipulators in free space \cite{marchese2014design} and in confined spaces \cite{marchese2014whole}. Positioning is achieved using forward and inverse kinematic models and real-time camera measurements. 
The manipulator curvatures are controlled in real-time using a curvature-volume cascaded control law.
\rkk{The work presented in this paper builds on top of this system and expands its capabilities.
The previous version was only suitable for contactless motions in space, that would be suitable for mere inspection.
The work presented here is capable of autonomous object manipulation on a plane. 
Furthermore, this work shows that combining two different soft actuator types can leverage the strength of each and together achieve a more complicated task of manipulating objects.
The control of the arm is improved from the previous version by using a more robust vision tracking approach. 
Previously, there were only single markers along the arm, which worked for a limited motion range, but was prone to fail if the markers go out of sight or another object is introduced to the environment. 
Also, many trial runs were needed to arrive at the various final positions in the maze.
%, so the previous system was no repeatable and robust. 
}

\subsection{Contributions}
This work differs from the previous work in that we %create an entirely soft and autonomously controlled \emph{grasping} manipulation system. 
do not attach a novel soft gripper to a hard arm nor do we move the gripper around manually, but we rather take on the challenge of grasping-and-placing objects with a seven degrees of freedom planar arm made entirely from soft rubber. 
We provide in this work the following contribution to soft robotics:
\begin{itemize}
  \item \rkk{A soft manipulator consisting of a multi-segment arm with a gripper to enable fully compliant planar grasping.}
  \item \rkk{A planning algorithm to grasp-and-place randomly positioned objects on a planar surface using a 7 DOF soft manipulator.}  
  \item \rkk{Repeatable successful grasping demonstrations with a physical prototype and an experimental characterization of the uncertainty regions that can be tolerated by the soft gripper.}
  %\item \rkk{End-effector control of the grasping manipulator attached to a soft arm using a motion tracking system}.
  \item \rkk{Demonstrate that soft robots do neither require force sensing nor accurate positioning to allow for proper manipulation of delicate objects.} 
\end{itemize}

%This paper is organized as follows: In Section~\ref{sec:System_Overview} we provide an overview of the planar manipulation system. In Section~\ref{sec:soft_grasping_manipulator} the gripper morphology is described, its operating principles are discussed in relation to existing morphologies, and the lost wax fabrication process is explained. Section~\ref{sec:processing_and_control} details the planning algorithms for grasp-and-place. Section~\ref{sec:experimental_results} shows results from experimental runs and provides evaluations and experimental insights. Lastly, Section~\ref{sec:conclusion} concludes by providing a summary and discussion.

### 2015-07-07 katzschmann2015autonomous.tex
initial commit of soro paper on automous grasping

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%2345678901234567890123456789012345678901234567890123456789012345678901234567890
%        1         2         3         4         5         6         7         8
\documentclass[letterpaper, 10 pt, twocolumn, conference]{article}

\usepackage[paper=letterpaper,left=19.1mm,right=19.1mm,width=7in,top=19.1mm,bottom=19.1mm]{geometry}
\usepackage{newtxmath}
\usepackage{times} % assumes new font selection scheme installed

\usepackage{multirow}
\usepackage{setspace} % This is used in the title page
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{array}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{amsmath, amssymb, graphics, setspace}
\usepackage{caption}
%\usepackage{algorithmic}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage[noend]{algpseudocode}
\usepackage{longtable}
\usepackage{natbib}
\bibliographystyle{plainnat}
%\usepackage{section}{placeins}
\usepackage{float}
\usepackage{hyperref}
\usepackage[section]{placeins}

%%USER ADDED PACKAGES

\usepackage{courier}
%\usepackage{makeidx}         % allows index generation
%\usepackage[pdftex]{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{xpatch} % for vertical spacing of algorithm environment
%\usepackage{epstopdf} % allow eps to pdf conversion
\usepackage{color}

%% END OF USER ADDED PACKAGES

%% User command

%% User command
\makeatletter
\newcommand{\algorithmicinput}{\textbf{Parameters:}}
\newcommand{\Input}{\item[\algorithmicinput]}
\makeatother

\let\oldhat\hat
\renewcommand{\vec}[1]{\boldsymbol{#1}}
\renewcommand{\hat}[1]{\oldhat{\mathbf{#1}}}

%to make vertical spacing of algorithm environment larger or smaller
\algrenewcommand\alglinenumber[1]{{\sffamily\footnotesize#1}}
\makeatletter
%\xpatchcmd{\algorithmic}{\itemsep\z@}{\itemsep=0.7ex}{}{} %..ex value decides about the algorithm environment spacing
\makeatother

\renewcommand{\algorithmiccomment}[1]{\bgroup\hfill\scriptsize//~#1\egroup}

\makeatletter
\let\OldStatex\Statex
\renewcommand{\Statex}[1][3]{%
  \setlength\@tempdima{\algorithmicindent}%
  \OldStatex\hskip\dimexpr#1\@tempdima\relax}
\makeatother

\restylefloat{figure}

\newcommand{\unit}[1]{\ensuremath{\, \mathrm{#1}}} %Use this macro to tell \LaTeX that you don’t want your units slanted in math mode.
%\newcommand{\rkk}[1]{{\color{blue}#1}} 
\newcommand{\rkk}[1]{#1}

\pdfminorversion=4

%% END user commands

\title{\LARGE \bf
Autonomous Object Manipulation using a Soft Planar Grasping Manipulator}
\author{Robert K. Katzschmann, Andrew D. Marchese, and Daniela Rus% <-this % stops a space
\thanks{Robert K. Katzschmann, Andrew D. Marchese, and Daniela Rus are with the Computer Science and Artificial Intelligence Laboratory, Massachusetts Institute of Technology, 32 Vassar St. Cambridge, MA 02139, USA, {\tt\small \{rkk, andy, rus\}@csail.mit.edu}}%
}

\begin{document}

\maketitle
\thanks
%\twocolumn[
  %\begin{@twocolumnfalse}
    \begin{abstract}
	\textbf{
      	\input{abstract}
	}
    \end{abstract}
    %\bigskip
  %\end{@twocolumnfalse}
%]
%\thispagestyle{empty}
%\pagestyle{plain}

\input{introduction}

\input{system_overview}

\input{robotic_gripper}

\input{processing_control}

\input{experimental_results}

\input{conclusion}

\section*{ACKNOWLEDGMENTS}
This research was conducted in the Distributed Robotics Laboratory at MIT with support from the National Science Foundation, grant numbers NSF 1117178, NSF EAGER 1133224, NSF IIS1226883 and NSF CCF1138967, and National Science Foundation Graduate Research Fellowship Program, primary award number 1122374. We are grateful for this support.

\bibliography{katzschmann2015autonomous}

\end{document}

### 2015-07-07 processing_control.tex
initial commit of soro paper on automous grasping

\section{Planning and Control}
\label{sec:processing_and_control}
\subsection{Existing Procedures}
The forward kinematics algorithm \texttt{forwKin()}, which we employ in this work, assumes piece-wise constant curvature according to \cite{webster2010design}. 
This algorithm was experimentally validated for the soft planar arm in \cite{marchese2014design}.
In order to uniquely fit a configuration representation to measured endpoint data in real-time, we use a previously developed single segment inverse kinematics algorithm \cite{marchese2014design} and refer to it in this work as \texttt{singSegInvKin()}.
The inputs to this block are the start and endpoint measurements in $\mathbb{R}^2$: $\mathbf{E}_n \; \forall n  = 1..N$, where $N$ is the number of segments composing the arm.
The outputs from this block are the representations of the measured manipulator configuration: $\boldsymbol{\kappa}_{\textrm{meas}}$ and $\mathbf{L}_{\textrm{meas}}$.
This work expands on the previously developed cascaded closed-loop curvature controller, whose input is target curvatures $\boldsymbol{\kappa}_{\textrm{target}}$ and whose output is the controlled adjustment of a fluidic drive cylinder array to resolve the error between $\boldsymbol{\kappa}_{\textrm{target}}$ and $\boldsymbol{\kappa}_{\textrm{meas}}$.
In this work we refer to it as the \texttt{curvatureController()}.

\rkk{The planning algorithm presented in \cite{marchese2014whole} was developed to plan the motion of a soft arm  without gripper through a confined environment. 
The optimization constraints and state machine setup in that work is significantly different and not applicable to the grasping shown here. 
Therefore, a new planner is presented in the following section.}

\subsection{Grasp-and-Place Planner}
\label{subsec:grasp-place-planner}
The robotic manipulation system is capable of autonomously performing grasp-and-place operations. 
A state flow diagram describing its sensing, planning and executions states is given in Fig. \ref{fig:grasp-and-place-planner}. 
A motion tracker constantly captures the position of the object and passes it along to a routine, which checks for the object to settle. 
After it has settled, the grasp object planner receives the coordinates and radius of the settled object and together with the current curvature values of the arm and gripper, it solves a series of constrained nonlinear optimization problems to generate end-effector poses approaching the object.
\rkk{Those end-effector poses are essentially waypoints for an optimized path the robot arm should take to get to the final position without the risk of pushing away the object before the gripper arrives there. 
Forcing the arm controller to follow those intermediate waypoints ensures that the arm moves to the object while its nullspace maintains a convex shape, bending away from the object. 
Furthermore, it allows the arm to move in smaller portions, decreasing the risk of large overshoots due to slip-stick friction between the roller supports and the ground.} 
This planner is described in more detail in Section~\ref{subsec:grasp_planner}.

\begin{figure}[!htb]
\centering
   \includegraphics[width=0.95\columnwidth]{Figures/processing_control/grasp_place_planner.eps}
   \caption{State flow diagram of the grasp-and-place planner developed for the autonomous grasp-and-place operation of the manipulator. This diagram describes essentially the flow of information from the motion tracking system to the discrete hardware.}
   \label{fig:grasp-and-place-planner}
\end{figure}

The grasp object planner passes the approach configurations $\boldsymbol{\kappa}_i^*$ of the arm to the \texttt{curvatureController()} for execution in real-time.
The controller receives measured curvatures $\boldsymbol{\kappa}_{meas}$ and lengths $\boldsymbol{L}_{meas}$ at an update rate of $100\unit{Hz}$ from the recursively called \texttt{singSegInvKin()} and uses these to successively control the arm to every intermediate configuration $\boldsymbol{\kappa}_i^*$.
During the arm initialization, the new curvature controller performs a pre-pressurization of both lateral channels. 
This is only done for the two segments closest to the root of the arm in order to stiffen them and shorten their response time constant.  
To allow for smoother transitions between each configuration $\boldsymbol{\kappa}_i^*$, we also added a trajectory generation procedure \texttt{trajGen()} to the new curvature controller. It generates in real-time for each individual degree-of-freedom velocity profiles with acceleration and velocity constraints.
These profiles allow real-time interpolation between the approach configurations of the arm and avoid overshooting at the next target configuration.
When the arm has arrived at the object, the curvature controller initiates \texttt{graspObject()}.
After encapsulating the object, \texttt{moveToBin()} requests \texttt{trajGen()} for another trajectory from the current pose to a pre-defined bin location.
After the manipulator has arrived at the bin location, the procedure \texttt{releaseObject()} causes the gripper to open and release the object.

\subsection{Grasp Planner}
\label{subsec:grasp_planner}
A fundamental component of the grasp-and-place planner is the system's ability to plan a feasible approach motion to the object.
That is, given the location $\left(x_o, \, y_o\right)$ and radius $r_o$ of a round object as well as the manipulator's current configuration $\boldsymbol{\kappa}_{\textrm{meas}}$, we determine a series of locally optimal manipulator configurations $\boldsymbol{\kappa}_i^* \; \forall i \, = 1.. numMoves$ that will, if sequentially achieved, bring the manipulator gradually closer to the object while \rkk{any part of the arm is} not touching the object.
We refer to these as approach configurations.
The process for determining these approach configurations is detailed in the \texttt{planGrasp()} procedure within the Grasp Object Planner, see Algorithm \ref{alg:planGrasp}.
The planner is visualized in Figure \ref{fig:planGrasp}.
In short, we define a series of approach radii $r_{a_i} \;  \forall i\, = 1.. numMoves$ that define concentric circles shrinking from the manipulator's starting tip pose towards the center of the object.
Given actuator limits, we then search for a series of feasible manipulator configurations $\boldsymbol{\kappa}_i^*$ that will place the robot's end-effector on these circles, parameterized by $r_a$ and $\phi$, while minimizing manipulator deformation.

\begin{figure}[htpb]
\centering
   \includegraphics[width=0.85\columnwidth, trim = 0mm 0mm 5mm 5mm, clip]{Figures/processing_control/grasp_object_planner.eps}
   \caption{Grasp object planner visualization. Concentric approach circles are shown in \emph{green} and are centered about the object shown in \emph{cyan}. The locally optimal approach configurations are shown in \emph{blue} and the gripper is shown in \emph{red}. The initially measured manipulator configuration is shown in black.}
   \label{fig:planGrasp}
\end{figure}

\begin{algorithm}[!htbp]
\begin{small}
  \SetAlgoLined\DontPrintSemicolon
  \KwIn{
  $\boldsymbol{\kappa}_{\textrm{meas}}$, $\mathbf{L}_{\textrm{meas}}$ $\gets$ measured arm configuration \;
  $\boldsymbol{\kappa}_{\textrm{off}}$ $\gets$ bias configuration offset at start \;
  $g_{\textrm{off}}$ $\gets$ gripper offset normal to end-effector\;
  $x_o$, $y_o$, $r_o$ $\gets$ object center coordinates and radius \;
  $N$ $\gets$ number of manipulator segments}
  \SetKwFunction{planGrasp}{planGrasp}
  \SetKwFunction{findOptimalConfig}{findOptimalConfig}
  \SetKwFunction{forwKin}{forwKin}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\planGrasp{}}{
  $\mathbf{w}_t \gets \forwKin \left( \boldsymbol{\kappa}_{\textrm{meas}}, \, \mathbf{L}_{\textrm{meas}}, \, N, \, L_N \right)$. \;
  $d_1 \gets \| \left[ x_o, \, y_o \right]^{\textrm{T}} \, - \, \mathbf{w}_t \|$. \;
  $d_2 \gets d_1 - r_o - g_{\textrm{off}}$. \;
  $numMoves \gets \lfloor \frac{d_2}{\Delta d} \rfloor$. \;
  $i$ = 0. \;
  \Repeat{$i$ = $numMoves$}{
    $i$ = $i \, + \, 1$ \;
    $r_{a_i} \gets d_1 \, - \, i\,\frac{d_2}{numMoves}$. \;
    $\boldsymbol{\kappa}_i^* \gets$ \findOptimalConfig{$r_{a_i}$}\;
  }
  \KwRet{$\boldsymbol{\kappa}_i^* \quad \forall i \, = 1.. numMoves$} \;}{}
  \setcounter{AlgoLine}{0}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\findOptimalConfig{$r_a$}}{
  $\begin{aligned}
    & \boldsymbol{\kappa}^* \, \gets \, \underset{\phi, \, \boldsymbol{\kappa}}{\text{min}}
    & & \mathbf{R} \, \left( \boldsymbol{\kappa} \, - \, \boldsymbol{\kappa}_{\textrm{off}} \right)^2. \\
    & \text{subject to}
    & &  \mathbf{w}_t \gets \begin{bmatrix} x_o \, + \, r \, \cos{\phi} \\ y_o \, + \, r \, \sin{\phi} \\ \phi \, + \, \frac{\pi}{2} \end{bmatrix}. \\
    & & & \mathbf{f} \gets \forwKin\left( \boldsymbol{\kappa}, \, \mathbf{L}, \, N, \, L_N \right). \\
    & & & \mathbf{w}_t - \mathbf{w}_{\textrm{off}}\left(r_o, \, \phi \right) - \mathbf{f} \, = \, \mathbf{0}. \\
    & & & \kappa_{n}^{\text{min}} \leq \kappa_n \leq \kappa_{n}^{\text{max}} \quad \forall \, n = 1 \, .. \,N. \\
    \end{aligned}$ \;
  \KwRet{$\boldsymbol{\kappa}^*$} \; }
  \setcounter{AlgoLine}{0}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\forwKin{$\boldsymbol{\kappa}$, $\mathbf{L}$, $i$, $s$ }}{
  \KwIn{$\boldsymbol{\kappa}$, $\mathbf{L}$, $i$ the segment of interest index, $s$ the arc length along the indexed segment}
  \eIf{$i = 0$}{
        $\theta_{i}(0) \gets \theta_0(0)$. \;
        $x_{i}(0) \gets 0$.\;
        $y_{i}(0) \gets 0$.\; }
    {
        $\left[ x_{i}(0), \, y_{i}(0), \, \theta_{i}(0) \right] \gets \forwKin \left(\boldsymbol{\kappa}, \, \mathbf{L}, \, i-1, \, L_{i-1} \right)$.\;
    }
    $\theta \gets \theta_{i}(0) + k_i s$. \;
    $x \gets x_{i}(0) + \frac{\sin{\theta}}{k_i} - \frac{\sin{\theta_{i}(0)}}{k_i}$. \;
    $y \gets y_{i}(0) - \frac{\cos{\theta}}{k_i} + \frac{\cos{\theta_{i}(0)}}{k_i}$. \;
  \KwRet{$\left[ x, \, y, \, \theta \right]^{\mathrm{T}}$ or $\left[ x, \, y \right]^{\mathrm{T}}$}}
  \caption{Grasp object planner}
  \label{alg:planGrasp}
\end{small}

\end{algorithm}

The procedure first determines the manipulator's current tip pose $\mathbf{w}_t$ and the Euclidean distance $d_1$ between the tip and the object's center. 
Next, considering the object's radius $r_o$ and the gripper normal offset $\mathbf{g}_{\textrm{off}}$, the minimal tip transit distance $d_2$ is calculated. 
$\mathbf{g}_{\textrm{off}}$ is the component of the end effector offset $\mathbf{w}_{\textrm{off}}$, which is normal to the end effector orientation. 
Also, the number of approach configurations $numMoves$ is determined as $\lfloor \frac{d_2}{\Delta d} \rfloor$, where $\Delta d$ is an allowable incremental distance. 
Using these parameters, approach radii $r_a$ are iteratively calculated and their corresponding locally optimal configurations are found using the \texttt{findOptimalConfig($r_a$)} procedure. 
This process is posed as a nonlinear optimization. 
Here, the objective function represents the summation of independently weighted manipulator curvatures and the constraints force the manipulator's tip to lie on and to be tangent to the approach circle. 
This process leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced in Algorithm \ref{alg:planGrasp} for convenience.

### 2015-07-07 robotic_gripper.tex
initial commit of soro paper on automous grasping

\section{Soft Grasping Manipulator}
\label{sec:soft_grasping_manipulator}
%The robotic manipulator is composed of multiple bidirectional planar arm segments and combined with a unidirectional soft gripper.
%We first introduce the previously developed uniform channel design, which is used for the soft body arm segments.
%Following this, 
We describe briefly the design, fabrication and functionality of the soft grasping manipulator. Further details on the design and fabrication can be found in \cite{marchese2015recipe}.

%\subsection{Uniform Channel Design of the Soft Arm}

\begin{figure}[thpb]
\centering
   \includegraphics[width=0.50\columnwidth]{figures/robotic_gripper/design_gripper.eps}
   \caption{The pleated channel designs. (\textbf{A}) depicts the segment in an unactuated state and (\textbf{B}) shows the segment in an actuated and therefore bent state. The expansion of the pressurized channels are schematically represented.}
   \label{fig:design}
\end{figure}

%Several existing body segment morphologies are serpentine channels \cite{correll2010soft, marchese2014design}, uniform lateral channels \cite{marchese2014whole}, and pleated channels \cite{polygerinos2013towards, mosadegh2014pneumatic}.
%The serpentine channel design with its multiple vertical channels was first characterized by Correll et al.\cite{correll2010soft} and Onal et al.\cite{onal2011soft} and called a fluidic elastomer actuator.
%A cross sectional view of this design is shown in Figure~\ref{fig:design}-1.
%The design is described in \cite{marchese2014design} and paraphrased here.
%Bidirectional bending of this segment type is achieved by the pressurization of paired agonistic fluidic channel groups shown in \emph{yellow} that are separated by an inextensible but flexible constraint layer shown in \emph{black}. 
%These fluid channels are embedded within elastomer layers shown in \emph{cyan}.
%When a channel's internal fluid is pressurized, the elastomer deforms and the inextensible constraint transforms this channel deformation into segment curvature.
%The inextensible layer is typically made of a thin plastic film or fabric.
%A uniform channel design for soft segments is shown in Figure~\ref{fig:design}-1.
%It is an extension of the serpentine channel design by Correll et al. \cite{correll2010soft} and Onal et al. \cite{onal2011soft}. 
%The uniform channel design is achieved through changing both its kinematic constraints and fluidic channel geometry.
%This new design was first described in \cite{marchese2014whole} and is reused for our soft arm.
%The outer concentric layer remains composed of soft silicone rubber and is shown as \emph{transparent}.
%Bidirectional bending is achieved by pressurizing one of the two cylindrically-shaped and laterally embedded agonistic channels within this outer layer. 
%These channels are shown in \emph{yellow}.
%Also, a stiffer inner silicone layer shown in \emph{cyan} replaces an inextensible constraint layer found in the serpentine channel design.
%The stiffer inner layer introduces a partial constraint, so that an expansion of the lateral fluidic channels causes bending.
%This entirely soft design is simpler to fabricate because it does not require lamination.
%The design though is limited in defining the geometry of the fluidic channels, only cylindrical or cone shaped fluidic channels are possible. 
%This design is modular, because tubes can be passed through a hollow center, which allows the combination of many segments to an arm.
%Also, this design does not delaminate under high pressure as opposed to the serpentine design.
%This design was therefore chosen for making the arm to which the gripper is attached.

\subsection{Pleated Channel Design for the Gripper}
The pleated channel design consists of evenly spaced ribs shown in \emph{cyan} with embedded hollow sections shown in \emph{yellow}.
Cut views of the un-actuated and actuated states are shown in Figure~\ref{fig:design}.
This design approach draws inspiration for its pleats from the soft pneumatic gloves developed by Polygerinos et al. \cite{polygerinos2013towards} and its homogeneous body design is inspired from the tail design of a soft robotic fish developed by Katzschmann et al. \cite{katzschmann2014hydraulic}.
This design is advantageous for grasping because it exhibits high curvature, minimal radial expansion, and remains compliant during actuation \cite{marchese2015recipe}. 
The hollow ribs within the segment's pleats are connected by a center channel and are accessible through a front inlet.
Under fluidic pressurization of the interior channel, an individual pleat allows for a ballon-like expansion of the thin exterior skin along the axial direction.
Similar to the uniform channel design, a stiffer silicone layer shown in \emph{blue} serves as an almost inextensible constraint layer.
The sum of the ballon-like expanding motions leads to bending of the less extensible center constraint layer to form a grasp.
The pleated design is capable of unidirectional bending up to extreme curvatures.
Using a lost-wax casting approach, we are not limited in defining the geometry of the segment's fluidic channels.
Using this approach, the \emph{cyan} portion of the pleated gripper can be cured in a single step, avoiding any weakening seams due to lamination.
Those seams are prone to rupture and manufacturing inconsistencies.

\subsection{\rkk{Lost Wax Fabrication for Fluidic Elastomer Actuators}}
Existing soft fluidic manipulators are produced through a multi-step lamination process, which results in weakening seams that can easily delaminate. 
This limits their range of applications and lifetime.
This is why we propose the application of lost-wax casting to the fabrication of soft fluidic actuators like a gripper.
The actuated cavities of the soft gripper are achieved by using a wax core, pourable silicone rubber and 3D printed molds.
The complete fabrication process for the soft gripper consists of eight steps that are depicted in Figure~\ref{fig:fabrication}.
The tools and equipment used are listed in Table~\ref{tab:MachineTools} and are referred to by superscripts.

\begin{figure}[htb]
\centering
   \includegraphics[width=0.98\columnwidth]{figures/robotic_gripper/fab_pleated_process_horizontal_no_labels.eps}
      \caption{Gripper fabrication process. (\textbf{A}) Pour and cure a rubber mold, (\textbf{B}) pour wax core with embedded supportive rod, (\textbf{C}) combine bottom mold, top mold and wax core using pins, (\textbf{D}) pour rubber into assembled mold, (\textbf{E}) pour stiffer rubber on top of the cured gripper to form a constraint layer, (\textbf{F}) remove cured gripper from mold, (\textbf{G}) using an oven melt out wax core from the gripper, and (\textbf{H}) add silicone tubing and plug using silicone sealant.}
      \label{fig:fabrication}
\end{figure}

In step (A), harder silicone rubber$^6$ is poured into a mold, which contains a printed model of the wax core.
In preparation for step (B), the model is removed and the rubber mold is left inside the outer mold.
A rigid rod is used as a supportive inlay inside the wax core.
The rod is laid into the cavity of the rubber mold, supported on both ends by the outer mold.
This ensures that the wax core does not break when removed from the rubber mold.
%Mold release spray is applied to the silicone rubber mold to ease the wax core removal process.
The bees-wax$^{7}$ is heated up until it becomes fully liquefied.
The assembly of rubber mold and outer mold is then heated up for a few minutes to the same temperature as the wax.
Using a syringe, the liquid wax is injected into the assembly.
Within a few minutes, the injected wax will start to solidify and significantly shrink in volume; this is counteracted by injecting more hot wax into the solidifying wax core during cool down.
In step (B), the wax core is first allowed to completely cool down, then it is released from the mold.
In step (C), the cooled down wax core is assembled together with the bottom mold, which defines the pleated structure of the gripper.
The mold assembly is aligned with a top mold using pins. This top mold provides for additional volume to cover the wax core.
In step (D), low elastic modulus rubber$^1$ is mixed, degassed in a vacuum$^2$, and poured to form the gripper and allowed to cure.
In step (E), stiffer rubber$^3$ is poured on top of the cured gripper to form a constraint layer.
In step (F), the cured gripper is removed from the mold.
In step (G), most of the wax core is melted out by placing the gripper into an oven in an upright position.
After this, remaining wax residues are cooked out in a boiling water bath.
Finally, in step (H) a silicone tube$^5$ and a piece of silicone cord$^{8}$ get covered with silicone sealant$^4$ and are inserted into the front and back holes respectively.

\begin{table}[h]
\caption{Commercially Available Tools and Equipment}
\centering
\begin{tabular}{c l l}
\hline
\hline
\# & Product Name & Company\\
\hline
1 & Ecoflex 0030&  Smooth-On\\
2 & AL Cube & Abbess Instruments and Systems, Inc.\\
3 & Mold Star 15 & Smooth-On\\
4 & Silicone Sealant 732 & Dow Corning Corp\\
5 & PN 51845K53 & McMaster\\
6 & Mold Star 30 & Smooth-On\\
7 & Beeswax & Jacquard\\
8 & PN 9808K21& McMaster\\
\hline
\end{tabular}
\label{tab:MachineTools}
\end{table}

\subsection{\rkk{Multi-segment Arm with Gripper}}

The design for our arm consisting of soft cylindrical segments was described in \cite{marchese2014whole}.
Each cylindrical segment can only be actuated up to a bend angle of less than $60^\circ$, therefore several segments have to be combined together to allow the arm to reach a large enough workspace to perform proper manipulation tasks on a plane. 
Our cylindrical design with its hollow channel in the center has enough space to accomodate for pneumatic tubes to connect to all six cylindrical segments and additionally to the pleated gripper, which is attached to the tip. 
The pleated gripper has to be appropriately sized, just big enough to allow for proper manipulation without exceeding the payload capacity of the soft arm.

The independent actuation of the unidirectional gripper and each bidirectional arm segment is achieved through an array of custom fluidic drive cylinders.
%The fluidic drive cylinders control the curvature of a bidirectional arm segment or a unidirectional gripper.
Those cylinders are driven by a linear actuator and controlled through a motor controller, which takes its command signals from a higher-level curvature controller. 
The modeling and design of these are described in \cite{marchese2014design}.

### 2015-07-07 system_overview.tex
initial commit of soro paper on automous grasping

\section{System Overview}
\label{sec:System_Overview}
The aggregate system is shown in Figure \ref{fig:sys_overview} and consists of a manipulator, a gripper, an object, a tracking system, control computers, a fluidic drive array and a rigid frame.
The planar six segment soft rubber manipulator consists of twelve distributed elastomer actuators. This manipulator moves with minimal friction on a level plane.
A soft rubber gripper is fixed to the tip of the manipulator.
An object is randomly placed within the reachable envelop of the manipulator. 
A motion capture system provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
The grasp motion planning algorithm as well as the curvature controller run on the control computers and take the tracking information as input.
The curvature controller then provides continuous closed-loop adjustment of the fluidic drive cylinder array.
The cylinder array directly actuates the manipulator and gripper.
A rigid frame holds all the subsystems together providing reliable and consistent hardware experiments.

\begin{figure}[htbp]
\begin{centering}
  \includegraphics[width=2.0in]{Figures/system_overview/sys_overview_smaller}\\
  \caption{System Overview. The system is composed of a motion capture system (A), rigid frame (B), soft six segment planar manipulator (C), an object within the grasp envelope (D), a soft gripper fixed to the manipulator (E), a fluidic drive cylinder array to control actuation (F), and computers for real-time processing and control (G).} \label{fig:sys_overview}
\end{centering}
\end{figure}

### 2015-07-30 introduction.tex
preparing for submission to soft robotics journal

@@
 Deimel and Brock \cite{deimel2013compliant} developed a pneumatically actuated three-fingered hand made of reinforced silicone that is mounted to a hard robot and capable of grasping.
-More recently, they have developed an anthropomorphic soft pneumatic hand capable of dexterous grasps, which is not mounted to a robot, but instead just held by a human\cite{deimel2014novel}. 
+More recently, they have developed an anthropomorphic soft pneumatic hand capable of dexterous grasps, which is not mounted to a robot, but instead just held by a human \cite{deimel2014novel}. 
 Ilievski et al. \cite{ilievski2011soft} create \rkk{through a soft-lithography fabrication} a pneumatic starfish-like gripper composed of \rkk{an array of silicone chambers and a PDMS membrane.} 
@@
 The closest related soft pneumatic actuator design to our current work is the fast Pneu-net designs by Mosadegh et al.
-detailed in \cite{mosadegh2014pneumatic} and by Polygerinos et al.
-detailed in \cite{polygerinos2013towards}.
+\cite{mosadegh2014pneumatic} and by Polygerinos et al.
+\cite{polygerinos2013towards}.
 These finger-like actuators deform with minimal volume change and can bend to high curvatures.

### 2015-07-30 katzschmann2015autonomous.tex
preparing for submission to soft robotics journal

@@
 \usepackage{natbib}
-\bibliographystyle{plainnat}
+\bibliographystyle{plain}
 %\usepackage{section}{placeins}
@@
 \section*{ACKNOWLEDGMENTS}
-This research was conducted in the Distributed Robotics Laboratory at MIT with support from the National Science Foundation, grant numbers NSF 1117178, NSF EAGER 1133224, NSF IIS1226883 and NSF CCF1138967, and National Science Foundation Graduate Research Fellowship Program, primary award number 1122374.
+This research was conducted in the Distributed Robotics Laboratory at MIT with support from the National Science Foundation, grant numbers NSF 1117178, NSF IIS1226883 and NSF CCF1138967, and National Science Foundation Graduate Research Fellowship Program, primary award number 1122374.
 We are grateful for this support.

### 2015-08-09 experimental_results.tex
moved figure 7 up

@@
 \label{sec:experimental_results}
+
+\begin{figure}[htb]
+\centering
+   \includegraphics[width=0.8\columnwidth]{Figures/experimental_results/uncertainty}
+   \caption{\rkk{Experimental characterization of the gripper's capture region: the allowable positioning uncertainty is determined through repeated placements of the center of a cylindrical object at different points on a grid relative to the gripper.
+Blue dots indicate all object center positions for which a grasp could be performed successfully, red crosses show the positions where a grasp failed.
+The grey line outlines an area for the object to be positioned within so the gripper can grasp it.
+The evaluation of the capture region was performed similarly to a method described in \cite{dogar2010push}.}}
+   \label{fig:grasp_uncertainty}
+\end{figure}
+
 \subsection{\rkk{Grasping Delicate Objects}}
@@
 The five points were chosen to approximately represent the major portion of the manipulator's reachable workspace.
-\rkk{As long as the root of the gripper stops so that the object is located within the capture region, the gripper will pick it up through its sweeping closing motion.
+As long as the root of the gripper stops so that the object is located within the capture region, the gripper will pick it up through its sweeping closing motion.
 The capture region is shown in grey in Figure~\ref{fig:grasp_uncertainty}.
-\begin{figure}[htb]
-\centering
-   \includegraphics[width=0.8\columnwidth]{Figures/experimental_results/uncertainty}
-   \caption{\rkk{Experimental characterization of the gripper's capture region: the allowable positioning uncertainty is determined through repeated placements of the center of a cylindrical object at different points on a grid relative to the gripper.
-Blue dots indicate all object center positions for which a grasp could be performed successfully, red crosses show the positions where a grasp failed.
-The grey line outlines an area for the object to be positioned within so the gripper can grasp it.
-The evaluation of the capture region was performed similarly to a method described in \cite{dogar2010push}.}}
-   \label{fig:grasp_uncertainty}
-\end{figure} 
-When the arm reaches the red bin location, it drops the object.}
+
+When the arm reaches the red bin location, it drops the object.
 

### 2015-10-08 experimental_results.tex
final adjustements before revision submission

@@
 \label{sec:experimental_results}
+In the following section summarizes the results from experiments with the soft manipulator.
+We discuss the grasping of delicate objects and cylindrical objects as well as the repeatability and success rate of the autonomous system.
+
+\subsection{\rkk{Grasping Delicate Objects}}
+The soft manipulator can pick up eggs and other delicate objects without breaking them. 
+Figure~\ref{fig:egg_approach_sequence} shows how the manipulator approaches and grasps an egg.
+Delicate objects can be manipulated without requiring a shape or a force sensor within its structure, since the compliant gripper body conforms to the object.
+Rigid-bodied grippers usually rely on force sensing or another type of sensory feedback to avoid damage caused to the object.
 
@@
    \includegraphics[width=0.8\columnwidth]{Figures/experimental_results/uncertainty}
-   \caption{\rkk{Experimental characterization of the gripper's capture region: the allowable positioning uncertainty is determined through repeated placements of the center of a cylindrical object at different points on a grid relative to the gripper.
+   \caption{Experimental characterization of the gripper's capture region: the allowable positioning uncertainty is determined through repeated placements of the center of a cylindrical object at different points on a grid relative to the gripper.
 Blue dots indicate all object center positions for which a grasp could be performed successfully, red crosses show the positions where a grasp failed.
 The grey line outlines an area for the object to be positioned within so the gripper can grasp it.
-The evaluation of the capture region was performed similarly to a method described in \cite{dogar2010push}.}}
+The evaluation of the capture region was performed similarly to a method described in \cite{dogar2010push}.}
    \label{fig:grasp_uncertainty}
 \end{figure}
-
-\subsection{\rkk{Grasping Delicate Objects}}
-\rkk{The soft manipulator can pick up hollowed-out eggs and other delicate objects without breaking them. 
-Figure~\ref{fig:egg_approach_sequence} shows how the manipulator approaches and grasps an egg.
-Delicate objects can be manipulated without requiring a shape or a force sensor within its structure, since the compliant gripper body conforms to the object.
-Rigid-bodied grippers usually rely on force sensing or another type of sensory feedback to avoid damage caused to the object.}
-
-%\subsection{\rkk{Allowable Grasping Uncertainty}}
-%
-%\rkk{We experimentally characterized the allowable grasping region of the soft gripper to show that despite positioning inaccuracies, the gripper can still successfully perform a grasp of an object. 
-%The evaluation of this allowable grasping region is performed similarly to a method described in Dogar and Srinivasa\cite{dogar2010push} work on determining capture regions for a push-grasp of a classical robotic gripper.}
-%
 
@@
 The object was placed five times on each of the five points marked on the board.
-\rkk{The markers only serve as a reference point for the user to place the object roughly at the same point at every repetition.
-The user's placing accuracy is not important to the algorithm, the tracking system newly registers every single time the position of the placed object.}
+The markers only serve as a reference point for the user to place the object roughly at the same point at every repetition.
+The user's placing accuracy is not important to the algorithm, the tracking system newly registers every single time the position of the placed object.
 The five points were chosen to approximately represent the major portion of the manipulator's reachable workspace.
@@
 The capture region is shown in grey in Figure~\ref{fig:grasp_uncertainty}.
+The evaluation of the capture region is performed similarly to a method described in Dogar and Srinivasa\cite{dogar2010push} work on determining capture regions for a push-grasp of a classical robotic gripper.
+Despite positioning inaccuracies of the soft manipulator, the gripper can nevertheless successfully perform a grasp of an object.
 

### 2015-10-08 processing_control.tex
final adjustements before revision submission

@@
 \label{sec:processing_and_control}
+This section covers our approach to preplanning motion waypoints for the soft robot and controlling the manipulator along those points.
+We cover existing procedures reused within the system, and detail the system's new architecture of for performing autonomous grasp-and-place tasks, including its main component, the Grasp Object Planner.
+
 \subsection{Existing Procedures}
@@
 
-\subsection{Grasp-and-Place Planner}
+\subsection{Autonomous Grasp-and-Place System}
 \label{subsec:grasp-place-planner}
@@
 A motion tracker constantly captures the position of the object and passes it along to a routine, which checks for the object to settle. 
-After it has settled, the grasp object planner receives the coordinates and radius of the settled object and together with the current curvature values of the arm and gripper, it solves a series of constrained nonlinear optimization problems to generate end-effector poses approaching the object.
+After it has settled, the Grasp Object Planner receives the coordinates and radius of the settled object and together with the current curvature values of the arm and gripper, it solves a series of constrained nonlinear optimization problems to generate end-effector poses approaching the object.
 \rkk{Those end-effector poses are essentially waypoints for an optimized path the robot arm should take to get to the final position without the risk of pushing away the object before the gripper arrives there.
@@
 
-The grasp object planner passes the approach configurations $\boldsymbol{\kappa}_i^*$ of the arm to the \texttt{curvatureController()} for execution in real-time.
+The Grasp Object Planner passes the approach configurations $\boldsymbol{\kappa}_i^*$ of the arm to the \texttt{curvatureController()} for execution in real-time.
 The controller receives measured curvatures $\boldsymbol{\kappa}_{meas}$ and lengths $\boldsymbol{L}_{meas}$ at an update rate of $100\unit{Hz}$ from the recursively called \texttt{singSegInvKin()} and uses these to successively control the arm to every intermediate configuration $\boldsymbol{\kappa}_i^*$.
@@
 
-\subsection{Grasp Planner}
+\subsection{Grasp Object Planner}
 \label{subsec:grasp_planner}
-A fundamental component of the grasp-and-place planner is the system's ability to plan a feasible approach motion to the object.
+A fundamental component of the grasp-and-place system is its ability to plan a feasible approach motion to the object.
 That is, given the location $\left(x_o, \, y_o\right)$ and radius $r_o$ of a round object as well as the manipulator's current configuration $\boldsymbol{\kappa}_{\textrm{meas}}$, we determine a series of locally optimal manipulator configurations $\boldsymbol{\kappa}_i^* \; \forall i \, = 1..
@@
    \includegraphics[width=0.85\columnwidth, trim = 0mm 0mm 5mm 5mm, clip]{Figures/processing_control/grasp_object_planner.eps}
-   \caption{Grasp object planner visualization.
+   \caption{Visualzation of the Grasp Object Planner.
 Concentric approach circles are shown in \emph{green} and are centered about the object shown in \emph{cyan}.
@@
   \KwRet{$\left[ x, \, y, \, \theta \right]^{\mathrm{T}}$ or $\left[ x, \, y \right]^{\mathrm{T}}$}}
-  \caption{Grasp object planner}
+  \caption{Grasp Object Planner}
   \label{alg:planGrasp}

### 2015-10-10 conclusion.tex
remove old /rkk comments

@@
 Such a homogeneous soft segment is less prone to rupture and to manufacturing inconsistencies, and would therefore allow for better robot performance.
-
+x
 The results presented in this paper suggest that despite their extreme compliance, soft robots are capable of repeatable object manipulation while simultaneously providing inherently safe interactions with their environment.
-\rkk{The manipulator is suitable to perform delicate tasks with low payloads, for example grasping objects that should not be squeezed and/or should not break during manipulation.}
+The manipulator is suitable to perform delicate tasks with low payloads, for example grasping objects that should not be squeezed and/or should not break during manipulation.
 We demonstrated the ability of an entirely soft manipulator to autonomously grasp an object, which leads to many potential applications.
@@
 In a human-centric environment, soft arm grasping manipulation may enable soft robots to interact safely with humans.
-Furthermore, in a surgical setting, highly compliant soft robots with grippers may assist with operations in sensitive environments \rkk{during tasks where no high level of precision is required.}
+Furthermore, in a surgical setting, highly compliant soft robots with grippers may assist with operations in sensitive environments during tasks where no high level of precision is required.

### 2015-10-10 experimental_results.tex
remove old /rkk comments

@@
 
-\subsection{\rkk{Grasping Delicate Objects}}
+\subsection{Grasping Delicate Objects}
 The soft manipulator can pick up eggs and other delicate objects without breaking them. 
@@
 
-\subsection{\rkk{Repeated Grasp Experiments}}
+\subsection{Repeated Grasp Experiments}
 We performed 25 experimental grasp-and-place trials at various positions to demonstrate the capabilities and repeatability of our system.
@@
 One representative approach, grasp, and retract move is shown in Figure~\ref{fig:oneTrialVsTime}.
-In 23 of 25 experimental trials, the manipulator successfully achieved the task of grasping an object and bringing it to a bin \rkk{location shown in red}.
+In 23 of 25 experimental trials, the manipulator successfully achieved the task of grasping an object and bringing it to a bin location shown in red.
 The object was placed five times on each of the five points marked on the board.
@@
 
-\rkk{The unsuccessful trials happened due to stick-slip friction between the roller bearings and the table surface.
+The unsuccessful trials happened due to stick-slip friction between the roller bearings and the table surface.
 Our kinematic modeling does not account for this non-linear behavior, which acts as a disturbance and can lead to failure to arrive at the next waypoint.
@@
 This outlier is shown in Figure~\ref{fig:allTestsOverlaid}.
-Overall, the experiments show that the system was repeatably able to autonomously locate a randomly placed object within its workspace, plan the arm motions, and perform the task of grasping and placing the object.}
+Overall, the experiments show that the system was repeatably able to autonomously locate a randomly placed object within its workspace, plan the arm motions, and perform the task of grasping and placing the object.
 
-\subsection{\rkk{Experimental Insights and Limitations}}
+\subsection{Experimental Insights and Limitations}
 The system can drag payloads of less than 40\unit{g}, higher payloads cause the cylindrical arm segments to stall and possibly lift off the table without moving the payload.

### 2015-10-10 introduction.tex
final adjustements before revision submission
remove old /rkk comments

@@
 %High Level Vision
-\rkk{
 Soft robots exhibit continuum body motion, large scale deformation, high compliance and adjustable impedance  compared to traditional rigid-bodied robots with high impedance \cite{trivedi2008soft}. 
@@
 A rigid gripper can not manipulate delicate objects without a lot of sensing.
-}
+
 Such characteristics make this class of robots well-suited for highly dexterous tasks and interactions that require conformation to environmental uncertainty.
@@
    \includegraphics[width=0.9\columnwidth]{Figures/experimental_results/egg_approach/egg_approach_sequence}
-   \caption{\rkk{The soft manipulator is grasping a hollowed-out egg. The robot repeatably approached, grasped and moved this delicate object without breaking it.}}
+   \caption{The soft manipulator is grasping an egg. The robot repeatably approached, grasped and moved this delicate object without breaking it.}
    \label{fig:egg_approach_sequence}
@@
 %To address these challenges, 
-%\rkk{We developed planning and control algorithms for a soft robotic arm with gripper.}
-\rkk{
+%We developed planning and control algorithms for a soft robotic arm with gripper.
 The fluid-powered gripper at the end of the arm can grasp an object through an open-loop controlled bending motion, even if the gripper is positioned relatively inaccurately in relation to the object to be grasped.
 %The gripper can conform due to his compliance to variations in object geometry, allowing it to successfully grasp.
-}
 The design of the gripper itself is inspired by work of Polygerinos et al.~\cite{polygerinos2013towards}
@@
 \subsection{Related Work}
-There are several examples of soft grippers described in recent literature, \rkk{we will mainly focus on fluidic-based systems.} 
+There are several examples of soft grippers described in recent literature, we will mainly focus on fluidic-based systems. 
 Deimel and Brock \cite{deimel2013compliant} developed a pneumatically actuated three-fingered hand made of reinforced silicone that is mounted to a hard robot and capable of grasping.
 More recently, they have developed an anthropomorphic soft pneumatic hand capable of dexterous grasps, which is not mounted to a robot, but instead just held by a human \cite{deimel2014novel}. 
-Ilievski et al. \cite{ilievski2011soft} create \rkk{through a soft-lithography fabrication} a pneumatic starfish-like gripper composed of \rkk{an array of silicone chambers and a PDMS membrane.} 
-\rkk{
+Ilievski et al. \cite{ilievski2011soft} create through a soft-lithography fabrication a pneumatic starfish-like gripper composed of an array of silicone chambers and a PDMS membrane.
+
 The gripper is hanging on a string and grasps objects like an egg or a mouse in an open-loop controlled manner.
-} 
+
 Stokes et al. \cite{Stokes2014hybrid} use a soft elastomer quadrupedal robot to grasp objects in a hard-soft hybrid robotic platform. 
@@
 An alternative to positive pressure actuated soft grippers is a robotic gripper that makes use of granular material jamming developed by Brown et al. and detailed in \cite{brown2010universal}.
-\rkk{The soft octopus-inspired arms developed in \cite{calisti2010study} and \cite{calisti2011octopus} are not fluidic powered, but instead use cables to pull rigid fixtures embedded within an elastomer body.
-The arms were capable of grasping objects like pens or screws.}
+The soft octopus-inspired arms developed in \cite{calisti2010study} and \cite{calisti2011octopus} are not fluidic powered, but instead use cables to pull rigid fixtures embedded within an elastomer body.
+The arms were capable of grasping objects like pens or screws.
 A soft robotic tentacle developed in \cite{martinez2013robotic} was able to hold a flower and a horseshoe-shaped object.
@@
 These finger-like actuators deform with minimal volume change and can bend to high curvatures.
-\rkk{None of the above described grippers were controlled autonomously to perform their tasks and accordingly no statement on repeatability of the autonomous execution was given.}
+None of the above described grippers were controlled autonomously to perform their tasks and accordingly no statement on repeatability of the autonomous execution was given.
 
-\rkk{Cho et al. \cite{cho2009review} review several manufacturing processes for soft biomimetic robots. 
+Cho et al. \cite{cho2009review} review several manufacturing processes for soft biomimetic robots. 
 The vast majority of soft elastomer robots rely on the processes of soft lithography \cite{xia1998soft} and/or shape deposition manufacturing \cite{cham2002fast}. 
 Especially noteworthy is the use of lost-wax fabrication for jammable skin chambers, which get vacuumed to stiffen up \cite{steltz2009soft}. 
-The gripper presented here also uses a lost-wax molding technique, but with a different type of actuation in mind: the obtained cavity structures are inflated to cause the gripper to bend.}
+The gripper presented here also uses a lost-wax molding technique, but with a different type of actuation in mind: the obtained cavity structures are inflated to cause the gripper to bend.
 
@@
 The manipulator curvatures are controlled in real-time using a curvature-volume cascaded control law.
-\rkk{The work presented in this paper builds on top of this system and expands its capabilities.
+The work presented in this paper builds on top of this system and expands its capabilities.
 The previous version was only suitable for contactless motions in space, that would be suitable for mere inspection.
@@
 %, so the previous system was no repeatable and robust.
-}
 
@@
 \begin{itemize}
-  \item \rkk{A soft manipulator consisting of a multi-segment arm with a gripper to enable fully compliant planar grasping.}
-  \item \rkk{A planning algorithm to grasp-and-place randomly positioned objects on a planar surface using a 7 DOF soft manipulator.}  
-  \item \rkk{Repeatable successful grasping demonstrations with a physical prototype and an experimental characterization of the uncertainty regions that can be tolerated by the soft gripper.}
-  %\item \rkk{End-effector control of the grasping manipulator attached to a soft arm using a motion tracking system}.
-  \item \rkk{Demonstrate that soft robots do neither require force sensing nor accurate positioning to allow for proper manipulation of delicate objects.} 
+  \item A soft manipulator consisting of a multi-segment arm with a gripper to enable fully compliant planar grasping.
+  \item A planning algorithm to grasp-and-place randomly positioned objects on a planar surface using a 7 DOF soft manipulator.  
+  \item Repeatable successful grasping demonstrations with a physical prototype and an experimental characterization of the uncertainty regions that can be tolerated by the soft gripper.
+  %\item End-effector control of the grasping manipulator attached to a soft arm using a motion tracking system.
+  \item Demonstrate that soft robots do neither require force sensing nor accurate positioning to allow for proper manipulation of delicate objects. 
 \end{itemize}

### 2015-10-10 processing_control.tex
remove old /rkk comments

@@
 
-\rkk{The planning algorithm presented in \cite{marchese2014whole} was developed to plan the motion of a soft arm  without gripper through a confined environment. 
+The planning algorithm presented in \cite{marchese2014whole} was developed to plan the motion of a soft arm  without gripper through a confined environment. 
 The optimization constraints and state machine setup in that work is significantly different and not applicable to the grasping shown here. 
-Therefore, a new planner is presented in the following section.}
+Therefore, a new planner is presented in the following section.
 
@@
 After it has settled, the Grasp Object Planner receives the coordinates and radius of the settled object and together with the current curvature values of the arm and gripper, it solves a series of constrained nonlinear optimization problems to generate end-effector poses approaching the object.
-\rkk{Those end-effector poses are essentially waypoints for an optimized path the robot arm should take to get to the final position without the risk of pushing away the object before the gripper arrives there.
-Forcing the arm controller to follow those intermediate waypoints ensures that the arm moves to the object while its nullspace maintains a convex shape, bending away from the object. 
-Furthermore, it allows the arm to move in smaller portions, decreasing the risk of large overshoots due to slip-stick friction between the roller supports and the ground.} 
+Those end-effector poses are essentially waypoints for an optimized path the robot arm should take to get to the final position without the risk of pushing away the object before the gripper arrives there.
+Forcing the arm controller to follow those intermediate waypoints ensures that the arm moves to the object while its null space maintains a convex shape, bending away from the object. 
+Furthermore, it allows the arm to move in smaller portions, decreasing the risk of large overshoots due to slip-stick friction between the roller supports and the ground.
 This planner is described in more detail in Section~\ref{subsec:grasp_planner}.
@@
 That is, given the location $\left(x_o, \, y_o\right)$ and radius $r_o$ of a round object as well as the manipulator's current configuration $\boldsymbol{\kappa}_{\textrm{meas}}$, we determine a series of locally optimal manipulator configurations $\boldsymbol{\kappa}_i^* \; \forall i \, = 1..
-numMoves$ that will, if sequentially achieved, bring the manipulator gradually closer to the object while \rkk{any part of the arm is} not touching the object.
+numMoves$ that will, if sequentially achieved, bring the manipulator gradually closer to the object while any part of the arm is not touching the object.
 We refer to these as approach configurations.

### 2015-10-10 robotic_gripper.tex
preparing for submission to soft robotics journal
remove old /rkk comments

@@
 \centering
-   \includegraphics[width=0.50\columnwidth]{figures/robotic_gripper/design_gripper.eps}
+   \includegraphics[width=0.90\columnwidth]{figures/robotic_gripper/design_gripper.eps}
    \caption{The pleated channel designs.
@@
 
-\subsection{\rkk{Lost Wax Fabrication for Fluidic Elastomer Actuators}}
+\subsection{Lost Wax Fabrication for Fluidic Elastomer Actuators}
 Existing soft fluidic manipulators are produced through a multi-step lamination process, which results in weakening seams that can easily delaminate. 
@@
 
-\subsection{\rkk{Multi-segment Arm with Gripper}}
+\subsection{Multi-segment Arm with Gripper}
 

### 2015-10-10 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex
moved reviewer comments to a tex document

\documentclass[letterpaper, 10 pt, twocolumn, conference]{article}

\usepackage[paper=letterpaper,left=19.1mm,right=19.1mm,width=7in,top=19.1mm,bottom=19.1mm]{geometry}

\begin{document}

\title{SoRo Submission: Reply to Reviewer Comments}
\author{Robert Katschmann, Andrew Marchese and Daniela Rus}
\date{October 10th, 2015}
\maketitle

We thank both reviewers for their time and effort to provide us with thoughtful comments. We worked on each point raised by the reviewers and hope that we have a much clearer and improved manuscript. Below we detail how we addressed the reviewers’ concerns. The original reviewer comments are shown in italics, our answers are given underneath.

%\clearpage

\section{Reviewer 1's Comments}

\textit{This paper discusses an autonomous object manipulation algorithm using a soft planar grasping manipulator.}

\subsection{Contribution Discussion}
\textit{Several major issues with the paper hold it back. First, the contribution of the paper seems very minor. A considerable amount of the paper is already covered in the work from [12-14], which involves the design of the robot, the recipe to create the robot, and the whole-arm motion planning. The contribution of this work is the grasping algorithm itself, which is a preplanned sequence of robot curvatures. In light of the whole arm motion planner in [12], this contribution seems minor when adding in a (circular) object.  The algorithm itself is implemented as a state-machine method, and with 4 or 5 states and seems trivial. Only one experimental test is performed to demonstrate the algorithm, and no quantitative error metrics are provided.}

We thank the reviewer for pointing out that the contribution is not clear. The contribution of this paper is an autonomous system for object pick-and-place manipulation that can handle objects of unknown geometry using only soft components to build the manipulator. The griper can pick up arbitrarily shaped objects (compatible with the size of the gripper) placed at arbitrary locations on the work space. 
TODO: We will revise the introduction section to make main contribution clear. We will also adjust the text to highlight the extensive experiments and the novelty.

\textit{For these reasons and especially for the minor contribution that this manuscript offers, I cannot recommend publication as a journal paper in SoRo. The contribution seems better suited for a conference paper submission.}

We believe that the contribution of successfully and repeatedly performing object manipulation using a fully soft, multiple degree of freedom arm is a novel capability. Our feasibility study opens many avenues for soft robotic manipulation. We will revise the introduction to better articulate these ideas.

\subsection{Motion-Capture}
\textit{With a motion-capture system, the problem becomes entirely well-defined.
However, soft robotics are specifically designed to work in confined or constrained environments where constraints and obstacles are unknown, with often no line of sight. Discuss how one might actually implement this without a motion-capture system that picks up the entire configuration of the robot manipulator.
Why does soft robotics systems need to specifically be designed for confined or constrained environments only? How is the use of motion capture systems a well-defined problem and how is it such especially in conjunction with soft robotics? Have others done it before, do you have a reference on this?}

We thank the reviewer for this observation. We used an external localization system in our experiments because localization was not the main point of the contribution. We developed an end-to-end system that can approximately locate an unknown object placed at an unknown location and move it somewhere else. The external localization system is a convenient way to approximately identify the location of the object and visualize/track how the object is moved in the space. We can replace the external localization system with any other method for localizing an object in the workspace. We will revise the exposition to make these points more clear.

\subsection{Suitable contactless/constrained motion?}
\textit{Section 1.1 Last paragraph: “was only suitable for contactless motion” implies that your proposed method solved motion when the robot is constrained by the environment, but it is rather about gripping objects.}
TODO: Read that sentence again and try to understand what this comment means ?????

\subsection{Contribution 1}
\textit{Section 1.2 Contribution 1 seems entirely described in [12] and [13]. Contribution 4 seems obvious that force sensing nor accurate positioning is required to manipulate objects (as discussed in [21]).}

Contribution 1 is different than the contributions in 12 and 13, which focus on planning for the body of the robot. Here we plan for an enveloping grasp of an unknown object in the plane and demonstrate pick-and-place from uncertain locations.

\subsection{System Overview Figure}
\textit{Section 2. System overview, Figure 2: The image is difficult to see and in its current form, and information of the physical frame surrounding the robot seems unnecessary.}

Thank you for this comment. We will revise the figure to make it clear what the system components are. We will be careful about the placement of labels.

\subsection{Fabrication Steps Detailing}
\textit{Section 3.1-3.2 These sections are completely described in [13] and comes off as a recipe to make the manipulator, which is the contribution of [13], and therefore should not be reproduced in the main text. Figure 4 and Table 1. Pulled from [13] seem unnecessary. Furthermore Table 1 does not fit the column.}

Indeed, Reference 13 includes some description of the fabrication steps, but the process described in reference 13 is different; specifically 13 does not describe the fabrication of the manipulator in this paper. We revised the manuscript to discuss the points necessary to allow the reader to reproduce the system.

\subsection{Motion Tracker}
\textit{Section 4.2 par 1., Which motion tracker was used?}
We used the commercially available The Opti-Track System. We will revise the text to make this precise.

\subsection{Optimization Equation}
\textit{Section 4.2 The optimization equation, as I eventually found hidden in Algorithm 1, is difficult to understand: what are parameters v.s. variables, and what is R in the objective function? I suggest writing the equation in the text in full.}

We revised the manuscript to clarify this point.

\subsection{Algorithm Difference}
\textit{I also find it difficult to see exactly the difference between the algorithm presented here and the one in [12]. While grasping is indeed is one objective, that seems to be realized by a curvature objective.}

We thank the reviewer for this comment. We revised the exposition to highlight the differences between the two approaches. The algorithm in [12] is about planning the motion of a soft arm without a gripper through a maze at a centerline while taking the arms bulging shape as a trapezoidal into account. The approach does not work for approaching objects with the manipulator including a gripper, because a tip trajectory for successfully moving towards the object is not known, but needs to be generated. That trajectory needs to avoid pushing the object away with the manipulator trunk when approaching it with the soft gripper at its end. In this paper we present an algorithm for approaching an object by following along concentric lines, which are further and further decreasing in size until object size is achieved. The non-linear optimization is finding tangent poses along these lines using non-linear optimization and then follows down those concentric lines, which implicitly guarantees the arms pose to stay convex – since the circles are convex themselves.

\subsection{Optimization Constraints}
\textit{Section 4.2 Is the optimization function over or underconstrained? Will you always find a solution? What happens if you don’t find a solution?}

The optimization function is only over-constrained if we have to achieve a pose outside of the reachable workspace. Otherwise it is well-constrained. The system optimizes for the quadratic cost of having high curvatures. A solution is not found only if the target object pose is not within the reachable workspace of the arm, that means of the object was placed by the user outside of the workspace. The arm’s workspace can easily be calculated and added this formula to the paper. This workspace check is performed before doing any further calculations.

\subsection{Solver Details}
\textit{Section 4.2 par 1., Provide the speed of the optimization solver as well as the solver used.}

We included this information in the paper.

\subsection{Convexity as Constraint?}
\textit{Section 4.2 par 1. “…while its null space maintains a convex shape, bending away from the object”. Is the convexity actually a hard constraint on the solver? How much does this depend on your specific task and the orientation of the arm/gripper combo?}

When solving for a tangent gripper pose in CCW direction along a concentric circle, this is automatically the constraint for convexity.

\subsection{Algorithm Numbering}
\textit{Section 4.3 The text describing Algorithm 1 would be well suited to have numbered sections that could help the reader understand at which location in the Algorithm the text is referring to.}

We revised the manuscript accordingly.

\subsection{Object Details}
\textit{Section 5.2 What is the object weight? What is the object radius?}

We added info about the sample objects we used in the paper.

\subsection{Task Execution Speed}
\textit{Figure 9: What is the time/speed of the task?}

We added this data to the paper.

\subsection{Additional References}

\textit{Lack of references (Some covered in DeVolder2010):
De Volder, Michaël, and Dominiek Reynaerts. "Pneumatic and hydraulic microactuators: a review." Journal of Micromechanics and microengineering20.4 (2010): 043001.
Ikuta, Koji, Hironobu Ichikawa, and Katsuya Suzuki. "Safety-active catheter with multiple-segments driven by micro-hydraulic actuators." Medical Image Computing and Computer-Assisted Intervention—MICCAI 2002. Springer Berlin Heidelberg, 2002. 182-191.
J. Xiao and R. Vatcha, “Real-time adaptive motion planning for a continuum manipulator,” Proc. IROS 2010, pp. 5919–5926, Oct. 2010.
J. Li and J. Xiao, “A general formulation and approach to constrained, continuum manipulation,” Adv. Robot., no. July 2015, pp. 1–11, 2015.}

Thank you, we added these references to the paper.

%\clearpage

\section{Reviewer 2's Comments}

\textit{This paper covers the fabrication and integration of a new soft robot gripper with a six degree of freedom soft multi-segment arm. The paper also describes a planner for grasping using the integrated system as well as some evaluation of grasping efficacy and the gripper workspace.}

\textit{In general, I think the topic is very interesting and the approach valuable. There seems to be a number of practical limitations to the platform and approach that I would like to see addressed or discussed in the paper. The following are specific feedback that I have:}

\subsection{Uncertainty Characterization}
\textit{For the third contribution listed on page 2 (line 33), I don't agree that you have characterized some of the uncertainty that is rather important. For example, you have shown for the gripper where it can grab for a single set of trials, but you do not describe repeating those trials, which would actually give you measures of uncertainty. Also, the red box used to denote the "bin" for placing the grasped object is an important measure of uncertainty. It seems like if this arm were to actually be used for manipulation, a good measure of uncertainty on positional accuracy would be important.}

Thank you for this comment, we revised the manuscript to highlight the contribution and provide the missing details on the experimentation.

\subsection{Delicate Object Manipulation}
\textit{For the fourth contribution listed on page 2 (about line 37), I don't believe that you have shown (either experimentally or analytically) that you can manipulate delicate objects. I believe it, but you haven't reported gripper forces or extensive trials with delicate objects. I would either perform those tests or rewrite this contribution. It also isn't clear what is meant by "proper manipulation."}

Thank you for this observation, we added the missing details to the paper.

\subsection{Clearer Fabrication Process Description}
\textit{I found the description of the fabrication process for the gripper to be slightly confusing. I think more annotations on figure 3 (such as point 1 or c, etc) and referring to those annotations in the description could make it clearer. Especially since this is listed as a major contribution.}

Figure 3’s point 1 and c were modified according to your suggestion and a note was added to the description in the paper.

\subsection{Distinguishing from Past Work}
\textit{Although you reference past papers from your own group, I think you could do a better job distinguishing from your own past work. Can the process for making the gripper be applied to the multi-segments as well? Which is better for what and why?}

We revised the exposition to clarify this point.

\subsection{Limitations that could be Addressed}
\textit{Many limitations of the hardware or approach should be addressed in the paper. I realize that they cannot all be addressed or discussed. Nor am I asking for you to solve these problems, but an effort could be made to talk about the following:}
See our answers below.

\begin{enumerate}
\item \textit{How would the design of the gripper change if we wanted to grip in both directions? Is it even possible with the current design?}

Two grippers could be mounted next to each other to allow grasping in two directions

\item \textit{Is using motion tracking realistic for some of the scenarios you suggest? I would guess not, but what is the future for state estimation? Existing sensors? Or are new sensors needed?}

Exteroceptive sensing can be replaced by proprioceptive sensing using resistive bend sensors (Reference conference work IROS 2015)

\item \textit{It requires 6 degrees of freedom to achieve a reasonable reachable work space, how does this scale to a full 6 DoF task? Or does it scale? Is it limited to in-plane tasks? What is the reachable work space in the plane with 6 DoF and the + or - 60 degree joint limit?}

We revised the text to clarify this point. The focus here is planar manipulation. Scaling to a 3-dimensional task is not considered in this paper. Our current work considers the 3D case.

\item \textit{Why was a convex shape necessary for approaching a grasp? What if I wanted to approach an object with a different orientation but in the same locations you already looked at?}

Thank you we revised the text to say that the shape needs not be convex. The convex shape approach is a conservative solution to guarantee minimal computation required in solving the planning problem while assuring not to collide.

\item \textit{What is the role of the rollers in carrying your payload? Without the rollers, could the arm not move the object?}

The rollers minimize friction to the surface and therefor minimize frictional forces that need to be overcome. Stick-Slip Frction effects would be greatly increased if arm would be run directly on a surface with non-negligible friction coefficient. We added these details to the text.

\item \textit{Why did you decide to minimize manipulator deformation for your grasp object planner? Furthermore, what if I wanted my plan to follow the shortest distance for the end effector to travel (essentially following the black line in Figure 6), is this even possible given the possible kinematics of the arm?}

Minimized manipulator deformation is a feasible approach, because it is proportional to energy consumed by cylindrical piston drives and it minimizes strain to the actuators and minimizes risk of exerting further than actuation limit of a segment. We added this explanation to the paper.

\end{enumerate}

\subsection{Grammar Comments}
\textit{Overall the paper is well-written, but there are some places with awkward or incorrect grammar. 
Examples include 
1)pg 2 line 37 "soft robots do neither require force sensing nor accurate ..."; 
2)pg 3 line 23 "Those seams are prone to rupture ..." refers to the laminated seams, but that isn't clear from phrasing; 
3)pg 7 line 21 "newly registers every single time the position of the placed object." is confusing.}

Thank you for pointing out these grammar mistakes. We proof read the paper and fixed them.

\subsection{Video Attachement}
\textit{The paper should definitely include a video of operation of the arm. The overlaid figures are very well done, but video would be a valuable contribution to understanding the performance of the system, especially since we have no other time dependent graphs of end effector or joint position.}

Thank you for this suggestion, the video will be attached again to the revised version of the paper.

\subsection{Table 1 Formatting}
\textit{Table 1 needs to be formatted to stay in column}

We adjusted the formatting accordingly.

\subsection{Variable Definitions}
\textit{I feel like many variables could be more clearly defined. Things such as $L_{meas}$, $\phi$, $g_{off}$ (described in algorithm, but still not clear where measured from), $w_{off}$, $L_N$, $\kappa$ (in algorithm 1, not clear if current $\kappa$ or desired or ...), $\kappa_{off}$ (defined in algorithm, but not clear again what it was). Some of these terms are on the diagram in Figure 6, but their definition was still not clear to me. This was especially the case since I'm not sure what the multiple green circles on each concentric circle signified. Some terms were also used but not clearly such as "minimal tip transit distance".}

Thank you for pointing this out. We revised the text accordingly. We added a more explicit description of the variable names into the document. We described in greater detail the figures.

\subsection{Value for $\delta d$}
\textit{Other items were clearly defined, but it wasn't clear how their value was set such as $\delta d$.}

We revised the text to describe how value for delta d was set

\subsection{Object Settling}
\textit{In Section 4.2, what does it mean for an "object to settle?"}

Object settling is defined that the object position has not changed within epsilon for T time. We added this detail to the manuscript.

\subsection{Forward Kinematics}
\textit{The forwKin procedure in algorithm 1 seemed a bit odd. It is recursive and requires calculating the forward kinematics of the previous link, all the way back to the base. That is fine, but the way it is defined, this would happen every time we step forward one link. Is that correct? Why not just use a for loop to be less confusing to a reader and more efficient computationally?}

We revised the text to clarify the forwKin procedure.

\subsection{Picking up Eggs}
\textit{Discussion of picking up eggs in section 5.1 is a bit out of place. Was actual testing done for this? Actually reporting grip forces or pressure would be much more interesting.}

Picking up eggs just as one example for delicate manipulation. We revised the text to make this clear.

\subsection{Uncertainty of User Placement}
\textit{For the trial shown in Figure 7, what was the uncertainty on the user placement of the object? This seems like it could be rather large (compared to the resolution of the discrete placement locations) unless you used the motion capture system somehow.}

The placement by the user was accurate within +-2mm in relation to the discrete placement locations. This test mainly serves as a qualitative measure to show a relation between object size to gripper size to area of successful grasp. We added an explanation to the manuscript.

\subsection{Final Drop Off Location Size}
\textit{How was an appropriate size determined for the red "bin" to determine success? It looks like the spread on placement was about 15 cm. That seems rather large and some commentary on it seems important.}

The red bin is a rectangle that was fit around the final motion after the experiments run to indicate the range wherein the objects were dropped. We added an explanation to the manuscript.

\subsection{Discussion Section in Paper}
\textit{The discussion in section 5.2 led me to have the following questions/comments:}
\begin{enumerate}
\item \textit{What if the object is not round?}

Picking up other objects that have a similar size compared to the round test object does also work. We included the other objects we used in the experiments in the manuscript.

\item \textit{What is the importance of the rate that way points are sent from the planner? Especially failure trials where the arm went unstable seemed to indicate that both the controller and planner may be very dependent on smoothing the desired curvature way points or sending them slowly in time. More detail would be good.}

We revised the manuscript to provide more detail. Specifically, a new waypoint is sent to the controller immediately after arriving within delta epsilon of the previous waypoint, the controllers for each arm segment then compensate for the new delta in angle as quickly as possible to the new pose. That is the PD controller. Smoothing of the trajectory with several intermediate waypoints was found to be necessary. For the given workspace of the arm, we found X intermediate waypoints to be working solution.

\item \textit{ The instability in general seems important and would be nice if it was determined if it was from the planner or controller.}

The instability was identified to come from stick slip friction to the ground, given a roller ball contact that is not continuously smooth. If a segment gets a little bit stuck on the ground, the moment it releases, the soft body releases like a spring and can cause an overshoot, which the controller has to again compensate. Another source of failure is when a marker along the arm gets occluded or merges with an adjacent marker, causing the tracking system loose track of a measured arm segment temporarily and therefore causing the control loop to not close properly. We added a description to the manuscript. 
\end{enumerate}

\subsection{High Dexterity Observation}
\textit{Discussion in conclusion refers to high dexterity when handling delicate objects. However, all of your tests showed approaching the object from more or less the same direction. Do you have a kinematic model or experimental data that shows your manipulator's dexterous workspace? This is similar to a previous comment above.}

Thank you for this observation. We revised the conclusions to remove the high dexterity discussion; instead we describe how widely the arm can be stretched in its various poses to approach the same object.

\end{document}

### 2015-10-11 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex
first round of changes to the manuscript

@@
 \usepackage[paper=letterpaper,left=19.1mm,right=19.1mm,width=7in,top=19.1mm,bottom=19.1mm]{geometry}
+
+\usepackage{natbib}
+\bibliographystyle{plain}
+%\usepackage{section}{placeins}
+
+\newcommand{\unit}[1]{\ensuremath{\, \mathrm{#1}}} %Use this macro to tell \LaTeX that you don’t want your units slanted in math mode.
 
@@
 The original reviewer comments are shown in italics, our answers are given underneath.
+The changes to the manuscript are all indicated by blue color.
 
@@
 The contribution of this paper is an autonomous system for object pick-and-place manipulation that can handle objects of unknown geometry using only soft components to build the manipulator.
-The griper can pick up arbitrarily shaped objects (compatible with the size of the gripper) placed at arbitrary locations on the work space.
+The gripper can pick up arbitrarily shaped objects (compatible with the size of the gripper) placed at arbitrary locations on the work space.
 TODO: We will revise the introduction section to make main contribution clear. We will also adjust the text to highlight the extensive experiments and the novelty.
@@
 Why not just use a for loop to be less confusing to a reader and more efficient computationally?}
-
-We revised the text to clarify the forwKin procedure.
-
+%
+Yes, if only one link is changed, it is more efficient to only update the individual segment's cartesian pose and all the segments following it.
+In fact, our actual implementation does check for this and would then only recalculate the necessary segments.
+The recursive function definition nevertheless makes sense and is efficient.
+In practice, all curvatures are actually constantly changing, both for measuring the curvatures from the tracking system as well as when running the optimization to find a minimal curvature $\kappa$.
+For the system shown in the paper, this algorithmic tweak would not lead to a significant performance increase.
+Furthermore, in order to not complicate the math too much, we decided not to mention this detail of implementation.
+%
 \subsection{Picking up Eggs}
 \textit{Discussion of picking up eggs in section 5.1 is a bit out of place. Was actual testing done for this? Actually reporting grip forces or pressure would be much more interesting.}
-
-Picking up eggs just as one example for delicate manipulation. We revised the text to make this clear.
-
+%
+Picking up eggs is just as one example for a delicate manipulation the gripper actually performed. We revised the text to make this clear:
+The soft manipulator picks up delicate objects such as eggs, shuttlecocks or bakery items without squishing or breaking those. 
+We also addressed the point of the gripping forces by adding:
+It was shown in \cite{marchese2015recipe} that pleated grippers of similar dimensions like the one used in this work can exert a continuous spectrum of blocking force in the range of 0-2\unit{N} at a pressure range of 0-60\unit{kPa}.
+Grasping delicate objects should therefore be possible with the soft manipulator.
+%
 \subsection{Uncertainty of User Placement}
@@
 This seems like it could be rather large (compared to the resolution of the discrete placement locations) unless you used the motion capture system somehow.}
-
-The placement by the user was accurate within +-2mm in relation to the discrete placement locations.
-This test mainly serves as a qualitative measure to show a relation between object size to gripper size to area of successful grasp.
-We added an explanation to the manuscript.
-
+%
+The grid paper and fine markings on all four sides of the round object ensure that the placement by the user is accurate within $\pm$1\unit{mm} in relation to the discrete placement locations.
+This test serves as a qualitative measure to show a relation between object size to gripper size to area of successful grasp..
+We added this explanation to the manuscript.
+%
 \subsection{Final Drop Off Location Size}
@@
 That seems rather large and some commentary on it seems important.}
-
-The red bin is a rectangle that was fit around the final motion after the experiments run to indicate the range wherein the objects were dropped. We added an explanation to the manuscript.
-
+%
+We added an explanation in the "Repeated Grasp Experiments" section: For these experiments, we focus on showing the capability of picking up objects at various places and moving them around, there is no emphasis set on having to drop off the object at a specific pose.
+To indicate that the arm can move the object after grasping, the arm was controlled to go back to the fully straight pose.
+When it got fairly close to that final straight pose within a large allowable delta, the gripper was set to release and drop the object.
+It was not ensured by the planner that the arm had to first settle to zero velocity at the final straight pose.
+As a consequence of this, the experimental data indicates as a red bin a relatively wide drop off area.
+%
 \subsection{Discussion Section in Paper}
@@
 \item \textit{What if the object is not round?}
-
+%
 Picking up other objects that have a similar size compared to the round test object does also work. We included the other objects we used in the experiments in the manuscript. 
-
+%
 \item \textit{What is the importance of the rate that way points are sent from the planner?
@@
 More detail would be good.}
-
+%
 We revised the manuscript to provide more detail.
-Specifically, a new waypoint is sent to the controller immediately after arriving within delta epsilon of the previous waypoint, the controllers for each arm segment then compensate for the new delta in angle as quickly as possible to the new pose.
-That is the PD controller.
-Smoothing of the trajectory with several intermediate waypoints was found to be necessary.
-For the given workspace of the arm, we found X intermediate waypoints to be working solution.
-
+Specifically, a smoothing of the complete trajectory with several intermediate waypoints was found to be necessary.
+The amount of intermediate waypoints is determined by the variable $\delta d$, which we found empirically to be 5\unit{cm}, around half the length of the gripper.
+A new waypoint is sent to the controller immediately after arriving within a small delta of the previous waypoint, the controllers for each arm segment then compensate for the new delta in curvature as quickly as possible to get to the new pose $\kappa_i^*$.
+%
 \item \textit{ The instability in general seems important and would be nice if it was determined if it was from the planner or controller.}
-
-The instability was identified to come from stick slip friction to the ground, given a roller ball contact that is not continuously smooth.
-If a segment gets a little bit stuck on the ground, the moment it releases, the soft body releases like a spring and can cause an overshoot, which the controller has to again compensate.
-Another source of failure is when a marker along the arm gets occluded or merges with an adjacent marker, causing the tracking system loose track of a measured arm segment temporarily and therefore causing the control loop to not close properly.
-We added a description to the manuscript.
+%
+We discuss this point now in the "Experimental Insights and Limitations" section.
+The instabilities observed in the unsuccessful trials could in general be fixed by loosening the constraints on the planner.
+The planner could allow the arm controller to have the arm pass over each intermediate waypoint without having to get to a full stop within an arbitrarily chosen delta of curvature values.
+The planner could take as a measure of progress a decreasing cartesian distance of the gripper to its final target pose.
+It is worth mentioning that the exteroceptive tracking system has the disadvantage that an occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment.
+In that case, the control loop can not function properly until the occlusion disappears.
+Proprioceptive sensors within the segments can solve this issue.
+%
 \end{enumerate}
@@
 This is similar to a previous comment above.}
-
+%
 Thank you for this observation.
 We revised the conclusions to remove the high dexterity discussion; instead we describe how widely the arm can be stretched in its various poses to approach the same object.
-
+We also describe how future work could investigate the dexterity of the arm when approaching the same object pose in various ways, just by changing the constraints and cost function when optimizing for the inverse kinematics solution.
+%
+\bibliography{../katzschmann2015autonomous}
+%
 \end{document}

### 2015-10-11 conclusion.tex
first round of changes to the manuscript

@@
 Such a homogeneous soft segment is less prone to rupture and to manufacturing inconsistencies, and would therefore allow for better robot performance.
-x
+
 The results presented in this paper suggest that despite their extreme compliance, soft robots are capable of repeatable object manipulation while simultaneously providing inherently safe interactions with their environment.
@@
 We demonstrated the ability of an entirely soft manipulator to autonomously grasp an object, which leads to many potential applications.
-In a manufacturing setting, this could resemble a soft robot executing tasks requiring high dexterity when handling delicate objects.
+\rkk{In a manufacturing setting, this could resemble a soft robot stretched widely to pick up objects situated at various locations.}
+\rkk{Future work could investigate the dexterity of the arm when approaching the same object pose in various ways, just by changing the constraints and cost function when optimizing for the inverse kinematics solution.}
 In a human-centric environment, soft arm grasping manipulation may enable soft robots to interact safely with humans.

### 2015-10-11 experimental_results.tex
first round of changes to the manuscript

@@
 \subsection{Grasping Delicate Objects}
-The soft manipulator can pick up eggs and other delicate objects without breaking them. 
+\rkk{It was shown in \cite{marchese2015recipe} that pleated grippers of similar dimensions like the one used in this work can exert a continuous spectrum of blocking force in the range of 0-2\unit{N} at a pressure range of 0-60\unit{kPa}.
+Grasping delicate objects should therefore be possible with the soft manipulator.}
+The manipulator in fact picks up delicate objects \rkk{such as eggs, shuttlecocks or bakery items} without \rkk{squishing} or breaking those. 
 Figure~\ref{fig:egg_approach_sequence} shows how the manipulator approaches and grasps an egg.
@@
 The evaluation of the capture region is performed similarly to a method described in Dogar and Srinivasa\cite{dogar2010push} work on determining capture regions for a push-grasp of a classical robotic gripper.
+\rkk{Grid paper and fine markings on all four sides of the round object ensure that the placement by the user is accurate within $\pm$1\unit{mm} in relation to the discrete placement locations on the grid.
+This test serves as a qualitative measure to show a relation between object size to gripper size to area of successful grasp.}
 Despite positioning inaccuracies of the soft manipulator, the gripper can nevertheless successfully perform a grasp of an object.
 
-When the arm reaches the red bin location, it drops the object.
+When the arm reaches \rkk{its straight pose within a relatively large delta}, it drops the object.
+\rkk{For these experiments, we focus on showing the capability of picking up objects at various places and moving them around, there is no emphasis set on having to drop off the object at a specific pose.
+To indicate that the arm can move the object after grasping, the arm was controlled to go back to the fully straight pose.
+When it got fairly close to that final straight pose within a large allowable delta, the gripper was set to release and drop the object.
+It was not ensured by the planner that the arm had to first settle to zero velocity at the final straight pose.
+As a consequence of this, the experimental data indicates as a red bin a relatively wide drop off area.}
 
@@
 Our kinematic modeling does not account for this non-linear behavior, which acts as a disturbance and can lead to failure to arrive at the next waypoint.
-To be more specific, in one of the trials, the robot slowed down too much before it almost reached its next waypoint and because of friction the arm got to a full stop. 
+To be more specific, in one of the trials, the robot slowed down too much before it almost reached its next waypoint and because of friction the arm halted to a full stop. 
 The proportional gain of the curvature controller was not able to compensate for that small positional delta and since the relatively low saturation level of the integrator portion of the controller was saturated, the arm did not move to the next waypoint pose.
@@
 The workspace of the manipulator is limited to the top and left by the maximal extension length of the arm, and to the bottom by the maximum bending curvature, which the arm can achieve without over-actuating a single segment.
+\rkk{The gripper presented can not only pick up a round object, but also more arbitrarily shaped objects of similar size, for example a star-shaped object, a tape holder, a shuttlecock or an egg.}
 Objects were only grasped within the left quadrant of the arm, because of the gripper orientation and an upright initial starting pose.
+\rkk{A smoothing of the complete trajectory with several intermediate waypoints was found to be necessary.
+The amount of intermediate waypoints is determined by the variable $\delta d$, which we found empirically to be 5\unit{cm}, around half the length of the gripper.
+A new waypoint is sent to the controller immediately after arriving within a small delta of the previous waypoint, the controllers for each arm segment then compensate for the new delta in curvature as quickly as possible to get to the new pose $\kappa_i^*$.}
+\rkk{The instabilities observed in the unsuccessful trials could be solved by loosening the constraints on the planner.
+The planner could allow the arm controller to have the arm pass over each intermediate waypoint without having to get to a full stop within an arbitrarily chosen delta of curvature values.
+The planner could take as a measure of progress a decreasing cartesian distance of the gripper to its final target pose.}
+\rkk{It is worth mentioning that the exteroceptive tracking system has the disadvantage that an occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment.
+In that case, the control loop can not function properly until the occlusion disappears.
+Proprioceptive sensors within the segments can solve this issue.}
 

### 2015-10-11 introduction.tex
first round of changes to the manuscript

@@
 \subsection{Contributions}
-This work differs from the previous work in that we %create an entirely soft and autonomously controlled \emph{grasping} manipulation system. 
-do not attach a novel soft gripper to a hard arm nor do we move the gripper around manually, but we rather take on the challenge of grasping-and-placing objects with a seven degrees of freedom planar arm made entirely from soft rubber.
+This work differs from the previous work in that we \rkk{create an entirely soft and autonomously controlled \emph{grasping} manipulation system. 
+We} do not attach a novel soft gripper to a hard arm nor do we move the gripper around manually, but we rather take on the challenge of grasping-and-placing objects with a seven degrees of freedom planar arm made entirely from soft rubber.
 We provide in this work the following contribution to soft robotics:

### 2015-10-11 robotic_gripper.tex
first round of changes to the manuscript

@@
 1 & Ecoflex 0030&  Smooth-On\\
-2 & AL Cube & Abbess Instruments and Systems, Inc.\\
+2 & AL Cube & Abbess Instr. and Sys., Inc.\\
 3 & Mold Star 15 & Smooth-On\\

### 2015-10-11 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex
fixed variable problems

@@
 
+\usepackage{amsmath, amssymb, graphics, setspace}
 \usepackage[paper=letterpaper,left=19.1mm,right=19.1mm,width=7in,top=19.1mm,bottom=19.1mm]{geometry}
@@
 The overlaid figures are very well done, but video would be a valuable contribution to understanding the performance of the system, especially since we have no other time dependent graphs of end effector or joint position.}
-
+%
 Thank you for this suggestion, the video will be attached again to the revised version of the paper.
-
+%
 \subsection{Table 1 Formatting}
 \textit{Table 1 needs to be formatted to stay in column}
-
+%
 We adjusted the formatting accordingly.
-
+%
 \subsection{Variable Definitions}
-\textit{I feel like many variables could be more clearly defined.
-Things such as $L_{meas}$, $\phi$, $g_{off}$ (described in algorithm, but still not clear where measured from), $w_{off}$, $L_N$, $\kappa$ (in algorithm 1, not clear if current $\kappa$ or desired or ...), $\kappa_{off}$ (defined in algorithm, but not clear again what it was).
+\textit{I feel like many variables could be more clearly defined. Things such as $L_{meas}$, $\phi$, $g_{off}$ (described in algorithm, but still not clear where measured from),}
+%
+Thank you for pointing all this out. We added clearer descriptions to the text and more indications in figure 5 and figure 6 to clarify these variables.
+%
+\textit{$w_{off}$, $L_N$, $\kappa$ (in algorithm 1, not clear if current $\kappa$ or desired or ...),}
+%
+We added: The end effector offset $\mathbf{w}_{\textrm{off}}$ describes the distance from the root of the gripper, to an offset point close to the lower end of the gripper's palm.
+It is visualized in the top left corner of Fig.
+5.
+We also added to the manuscript: The arc length input to the arm's forward kinematics is the $N$-th element of the segment lengths $\mathbf{L}_{\textrm{meas}}$.
+%
+We assume that it is clear 
+$\kappa$ is the variable being optimized for in $\underset{\phi, \, \boldsymbol{\kappa}}{\text{min}}$
+%
+\textit{$\kappa_{off}$ (defined in algorithm, but not clear again what it was).
 Some of these terms are on the diagram in Figure 6, but their definition was still not clear to me.
@@
 Some terms were also used but not clearly such as "minimal tip transit distance".}
+%
+$\kappa_{off}$  is now better defined by: "measured manipulator configuration at start". We also clarified the meaning of the \emph{green} circles in the text.
+%
 
-Thank you for pointing this out. We revised the text accordingly. We added a more explicit description of the variable names into the document. We described in greater detail the figures.
-
+%
 \subsection{Value for $\delta d$}
@@
 \textit{In Section 4.2, what does it mean for an "object to settle?"}
-
-Object settling is defined that the object position has not changed within epsilon for T time. We added this detail to the manuscript.
-
+%
+We consider the object to have settled if it has not moved for 2\unit{s}. We added this sentence to the manuscript.
+%
 \subsection{Forward Kinematics}

### 2015-10-11 processing_control.tex
first round of changes to the manuscript
fixed variable problems

@@
 The outputs from this block are the representations of the measured manipulator configuration: $\boldsymbol{\kappa}_{\textrm{meas}}$ and $\mathbf{L}_{\textrm{meas}}$.
+\rkk{Each segment of the manipulator is described by its measured curvature $\kappa_{\textrm{meas}}$ and its segment length $L_{\textrm{meas}}$}.
 This work expands on the previously developed cascaded closed-loop curvature controller, whose input is target curvatures $\boldsymbol{\kappa}_{\textrm{target}}$ and whose output is the controlled adjustment of a fluidic drive cylinder array to resolve the error between $\boldsymbol{\kappa}_{\textrm{target}}$ and $\boldsymbol{\kappa}_{\textrm{meas}}$.
@@
 A motion tracker constantly captures the position of the object and passes it along to a routine, which checks for the object to settle.
+\rkk{We consider the object to have settled if it has not moved by more than a small $\epsilon$ for 2\unit{s}}.
 After it has settled, the Grasp Object Planner receives the coordinates and radius of the settled object and together with the current curvature values of the arm and gripper, it solves a series of constrained nonlinear optimization problems to generate end-effector poses approaching the object.
@@
 A fundamental component of the grasp-and-place system is its ability to plan a feasible approach motion to the object.
-That is, given the location $\left(x_o, \, y_o\right)$ and radius $r_o$ of a round object as well as the manipulator's current configuration $\boldsymbol{\kappa}_{\textrm{meas}}$, we determine a series of locally optimal manipulator configurations $\boldsymbol{\kappa}_i^* \; \forall i \, = 1..
+That is, given the location $\left(x_o, \, y_o\right)$ and radius $r_o$ of a round object as well as the manipulator's current configuration $\boldsymbol{\kappa}_{\textrm{meas}}$ \rkk{and segment lengths $\mathbf{L}_{\textrm{meas}}$}, we determine a series of locally optimal manipulator configurations $\boldsymbol{\kappa}_i^* \; \forall i \, = 1..
 numMoves$ that will, if sequentially achieved, bring the manipulator gradually closer to the object while any part of the arm is not touching the object.
+
 We refer to these as approach configurations.
@@
 numMoves$ that define concentric circles shrinking from the manipulator's starting tip pose towards the center of the object.
-Given actuator limits, we then search for a series of feasible manipulator configurations $\boldsymbol{\kappa}_i^*$ that will place the robot's end-effector on these circles, parameterized by $r_a$ and $\phi$, while minimizing manipulator deformation.
+Given actuator limits, we then search for a series of feasible manipulator configurations $\boldsymbol{\kappa}_i^*$ that will place the robot's end-effector on these \rkk{green} circles, parameterized by $r_a$ and $\phi$, while minimizing manipulator deformation.
 
@@
    \includegraphics[width=0.85\columnwidth, trim = 0mm 0mm 5mm 5mm, clip]{Figures/processing_control/grasp_object_planner.eps}
-   \caption{Visualzation of the Grasp Object Planner.
+   \caption{Visualization of the Grasp Object Planner.
 Concentric approach circles are shown in \emph{green} and are centered about the object shown in \emph{cyan}.
@@
   $\boldsymbol{\kappa}_{\textrm{meas}}$, $\mathbf{L}_{\textrm{meas}}$ $\gets$ measured arm configuration \;
-  $\boldsymbol{\kappa}_{\textrm{off}}$ $\gets$ bias configuration offset at start \;
+  $\boldsymbol{\kappa}_{\textrm{off}}$ $\gets$ \rkk{measured manipulator} configuration at start \;
   $g_{\textrm{off}}$ $\gets$ gripper offset normal to end-effector\;
@@
 The procedure first determines the manipulator's current tip pose $\mathbf{w}_t$ and the Euclidean distance $d_1$ between the tip and the object's center. 
+\rkk{The arc length input to the arm's forward kinematics is the $N$-th element of the segment lengths $\mathbf{L}_{\textrm{meas}}$.}
 Next, considering the object's radius $r_o$ and the gripper normal offset $\mathbf{g}_{\textrm{off}}$, the minimal tip transit distance $d_2$ is calculated. 
-$\mathbf{g}_{\textrm{off}}$ is the component of the end effector offset $\mathbf{w}_{\textrm{off}}$, which is normal to the end effector orientation. 
+\rkk{The end effector offset $\mathbf{w}_{\textrm{off}}$ describes the distance from the root of the gripper, to an offset point close to the lower end of the gripper's palm.
+It is visualized in the top left corner of Fig.~\ref{fig:grasp-and-place-planner}.}
+\rkk{The length} $\mathbf{g}_{\textrm{off}}$ represents the component of the end effector offset $\mathbf{w}_{\textrm{off}}$, which is normal to the end effector orientation. 
 Also, the number of approach configurations $numMoves$ is determined as $\lfloor \frac{d_2}{\Delta d} \rfloor$, where $\Delta d$ is an allowable incremental distance. 

### 2015-10-11 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex
delta d comment

@@
 %
-\subsection{Value for $\delta d$}
-\textit{Other items were clearly defined, but it wasn't clear how their value was set such as $\delta d$.}
-
-We revised the text to describe how value for delta d was set
-
+\subsection{Value for $\Delta d$}
+\textit{Other items were clearly defined, but it wasn't clear how their value was set such as $\Delta d$.}
+%
+To address this question, we added to the "Experimental Insights and Limitations section" this sentence: 
+The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found empirically to be 5\unit{cm}, around half the length of the gripper.
+%
 \subsection{Object Settling}

### 2015-10-11 experimental_results.tex
delta d comment

@@
 \rkk{A smoothing of the complete trajectory with several intermediate waypoints was found to be necessary.
-The amount of intermediate waypoints is determined by the variable $\delta d$, which we found empirically to be 5\unit{cm}, around half the length of the gripper.
+The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found empirically to be 5\unit{cm}, around half the length of the gripper.
 A new waypoint is sent to the controller immediately after arriving within a small delta of the previous waypoint, the controllers for each arm segment then compensate for the new delta in curvature as quickly as possible to get to the new pose $\kappa_i^*$.}

### 2015-10-11 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex
fixed grammar mistakes

@@
 The rollers minimize friction to the surface and therefor minimize frictional forces that need to be overcome.
-Stick-Slip Frction effects would be greatly increased if arm would be run directly on a surface with non-negligible friction coefficient.
+Stick-Slip Friction effects would be greatly increased if arm would be run directly on a surface with non-negligible friction coefficient.
 We added these details to the text.
@@
 \end{enumerate}
-
+%
 \subsection{Grammar Comments}
 \textit{Overall the paper is well-written, but there are some places with awkward or incorrect grammar. 
-Examples include 
-1)pg 2 line 37 "soft robots do neither require force sensing nor accurate ..."; 
-2)pg 3 line 23 "Those seams are prone to rupture ..." refers to the laminated seams, but that isn't clear from phrasing; 
-3)pg 7 line 21 "newly registers every single time the position of the placed object." is confusing.}
-
-Thank you for pointing out these grammar mistakes. We proof read the paper and fixed them.
-
+Examples include}
+Thank you for pointing out these grammar mistakes. We made the following changes:
+\begin{enumerate}
+\item \textit{pg 2 line 37 "soft robots do neither require force sensing nor accurate ...";}
+%
+Replaced by: "Demonstrating that soft robots allow for proper autonomous manipulation of delicate objects without requiring force sensing or accurate positioning."
+%
+\item \textit{pg 3 line 23 "Those seams are prone to rupture ..." refers to the laminated seams, but that isn't clear from phrasing;}
+%
+Replaced by: "Fabrication techniques based on the lamination of several cast rubber pieces lead to more manufacturing inconsistencies due to slight misalignments of layers. 
+We observed that soft actuators built this way tend to rupture more easily at their weakening seams."
+%
+\item \textit{pg 7 line 21 "newly registers every single time the position of the placed object." is confusing.}
+%
+Replaced by: " The user's placing accuracy is not important to the algorithm, since the tracking system newly registers the position of the object every time it is placed."
+%
+\end{enumerate}
+%
 \subsection{Video Attachement}
@@
 $\kappa_{off}$  is now better defined by: "measured manipulator configuration at start". We also clarified the meaning of the \emph{green} circles in the text.
-%
-
 %

### 2015-10-11 experimental_results.tex
fixed grammar mistakes

@@
 The markers only serve as a reference point for the user to place the object roughly at the same point at every repetition.
-The user's placing accuracy is not important to the algorithm, the tracking system newly registers every single time the position of the placed object.
+The user's placing accuracy is not important to the algorithm, \rkk{since the tracking system newly registers the position of the object every time it is placed.}
 The five points were chosen to approximately represent the major portion of the manipulator's reachable workspace.

### 2015-10-11 introduction.tex
fixed grammar mistakes

@@
   %\item End-effector control of the grasping manipulator attached to a soft arm using a motion tracking system.
-  \item Demonstrate that soft robots do neither require force sensing nor accurate positioning to allow for proper manipulation of delicate objects. 
+  \item \rkk{Demonstrating that soft robots allow for proper autonomous manipulation of delicate objects without requiring force sensing or accurate positioning.} 
 \end{itemize}

### 2015-10-11 robotic_gripper.tex
fixed grammar mistakes

@@
 Using this approach, the \emph{cyan} portion of the pleated gripper can be cured in a single step, avoiding any weakening seams due to lamination.
-Those seams are prone to rupture and manufacturing inconsistencies.
+\rkk{Fabrication techniques based on the lamination of several cast rubber pieces lead to more manufacturing inconsistencies due to slight misalignments of layers. 
+We observed that soft actuators built this way tend to rupture more easily at their weakening seams.}
 

### 2015-10-11 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex
reviewer comments all handeled except for limitations

@@
 It seems like if this arm were to actually be used for manipulation, a good measure of uncertainty on positional accuracy would be important.}
-
-Thank you for this comment, we revised the manuscript to highlight the contribution and provide the missing details on the experimentation.
-
+%
+Thank you for this comment.
+The capture region characterization was performed three times, always yielding to the same capture region given the grid size.
+The intent of this experiment was to qualitatively describe a relation between object size to gripper size to area of successful grasp.
+We revised the manuscript to properly phrase the contribution and provide the missing details on the experimentation.
+%
 \subsection{Delicate Object Manipulation}
@@
 It also isn't clear what is meant by "proper manipulation."}
-
+%
 Thank you for this observation, we added the missing details to the paper.
-
+We rewrote the Grasping delicate objects section to provide more detail on what delicate objects have been successfully grasped, pointing out that the egg is just one example.
+We also describe how blocking force and pressures have been analyzed for the gripper and how the small range .
+%
 \subsection{Clearer Fabrication Process Description}
@@
 Especially since this is listed as a major contribution.}
-
-Figure 3’s point 1 and c were modified according to your suggestion and a note was added to the description in the paper.
-
+%
+Figure 3’s point 1 and c were modified according to your suggestion and more descriptive note were added to the fabricationg figure and the description in the paper.
+%
 \subsection{Distinguishing from Past Work}
@@
 Which is better for what and why?}
-
-We revised the exposition to clarify this point.
-
+%
+We revised the exposition to clarify this point. We added to the Lost Wax Fabrication section theses sentences:
+"The retractable pin fabrication for uniform lateral channels, first introduced in reference [12], does not cause weakening seams to the actuator, but it also does not allow for cavities more complicated than cylindrical shapes.
+This is why we propose the application of lost-wax casting to the fabrication of soft fluidic actuators like a gripper."
+Later in the multi-segment arm section, we also added:
+"The cylindrical segments of the arm are fabricated through a retractable pin fabrication technique, which does not require lost wax cores because of their simple cylindrical cavities."
+%
 \subsection{Limitations that could be Addressed}

### 2015-10-11 experimental_results.tex
reviewer comments all handeled except for limitations

@@
 \subsection{Grasping Delicate Objects}
-\rkk{It was shown in \cite{marchese2015recipe} that pleated grippers of similar dimensions like the one used in this work can exert a continuous spectrum of blocking force in the range of 0-2\unit{N} at a pressure range of 0-60\unit{kPa}.
-Grasping delicate objects should therefore be possible with the soft manipulator.}
+\rkk{It was shown in \cite{marchese2015recipe} that pleated grippers of similar dimensions like the one used in this work can be contiuously actuated in a pressure range of 0-60\unit{kPa} and create blocking forces in the range of 0-2\unit{N}.
+This fine actuation range and the fact that soft manipulators easily conform to shapes implies that grasping delicate objects should be possible.}
 The manipulator in fact picks up delicate objects \rkk{such as eggs, shuttlecocks or bakery items} without \rkk{squishing} or breaking those. 
-Figure~\ref{fig:egg_approach_sequence} shows how the manipulator approaches and grasps an egg.
+Figure~\ref{fig:egg_approach_sequence} shows \rkk{for example} how the manipulator approaches and grasps an egg.
 Delicate objects can be manipulated without requiring a shape or a force sensor within its structure, since the compliant gripper body conforms to the object.
@@
 The capture region is shown in grey in Figure~\ref{fig:grasp_uncertainty}.
+
 The evaluation of the capture region is performed similarly to a method described in Dogar and Srinivasa\cite{dogar2010push} work on determining capture regions for a push-grasp of a classical robotic gripper.
 \rkk{Grid paper and fine markings on all four sides of the round object ensure that the placement by the user is accurate within $\pm$1\unit{mm} in relation to the discrete placement locations on the grid.
-This test serves as a qualitative measure to show a relation between object size to gripper size to area of successful grasp.}
+This test serves as a qualitative measure to show qualitatively a relation between object size to gripper size to area of successful grasp.}
+\rkk{This characterization was repeated two times, resulting always in the same capture region.}
 Despite positioning inaccuracies of the soft manipulator, the gripper can nevertheless successfully perform a grasp of an object.

### 2015-10-11 introduction.tex
reviewer comments all handeled except for limitations

@@
 \begin{itemize}
-  \item A soft manipulator consisting of a multi-segment arm with a gripper to enable fully compliant planar grasping.
+  \item A \rkk{controllable} soft manipulator consisting of a multi-segment arm with a gripper to enable fully compliant planar grasping.
   \item A planning algorithm to grasp-and-place randomly positioned objects on a planar surface using a 7 DOF soft manipulator.  
-  \item Repeatable successful grasping demonstrations with a physical prototype and an experimental characterization of the uncertainty regions that can be tolerated by the soft gripper.
+  \item Repeatable successful grasping demonstrations with a physical prototype and a \rkk{qualitative} experimental characterization of the uncertainty regions that can be tolerated by the soft gripper.
   %\item End-effector control of the grasping manipulator attached to a soft arm using a motion tracking system.

### 2015-10-11 robotic_gripper.tex
reviewer comments all handeled except for limitations

@@
 \label{sec:soft_grasping_manipulator}
-%The robotic manipulator is composed of multiple bidirectional planar arm segments and combined with a unidirectional soft gripper.
+\rkk{The robotic manipulator is composed of multiple bidirectional planar arm segments and combined with a unidirectional soft gripper.}
 %We first introduce the previously developed uniform channel design, which is used for the soft body arm segments.
 %Following this, 
-We describe briefly the design, fabrication and functionality of the soft grasping manipulator. Further details on the design and fabrication can be found in \cite{marchese2015recipe}.
+We describe briefly the design, fabrication and functionality of this soft grasping manipulator. Further details on the design and fabrication can be found in \cite{marchese2015recipe}.
 
 %\subsection{Uniform Channel Design of the Soft Arm}
-
-\begin{figure}[thpb]
-\centering
-   \includegraphics[width=0.90\columnwidth]{figures/robotic_gripper/design_gripper.eps}
-   \caption{The pleated channel designs.
-(\textbf{A}) depicts the segment in an unactuated state and (\textbf{B}) shows the segment in an actuated and therefore bent state.
-The expansion of the pressurized channels are schematically represented.}
-   \label{fig:design}
-\end{figure}
-
+%Several existing body segment morphologies are serpentine channels \cite{correll2010soft, marchese2014design}, uniform lateral channels \cite{marchese2014whole}, and pleated channels \cite{polygerinos2013towards, mosadegh2014pneumatic}.
+%The serpentine channel design with its multiple vertical channels was first characterized by Correll et al.\cite{correll2010soft} and Onal et al.\cite{onal2011soft} and called a fluidic elastomer actuator.
 %Several existing body segment morphologies are serpentine channels \cite{correll2010soft, marchese2014design}, uniform lateral channels \cite{marchese2014whole}, and pleated channels \cite{polygerinos2013towards, mosadegh2014pneumatic}.
@@
 
+\begin{figure}[thpb]
+\centering
+   \includegraphics[width=0.90\columnwidth]{figures/robotic_gripper/design_gripper.eps}
+   \caption{The pleated channel designs.
+(\textbf{A}) depicts the segment in an unactuated state and (\textbf{B}) shows the segment in an actuated and therefore bent state.
+The expansion of the pressurized channels are schematically represented.}
+   \label{fig:design}
+\end{figure}
+
 \subsection{Pleated Channel Design for the Gripper}
@@
 This limits their range of applications and lifetime.
+\rkk{The retractable pin fabrication for uniform lateral channels, first introduced in \cite{marchese2014whole}, does not cause weakening seams to the actuator, but it also does not allow for cavities more complicated than cylindrical shapes.}
 This is why we propose the application of lost-wax casting to the fabrication of soft fluidic actuators like a gripper.
@@
 \centering
-   \includegraphics[width=0.98\columnwidth]{figures/robotic_gripper/fab_pleated_process_horizontal_no_labels.eps}
+   \includegraphics[width=0.98\columnwidth]{figures/robotic_gripper/fabrication_new.eps} %fab_pleated_process_horizontal_no_labels.eps
       \caption{Gripper fabrication process.
-(\textbf{A}) Pour and cure a rubber mold, (\textbf{B}) pour wax core with embedded supportive rod, (\textbf{C}) combine bottom mold, top mold and wax core using pins, (\textbf{D}) pour rubber into assembled mold, (\textbf{E}) pour stiffer rubber on top of the cured gripper to form a constraint layer, (\textbf{F}) remove cured gripper from mold, (\textbf{G}) using an oven melt out wax core from the gripper, and (\textbf{H}) add silicone tubing and plug using silicone sealant.}
+(\textbf{A}) Pour and cure a rubber mold \rkk{(blue)}, (\textbf{B}) pour wax core \rkk{(yellow)} with embedded supportive rod \rkk{(brown)}, (\textbf{C}) combine bottom mold \rkk{(green)}, top mold \rkk{(grey)} and wax core using pins, (\textbf{D}) pour \rkk{softer} rubber \rkk{(light green)} into assembled mold, (\textbf{E}) pour stiffer rubber \rkk{(blue)} on top of the cured gripper \rkk{(light green)} to form a constraint layer, (\textbf{F}) remove cured gripper from mold, (\textbf{G}) using an oven melt out wax core from the gripper, and (\textbf{H}) add silicone tubing and plug using silicone sealant.
+\rkk{Reproduced from \cite{marchese2015recipe}.}}
       \label{fig:fabrication}
@@
 
-In step (A), harder silicone rubber$^6$ is poured into a mold, which contains a printed model of the wax core.
+In step (A), harder silicone rubber$^6$ is poured into a mold, which contains a 3D-printed model of the wax core.
 In preparation for step (B), the model is removed and the rubber mold is left inside the outer mold.
-A rigid rod is used as a supportive inlay inside the wax core.
+A rigid rod is \rkk{embedded} as a supportive inlay inside the wax core.
 The rod is laid into the cavity of the rubber mold, supported on both ends by the outer mold.
 This ensures that the wax core does not break when removed from the rubber mold.
-%Mold release spray is applied to the silicone rubber mold to ease the wax core removal process.
+\rkk{Mold release spray is applied to the silicone rubber mold to ease the wax core removal process.}
 The bees-wax$^{7}$ is heated up until it becomes fully liquefied.
@@
 
-The design for our arm consisting of soft cylindrical segments was described in \cite{marchese2014whole}.
+The design for the arm consisting of soft cylindrical segments was described in \cite{marchese2014whole}.
+ \rkk{The cylindrical segments of the arm are fabricated through a retractable pin fabrication technique, which does not require lost wax cores because of their simple cylindrical cavities.} 
 Each cylindrical segment can only be actuated up to a bend angle of less than $60^\circ$, therefore several segments have to be combined together to allow the arm to reach a large enough workspace to perform proper manipulation tasks on a plane.
-Our cylindrical design with its hollow channel in the center has enough space to accomodate for pneumatic tubes to connect to all six cylindrical segments and additionally to the pleated gripper, which is attached to the tip.
+The cylindrical design with its hollow channel in the center has enough space to accommodate for pneumatic tubes to connect to all six cylindrical segments and additionally to the pleated gripper, which is attached to the tip.
 The pleated gripper has to be appropriately sized, just big enough to allow for proper manipulation without exceeding the payload capacity of the soft arm.
@@
 Those cylinders are driven by a linear actuator and controlled through a motor controller, which takes its command signals from a higher-level curvature controller. 
-The modeling and design of these are described in \cite{marchese2014design}.
+The design of these cylindrical actuators is given in \cite{marchese2014design}.

### 2015-10-11 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex
finished reviewer 2's comments

@@
 See our answers below.
-
+%
 \begin{enumerate}
 \item \textit{How would the design of the gripper change if we wanted to grip in both directions? Is it even possible with the current design?}
-
-Two grippers could be mounted next to each other to allow grasping in two directions
-
+%
+We added to the limitations discussion in the manuscript:
+"The experiments were only performed for picking up objects on the left quadrant of the manipulator. Grasping objects in both directions could be achieved in various ways by 
+\begin{enumerate}
+\item increasing the reachable workspace through starting the soft arm at an extreme curvature configuration within the right quadrant,
+\item replacing the large gripper with two smaller grippers next to each other at the end of the arm, 
+\item mounting roller supports on the top face of the manipulator and then rotating the manipulator at its root by $180^{\circ}$."  
+\end{enumerate}
+%
 \item \textit{Is using motion tracking realistic for some of the scenarios you suggest? I would guess not, but what is the future for state estimation? Existing sensors? Or are new sensors needed?}
-
-Exteroceptive sensing can be replaced by proprioceptive sensing using resistive bend sensors (Reference conference work IROS 2015)
-
+%
+We added:
+"It is worth mentioning that the exteroceptive tracking system has the disadvantage that a full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment.
+In that case, the control loop can not function properly until the occlusion disappears.
+Proprioceptive sensors within the segments can solve this issue.
+A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in reference [9]."
+%
 \item \textit{It requires 6 degrees of freedom to achieve a reasonable reachable work space, how does this scale to a full 6 DoF task?
@@
 What is the reachable work space in the plane with 6 DoF and the + or - 60 degree joint limit?}
-
-We revised the text to clarify this point. The focus here is planar manipulation. Scaling to a 3-dimensional task is not considered in this paper. Our current work considers the 3D case.
-
+%
+Thank you for this observation. The focus of the paper is planar manipulation. Scaling to a 3-dimensional task is not considered in this paper. Our current work will consider the 3D case.
+We revised the text to clarify this point, we added in the multi-segment arm section: 
+"As was shown in [13] through the characterization of various actuator morphologies, the concatenation of soft cylindrical segments is most suitable to build up a robot arm that can create high blocking forces per fluid energy inserted."
+We also added to the same section:
+"Using six segments, the $\pm 60^\circ$ joint limit does not prohibit the robot to reach its own base.
+Calculating the forward kinematics, see \texttt{forwKin()} in Algorithm~\ref{alg:planGrasp}, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl."
+%
 \item \textit{Why was a convex shape necessary for approaching a grasp? What if I wanted to approach an object with a different orientation but in the same locations you already looked at?}
-
-Thank you we revised the text to say that the shape needs not be convex.
-The convex shape approach is a conservative solution to guarantee minimal computation required in solving the planning problem while assuring not to collide.
-
+%
+We added an emphasis to the manuscript to say that the shape needs not be convex.
+The convex shape approach is a conservative solution with minimal computation required in solving the planning problem while assuring not to collide.
+%
 \item \textit{What is the role of the rollers in carrying your payload? Without the rollers, could the arm not move the object?}
-
-The rollers minimize friction to the surface and therefor minimize frictional forces that need to be overcome.
-Stick-Slip Friction effects would be greatly increased if arm would be run directly on a surface with non-negligible friction coefficient.
-We added these details to the text.
-
+%
+Thank you for this comment, we added to the multi segment arm section:
+"The complete multi-segment arm is supported off the ground with two roller supports per segment. 
+The rollers minimize frictional forces to the surface. 
+If the arm would be moved over a non-slippery surface without rollers, the frictional effects would greatly reduce the agility of the arm and largely increase the stick-slip friction effects with the ground, rendering the arm less useful."
+%
 \item \textit{Why did you decide to minimize manipulator deformation for your grasp object planner?
 Furthermore, what if I wanted my plan to follow the shortest distance for the end effector to travel (essentially following the black line in Figure 6), is this even possible given the possible kinematics of the arm?}
-
-Minimized manipulator deformation is a feasible approach, because it is proportional to energy consumed by cylindrical piston drives and it minimizes strain to the actuators and minimizes risk of exerting further than actuation limit of a segment.
-We added this explanation to the paper.
-
+%
+Minimized manipulator deformation seemed to be a feasible approach, because it is proportional to energy consumed by the cylindrical piston drives and it minimizes strain to the actuators and minimizes risk of exerting further than actuation limit of a segment.
+We also added this explanation to the paper.
+%
 \end{enumerate}

### 2015-10-11 experimental_results.tex
finished reviewer 2's comments

@@
 The planner could take as a measure of progress a decreasing cartesian distance of the gripper to its final target pose.}
-\rkk{It is worth mentioning that the exteroceptive tracking system has the disadvantage that an occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment.
+\rkk{It is worth mentioning that the exteroceptive tracking system has the disadvantage that the full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment.
 In that case, the control loop can not function properly until the occlusion disappears.
-Proprioceptive sensors within the segments can solve this issue.}
+Proprioceptive sensors within the segments can solve this issue.
+A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in \cite{homberg2015haptic}.}
 
@@
 The magenta configurations represent the manipulator after grasping the object, that is moving from the object's location back to the bin location shown in red.
-Right: A photograph of the arm moving from its initial pose to the object and from the object to the release location, respectively.
-}
+Right: A photograph of the arm moving from its initial pose to the object and from the object to the release location, respectively.}
 \label{fig:oneTrialVsTime}
@@
 \end{figure*}
+
+\rkk{The experiments were performed for picking up objects on the left quadrant of the manipulator.
+Grasping objects on both sides of the manipulator could be achieved in various ways by 
+\begin{enumerate}
+\item replacing the large gripper at the end of the arm with two smaller grippers next to each other, 
+\item mounting roller supports on the top face of the manipulator and then rotating the manipulator at its root by $180^{\circ}$,
+\item increasing the reachable workspace through starting the soft arm at an extreme curvature configuration within the right quadrant.  
+\end{enumerate}
+}

### 2015-10-11 processing_control.tex
finished reviewer 2's comments

@@
 Those end-effector poses are essentially waypoints for an optimized path the robot arm should take to get to the final position without the risk of pushing away the object before the gripper arrives there.
-Forcing the arm controller to follow those intermediate waypoints ensures that the arm moves to the object while its null space maintains a convex shape, bending away from the object. 
-Furthermore, it allows the arm to move in smaller portions, decreasing the risk of large overshoots due to slip-stick friction between the roller supports and the ground.
+Forcing the arm controller to follow those intermediate waypoints ensures that the arm moves to the object while its null space maintains a convex shape, \rkk{always} bending away from the object. 
+\rkk{This is a conservative approach requiring minimal computation to solve the planning problem of not prematurely colliding with the object.} 
+Furthermore, \rkk{this approach} allows the arm to move in smaller portions, decreasing the risk of large overshoots due to slip-stick friction between the roller supports and the ground.
 This planner is described in more detail in Section~\ref{subsec:grasp_planner}.
@@
 After encapsulating the object, \texttt{moveToBin()} requests \texttt{trajGen()} for another trajectory from the current pose to a pre-defined bin location.
-After the manipulator has arrived at the bin location, the procedure \texttt{releaseObject()} causes the gripper to open and release the object.
+\rkk{When the manipulator gets close to the bin location}, the procedure \texttt{releaseObject()} causes the gripper to open and release the object.
 
@@
 In short, we define a series of approach radii $r_{a_i} \;  \forall i\, = 1..
-numMoves$ that define concentric circles shrinking from the manipulator's starting tip pose towards the center of the object.
+numMoves$ that define concentric \rkk{green} circles shrinking from the manipulator's starting tip pose towards the center of the object.
 Given actuator limits, we then search for a series of feasible manipulator configurations $\boldsymbol{\kappa}_i^*$ that will place the robot's end-effector on these \rkk{green} circles, parameterized by $r_a$ and $\phi$, while minimizing manipulator deformation.
+\rkk{Minimized manipulator deformation is chosen as the optimization criterion, because it is proportional to the energy consumed by the fluidic drive cylinders and it also minimizes the strain to the soft actuators.}
 
@@
 Here, the objective function represents the summation of independently weighted manipulator curvatures and the constraints force the manipulator's tip to lie on and to be tangent to the approach circle.
-This process leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced in Algorithm \ref{alg:planGrasp} for convenience.
+This process leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced in Algorithm~\ref{alg:planGrasp} for convenience.

### 2015-10-11 robotic_gripper.tex
finished reviewer 2's comments

@@
 The design for the arm consisting of soft cylindrical segments was described in \cite{marchese2014whole}.
+\rkk{As was shown in \ref{marchese2015recipe} through the characterization of various actuator morphologies, the concatenation of soft cylindrical segments is most suitable to build up a robotic arm that can create high blocking forces per fluid energy inserted.}
  \rkk{The cylindrical segments of the arm are fabricated through a retractable pin fabrication technique, which does not require lost wax cores because of their simple cylindrical cavities.} 
-Each cylindrical segment can only be actuated up to a bend angle of less than $60^\circ$, therefore several segments have to be combined together to allow the arm to reach a large enough workspace to perform proper manipulation tasks on a plane.
-The cylindrical design with its hollow channel in the center has enough space to accommodate for pneumatic tubes to connect to all six cylindrical segments and additionally to the pleated gripper, which is attached to the tip.
+Each cylindrical segment can only be actuated up to a bend angle of about $60^\circ$, therefore several segments have to be combined together to allow the arm to reach a large enough workspace to perform proper manipulation tasks on a plane.
+\rkk{Using six segments, the $\pm 60^\circ$ joint limit does not prohibit the robot to reach its own base.
+Calculating the forward kinematics, see \texttt{forwKin()} in Algorithm~\ref{alg:planGrasp}, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl.}
+The cylindrical segment design with its hollow channel in the center has enough space to accommodate for pneumatic tubes to connect to all six cylindrical segments and additionally to the pleated gripper, which is attached to the tip.
 The pleated gripper has to be appropriately sized, just big enough to allow for proper manipulation without exceeding the payload capacity of the soft arm.
+
+\rkk{The complete multi-segment arm is supported off the ground with two roller supports per segment. 
+The rollers minimize frictional forces to the surface. 
+If the arm would be moved over a non-slippery surface without rollers, the frictional effects would greatly reduce the agility of the arm and largely increase the stick-slip friction effects with the ground, rendering the arm less useful.}
 

### 2015-10-12 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex
response to reviewer 1 comments, half way

@@
 \textit{Section 4.2 par 1., Provide the speed of the optimization solver as well as the solver used.}
-
+%
+The nonlinear optimization problem was implemented using Matlab’s Optimization Toolbox with the function calls fmincon, which finds the minimum of a constrained nonlinear multivariable function.
+Sequential Quadratic Programming was used as the solver with a relative upper bound of $2 \times 10^{-3}$ on the magnitude of the constraint functions.
+The lower bound on the size of a step was given by $1 \times 10^{-6}$.
+The solver takes about 1\unit{s} on a regular PC to solve for all waypoints from start to finish.
 We included this information in the paper.
-
+%
 \subsection{Convexity as Constraint?}
@@
 How much does this depend on your specific task and the orientation of the arm/gripper combo?}
-
-When solving for a tangent gripper pose in CCW direction along a concentric circle, this is automatically the constraint for convexity.
-
+%
+When solving for a tangent gripper pose in CCW direction along the green concentric circles, this is implicitly the constraint for convexity.
+The algorithm proposed is task-specific as to picking up an object on a plane without pushing it away prematurely.
+We also added a note to the manuscript to clarify this.
+%
 \subsection{Algorithm Numbering}
 \textit{Section 4.3 The text describing Algorithm 1 would be well suited to have numbered sections that could help the reader understand at which location in the Algorithm the text is referring to.}
-
-We revised the manuscript accordingly.
-
+%
+Thank you for this advise.
+The way the algorithmic environment was set up in this document, it is not trivial to add line numbering to it.
+Instead we clarified the description of the algorithmic steps within the manuscript better, it should not require the line numbers anymore.
+%
 \subsection{Object Details}
 \textit{Section 5.2 What is the object weight? What is the object radius?}
-
-We added info about the sample objects we used in the paper.
-
+%
+The object has a weight of 18\unit{g} and a diameter of 3.3\unit{cm}. We added this info to the manuscript.
+%
 \subsection{Task Execution Speed}
 \textit{Figure 9: What is the time/speed of the task?}
-
-We added this data to the paper.
-
+%
+Depending on where the object is placed, the arm takes between 17-35\unit{s} to approach it. The task of moving back to the bin takes between 10-20\unit{s}. We added this data to the paper. 
+%
 \subsection{Additional References}
-
+%
 \textit{Lack of references (Some covered in DeVolder2010):
@@
 J. Li and J. Xiao, “A general formulation and approach to constrained, continuum manipulation,” Adv. Robot., no. July 2015, pp. 1–11, 2015.}
-
-Thank you, we added these references to the paper.
-
+%
+Thank you for your comments, we added these references to the introduction section of the paper.
+%
 %\clearpage
-
+%
 \section{Reviewer 2's Comments}
-
+%
 \textit{This paper covers the fabrication and integration of a new soft robot gripper with a six degree of freedom soft multi-segment arm.
 The paper also describes a planner for grasping using the integrated system as well as some evaluation of grasping efficacy and the gripper workspace.}
-
+%
 \textit{In general, I think the topic is very interesting and the approach valuable.
@@
 The following are specific feedback that I have:}
-
+%
 \subsection{Uncertainty Characterization}

### 2015-10-12 experimental_results.tex
response to reviewer 1 comments, half way

@@
 In 23 of 25 experimental trials, the manipulator successfully achieved the task of grasping an object and bringing it to a bin location shown in red.
+\rkk{The test object has a weight of 18\unit{g} and a diameter of 3.3\unit{cm}.}
 The object was placed five times on each of the five points marked on the board.
@@
 It is to note, that the saturation level for the integrator is defined by a safety limit on the maximal inflation of the robotic arm.
-In the other unsuccesful trial, the stick-slip friction also caused the arm to halt before a waypoint.
+In the other unsuccessful trial, the stick-slip friction also caused the arm to halt before a waypoint.
 The controller built up enough forcing due to inflation, so that the arm slipped over the close waypoint without having all of its single arm segment curvature within an acceptable epsilon.
@@
 The cyan configurations represent the manipulator prior to grasping the object, that is moving from its initial configuration to the object's location.
-The magenta configurations represent the manipulator after grasping the object, that is moving from the object's location back to the bin location shown in red.
-Right: A photograph of the arm moving from its initial pose to the object and from the object to the release location, respectively.}
+\rkk{Depending on where the object is placed, the arm takes between 17-35\unit{s} to approach it.} The magenta configurations represent the manipulator after grasping the object, that is moving from the object's location back to the bin location shown in red.
+\rkk{This task of moving back to the bin takes between 10-20\unit{s}.} Right: A photograph of the arm moving from its initial pose to the object and from the object to the release location, respectively.}
 \label{fig:oneTrialVsTime}

### 2015-10-12 introduction.tex
response to reviewer 1 comments, half way

@@
 \subsection{Related Work}
-There are several examples of soft grippers described in recent literature, we will mainly focus on fluidic-based systems. 
+\rkk{An overview of pneumatic and hydraulic microactuators has been provided by Volder et al. \cite{volder2010pneumatic}.} 
+\rkk{Ikuta and Suzuki \cite{ikuta2002safety} developed a multiple-segment micro-hydraulic actuator that can be controlled open-loop within blood vessels.}
+\rkk{Xiao and Vatcha\cite{xiao2010realtime} present simulation results of an online motion planner for a planar continuum manipulators.}
+\rkk{ Li and Xiao \cite{li2015general} extend this work to present a more general formulation to constrained, continuum manipulation.}
+There are \rkk{also} several examples of soft grippers described in recent literature, we will mainly focus on fluidic-based systems.
 Deimel and Brock \cite{deimel2013compliant} developed a pneumatically actuated three-fingered hand made of reinforced silicone that is mounted to a hard robot and capable of grasping.

### 2015-10-12 processing_control.tex
response to reviewer 1 comments, half way

@@
 
-The procedure first determines the manipulator's current tip pose $\mathbf{w}_t$ and the Euclidean distance $d_1$ between the tip and the object's center. 
+The procedure \rkk{\texttt{planGrasp()} in Algorithm \ref{alg:planGrasp}} first determines the manipulator's current tip pose $\mathbf{w}_t$ and the Euclidean distance $d_1$ between the tip and the object's center.
 \rkk{The arc length input to the arm's forward kinematics is the $N$-th element of the segment lengths $\mathbf{L}_{\textrm{meas}}$.}
-Next, considering the object's radius $r_o$ and the gripper normal offset $\mathbf{g}_{\textrm{off}}$, the minimal tip transit distance $d_2$ is calculated. 
 \rkk{The end effector offset $\mathbf{w}_{\textrm{off}}$ describes the distance from the root of the gripper, to an offset point close to the lower end of the gripper's palm.
@@
 \rkk{The length} $\mathbf{g}_{\textrm{off}}$ represents the component of the end effector offset $\mathbf{w}_{\textrm{off}}$, which is normal to the end effector orientation. 
+The minimal tip transit distance $d_2$ is calculated by \rkk{considering the object's radius $r_o$ and the gripper normal offset $\mathbf{g}_{\textrm{off}}$.} 
 Also, the number of approach configurations $numMoves$ is determined as $\lfloor \frac{d_2}{\Delta d} \rfloor$, where $\Delta d$ is an allowable incremental distance. 
-Using these parameters, approach radii $r_a$ are iteratively calculated and their corresponding locally optimal configurations are found using the \texttt{findOptimalConfig($r_a$)} procedure. 
-This process is posed as a nonlinear optimization. 
-Here, the objective function represents the summation of independently weighted manipulator curvatures and the constraints force the manipulator's tip to lie on and to be tangent to the approach circle.
-This process leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced in Algorithm~\ref{alg:planGrasp} for convenience.
+Using these parameters, approach radii $r_a$ \rkk{shown by the green circles} are iteratively calculated and their corresponding locally optimal configurations are found using the \texttt{findOptimalConfig($r_a$)} procedure.
+
+\rkk{The procedure \texttt{findOptimalConfig($r_a$)}} is posed as a nonlinear optimization \rkk{problem}. 
+Here, the objective function represents the summation of independently weighted manipulator curvatures \rkk{$\boldsymbol{\kappa} - \boldsymbol{\kappa}_{\textrm{off}}$.} The optimization constraints \rkk{cause} the manipulator's tip to lie on and to be tangent to the approach circle.
+\rkk{The constraints also ensure that the manipulator segment curvatures do not exceed the single soft actuator limits.}
+\rkk{Furthermore,} this \rkk{procedure} leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced \rkk{in the last section} of Algorithm~\ref{alg:planGrasp} for convenience.
+
+\rkk{The nonlinear optimization problem was implemented using Matlab’s Optimization Toolbox with the function calls \emph{fmincon}, which finds the minimum of a constrained nonlinear multivariable function.
+Sequential Quadratic Programming was used as the solver with a relative upper bound of $2 \times 10^{-3}$ on the magnitude of the constraint functions.
+The lower bound on the size of a step was given by $1 \times 10^{-6}$.
+The solver takes about 1\unit{s} on a regular PC to solve for all waypoints from start to finish.}

### 2015-10-12 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex
two comments left for reviewer 1

@@
 Only one experimental test is performed to demonstrate the algorithm, and no quantitative error metrics are provided.}
-
+%
 We thank the reviewer for pointing out that the contribution is not clear.
@@
 The gripper can pick up arbitrarily shaped objects (compatible with the size of the gripper) placed at arbitrary locations on the work space.
-TODO: We will revise the introduction section to make main contribution clear. We will also adjust the text to highlight the extensive experiments and the novelty.
-
+We revised the introduction section to make the main contribution clear.
+We also adjusted the text to highlight the extensive experiments.
+%
 \textit{For these reasons and especially for the minor contribution that this manuscript offers, I cannot recommend publication as a journal paper in SoRo.
 The contribution seems better suited for a conference paper submission.}
-
+%
 We believe that the contribution of successfully and repeatedly performing object manipulation using a fully soft, multiple degree of freedom arm is a novel capability.
 Our feasibility study opens many avenues for soft robotic manipulation.
-We will revise the introduction to better articulate these ideas.
-
+We revised the conclusion section to better articulate these ideas.
+%
 \subsection{Motion-Capture}
@@
 Have others done it before, do you have a reference on this?}
-
+%
 We thank the reviewer for this observation.
-We used an external localization system in our experiments because localization was not the main point of the contribution.
-We developed an end-to-end system that can approximately locate an unknown object placed at an unknown location and move it somewhere else.
-The external localization system is a convenient way to approximately identify the location of the object and visualize/track how the object is moved in the space.
-We can replace the external localization system with any other method for localizing an object in the workspace.
-We will revise the exposition to make these points more clear.
-
+We developed an end-to-end system that can approximately locate an object placed at an a priori unknown location and move it somewhere else.
+The external localization system is a convenient way to approximately identify the location of the object and to track how the object is moved around.
+The exteroceptive tracking system has the disadvantage that the full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment. 
+In that case, the control loop can not function properly until the occlusion disappears. 
+The external localization system could be replaced with another method for localizing the manipulator and the object in the workspace.
+For example, proprioceptive sensors within the segments could solve this issue partially. 
+A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in reference [9].
+%
 \subsection{Suitable contactless/constrained motion?}
 \textit{Section 1.1 Last paragraph: “was only suitable for contactless motion” implies that your proposed method solved motion when the robot is constrained by the environment, but it is rather about gripping objects.}
-TODO: Read that sentence again and try to understand what this comment means ?????
-
+%
+The sentence was confusing, we clarified the manuscript.
+%
 \subsection{Contribution 1}
@@
 Contribution 4 seems obvious that force sensing nor accurate positioning is required to manipulate objects (as discussed in [21]).}
-
-Contribution 1 is different than the contributions in 12 and 13, which focus on planning for the body of the robot.
-Here we plan for an enveloping grasp of an unknown object in the plane and demonstrate pick-and-place from uncertain locations.
-
+%
+Contribution 1 is different than the contributions listed in references [12] and [13].
+Reference [12] only presents a 6 segment soft arm that can move on a plane, not interaction or manipulation capabilities with objects are shown.
+The paper deals with the changing body shape of the soft arm when moving it around on a plane.
+Reference [13] discusses fundamental actuator morphologies and presents recipes on combining those morphologies, but an actually controllable 7 DOF arm is not detailed in that work.
+In this manuscript, we plan for an enveloping grasp of an unknown object in the plane and demonstrate pick-and-place from uncertain locations.
+We made clarifications to the contributions sections accordingly.
+%
 \subsection{System Overview Figure}
 \textit{Section 2. System overview, Figure 2: The image is difficult to see and in its current form, and information of the physical frame surrounding the robot seems unnecessary.}
-
-Thank you for this comment. We will revise the figure to make it clear what the system components are. We will be careful about the placement of labels.
-
+%
+Thank you for this comment.
+We moved the labels on the figure.
+Also, we added to the paper why the physical frame is important to have a mobile presentation platform that can keep the system together, hold the tracking cameras rigidly in place, and does not require recalibration of the tracking cameras.
+%
 \subsection{Fabrication Steps Detailing}
@@
 Furthermore Table 1 does not fit the column.}
-
-Indeed, Reference 13 includes some description of the fabrication steps, but the process described in reference 13 is different; specifically 13 does not describe the fabrication of the manipulator in this paper.
-We revised the manuscript to discuss the points necessary to allow the reader to reproduce the system.
-
+%
+Reference 13 includes some description of the fabrication steps, mainly to depict the more generic pleated fabrication process.
+The process described in that paper is not complete to allow the reader to reproduce this particular manipulation system.
+We added further clarification to the text.
+We also fixed the Table 1 formatting.
+%
 \subsection{Motion Tracker}
 \textit{Section 4.2 par 1., Which motion tracker was used?}
-We used the commercially available The Opti-Track System. We will revise the text to make this precise.
-
+We used the commercially available The OptiTrack Flex 3 System by Natural Point, Inc. We revised the text to add this information.
+%
 \subsection{Optimization Equation}
@@
 I suggest writing the equation in the text in full.}
-
-We revised the manuscript to clarify this point.
-
+%
+The weights are set by the matrix $\mathbf{R}$.
+The variables to optimize for are $\phi$ and $\kappa$.
+All parameters are introduced as inputs to the algorithm.
+We revised the manuscript to clarify this point and make it easier to find the optimization equation.
+%
 \subsection{Algorithm Difference}

### 2015-10-12 conclusion.tex
two comments left for reviewer 1

--- 2015-10-10 conclusion.tex
@@
 Such a homogeneous soft segment is less prone to rupture and to manufacturing inconsistencies, and would therefore allow for better robot performance.
-x
-The results presented in this paper suggest that despite their extreme compliance, soft robots are capable of repeatable object manipulation while simultaneously providing inherently safe interactions with their environment.
+
 The manipulator is suitable to perform delicate tasks with low payloads, for example grasping objects that should not be squeezed and/or should not break during manipulation.
-We demonstrated the ability of an entirely soft manipulator to autonomously grasp an object, which leads to many potential applications.
-In a manufacturing setting, this could resemble a soft robot executing tasks requiring high dexterity when handling delicate objects.
+\rkk{The ability to successfully and repeatedly perform object manipulation using a fully soft, multiple degree of freedom arm suggests} that despite their extreme compliance, soft robots are capable of \rkk{reliable and robust} object manipulation while simultaneously providing inherently safe interactions with the environment.
+We \rkk{also} demonstrated the \rkk{manipulator's} ability to autonomously grasp an object, which leads to many potential applications \rkk{for full soft robotic manipulation}.
+\rkk{In a manufacturing setting, this could resemble a soft robot stretched widely to pick up objects situated at various locations.}
 In a human-centric environment, soft arm grasping manipulation may enable soft robots to interact safely with humans.
 Furthermore, in a surgical setting, highly compliant soft robots with grippers may assist with operations in sensitive environments during tasks where no high level of precision is required.
+\rkk{To foster those assumptions, future work could investigate the dexterity of the arm when approaching same object poses in various ways, just by changing the constraints and cost function when optimizing for the inverse kinematics solution.
+Integrating proprioceptive sensing within a multi-segment soft actuator will further improve the use of these manipualtors in occluded environments.}

### 2015-10-12 experimental_results.tex
two comments left for reviewer 1

@@
 The planner could take as a measure of progress a decreasing cartesian distance of the gripper to its final target pose.}
-\rkk{It is worth mentioning that the exteroceptive tracking system has the disadvantage that the full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment.
+\rkk{We developed an end-to-end system that can approximately locate an object placed at an a priori unknown location and move it somewhere else.
+The external localization system is a convenient way to approximately identify the location of the object and to track how the object is moved around.
+The exteroceptive tracking system has the disadvantage that the full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment. 
 In that case, the control loop can not function properly until the occlusion disappears. 
-Proprioceptive sensors within the segments can solve this issue.
+The external localization system could be replaced with another method for localizing the manipulator and the object in the workspace.
+For example, proprioceptive sensors within the segments could solve this issue partially. 
 A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in \cite{homberg2015haptic}.}

### 2015-10-12 introduction.tex
two comments left for reviewer 1

@@
 The manipulator curvatures are controlled in real-time using a curvature-volume cascaded control law.
-The work presented in this paper builds on top of this system and expands its capabilities.
-The previous version was only suitable for contactless motions in space, that would be suitable for mere inspection.
+The work presented in this work builds on top \rkk{of the previous} system and expands its capabilities \rkk{to do actual manipulation}.
+The previous version \rkk{was only suitable for moving a soft manipulator through a constrained environment without object interaction or manipulation.
+That system is only suitable for inspection tasks}.
 The work presented here is capable of autonomous object manipulation on a plane. 
@@
 Previously, there were only single markers along the arm, which worked for a limited motion range, but was prone to fail if the markers go out of sight or another object is introduced to the environment.
-Also, many trial runs were needed to arrive at the various final positions in the maze.
-%, so the previous system was no repeatable and robust.
+Also, previously many trials were needed to successfully arrive at a final position.
 
@@
   %\item End-effector control of the grasping manipulator attached to a soft arm using a motion tracking system.
-  \item \rkk{Demonstrating that soft robots allow for proper autonomous manipulation of delicate objects without requiring force sensing or accurate positioning.} 
+  \item \rkk{Demonstrating that soft robots allow for proper autonomous manipulation of various delicate objects without requiring force sensing or accurate positioning.} 
 \end{itemize}

### 2015-10-12 processing_control.tex
two comments left for reviewer 1

@@
   \SetKwProg{myproc}{Procedure}{}{}
-  \myproc{\findOptimalConfig{$r_a$}}{
+  \myproc{\findOptimalConfig{$r_{a_i}$}}{
   $\begin{aligned}
@@
     & \text{subject to}
-    & &  \mathbf{w}_t \gets \begin{bmatrix} x_o \, + \, r \, \cos{\phi} \\ y_o \, + \, r \, \sin{\phi} \\ \phi \, + \, \frac{\pi}{2} \end{bmatrix}. \\
+    & &  \mathbf{w}_t \gets \begin{bmatrix} x_o \, + \, r_{a_i} \, \cos{\phi} \\ y_o \, + \, r_{a_i} \, \sin{\phi} \\ \phi \, + \, \frac{\pi}{2} \end{bmatrix}. \\
     & & & \mathbf{f} \gets \forwKin\left( \boldsymbol{\kappa}, \, \mathbf{L}, \, N, \, L_N \right). \\
@@
 Also, the number of approach configurations $numMoves$ is determined as $\lfloor \frac{d_2}{\Delta d} \rfloor$, where $\Delta d$ is an allowable incremental distance. 
-Using these parameters, approach radii $r_a$ \rkk{shown by the green circles} are iteratively calculated and their corresponding locally optimal configurations are found using the \texttt{findOptimalConfig($r_a$)} procedure.
+Using these parameters, approach radii $r_a$ \rkk{shown by the green circles} are iteratively calculated and their corresponding locally optimal configurations are found \rkk{by using the optimization equation and constraints described in procedure} \texttt{findOptimalConfig($r_{a_i}$)} \rkk{of Algorithm \ref{alg:planGrasp}}.
 
 \rkk{The procedure \texttt{findOptimalConfig($r_a$)}} is posed as a nonlinear optimization \rkk{problem}. 
-Here, the objective function represents the summation of independently weighted manipulator curvatures \rkk{$\boldsymbol{\kappa} - \boldsymbol{\kappa}_{\textrm{off}}$.} The optimization constraints \rkk{cause} the manipulator's tip to lie on and to be tangent to the approach circle.
+Here, the objective function represents the summation of independently weighted manipulator curvatures \rkk{$\boldsymbol{\kappa} - \boldsymbol{\kappa}_{\textrm{off}}$.}
+\rkk{The weights are set by the matrix $\mathbf{R}$.}
+\rkk{The variables to optimize for are $\phi$ and $\kappa$.}
+The optimization constraints \rkk{cause} the manipulator's tip to lie on and to be tangent to the approach circle. 
 \rkk{The constraints also ensure that the manipulator segment curvatures do not exceed the single soft actuator limits.}

### 2015-10-12 robotic_gripper.tex
two comments left for reviewer 1

@@
 %Following this, 
-We describe briefly the design, fabrication and functionality of this soft grasping manipulator. Further details on the design and fabrication can be found in \cite{marchese2015recipe}.
+We describe the design, fabrication and functionality of this soft grasping manipulator. Further details on the underlying design and fabrication recipes can be found in \cite{marchese2015recipe}.
 
@@
 (\textbf{A}) depicts the segment in an unactuated state and (\textbf{B}) shows the segment in an actuated and therefore bent state.
-The expansion of the pressurized channels are schematically represented.}
+The expansion of the pressurized channels are schematically represented.
+\rkk{Reproduced from \cite{marchese2015recipe}.}}
    \label{fig:design}
+\end{figure}
+
+\begin{figure}[!ht]
+\centering
+   \includegraphics[width=0.85\columnwidth]{figures/robotic_gripper/fabrication_upright.eps} %fab_pleated_process_horizontal_no_labels.eps
+      \caption{Gripper fabrication process.
+(\textbf{A}) Pour and cure a rubber mold \rkk{(blue)}, (\textbf{B}) pour wax core \rkk{(yellow)} with embedded supportive rod \rkk{(brown)}, (\textbf{C}) combine bottom mold \rkk{(green)}, top mold \rkk{(grey)} and wax core using pins, (\textbf{D}) pour \rkk{softer} rubber \rkk{(light green)} into assembled mold, (\textbf{E}) pour stiffer rubber \rkk{(blue)} on top of the cured gripper \rkk{(light green)} to form a constraint layer, (\textbf{F}) remove cured gripper from mold, (\textbf{G}) using an oven melt out wax core from the gripper, and (\textbf{H}) add silicone tubing and plug using silicone sealant.
+\rkk{Reproduced from \cite{marchese2015recipe}.}}
+      \label{fig:fabrication}
 \end{figure}
@@
 The tools and equipment used are listed in Table~\ref{tab:MachineTools} and are referred to by superscripts.
-
-\begin{figure}[htb]
-\centering
-   \includegraphics[width=0.98\columnwidth]{figures/robotic_gripper/fabrication_new.eps} %fab_pleated_process_horizontal_no_labels.eps
-      \caption{Gripper fabrication process.
-(\textbf{A}) Pour and cure a rubber mold \rkk{(blue)}, (\textbf{B}) pour wax core \rkk{(yellow)} with embedded supportive rod \rkk{(brown)}, (\textbf{C}) combine bottom mold \rkk{(green)}, top mold \rkk{(grey)} and wax core using pins, (\textbf{D}) pour \rkk{softer} rubber \rkk{(light green)} into assembled mold, (\textbf{E}) pour stiffer rubber \rkk{(blue)} on top of the cured gripper \rkk{(light green)} to form a constraint layer, (\textbf{F}) remove cured gripper from mold, (\textbf{G}) using an oven melt out wax core from the gripper, and (\textbf{H}) add silicone tubing and plug using silicone sealant.
-\rkk{Reproduced from \cite{marchese2015recipe}.}}
-      \label{fig:fabrication}
-\end{figure}
 

### 2015-10-12 system_overview.tex
two comments left for reviewer 1

@@
 A motion capture system provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
+\rkk{We used the motion capture system OptiTrack Flex 3 by by Natural Point, Inc.}
 The grasp motion planning algorithm as well as the curvature controller run on the control computers and take the tracking information as input.
@@
 A rigid frame holds all the subsystems together providing reliable and consistent hardware experiments. 
+\rkk{The frame serves also as a mobile presentation platform that keeps the complete system together and holds the tracking cameras rigidly in place, not requiring recalibration after moving the system around.}
 
@@
   \caption{System Overview.
-The system is composed of a motion capture system (A), rigid frame (B), soft six segment planar manipulator (C), an object within the grasp envelope (D), a soft gripper fixed to the manipulator (E), a fluidic drive cylinder array to control actuation (F), and computers for real-time processing and control (G).} \label{fig:sys_overview}
+The system is composed of (\textbf{A}) a motion capture system, (\textbf{B}) rigid frame, (\textbf{C}) soft six segment planar manipulator, (\textbf{D}) an object within the grasp envelope, (\textbf{E}) a soft gripper fixed to the manipulator, (\textbf{F}) a fluidic drive cylinder array to control actuation, and (\textbf{F}) computers for real-time processing and control.} \label{fig:sys_overview}
 \end{centering}

### 2015-10-12 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex
final comments

@@
 First, the contribution of the paper seems very minor.
-A considerable amount of the paper is already covered in the work from [12-14], which involves the design of the robot, the recipe to create the robot, and the whole-arm motion planning.
+A considerable amount of the paper is already covered in the work\cite{marchese2014whole} \cite{marchese2014design} \cite{marchese2015recipe}, which involves the design of the robot, the recipe to create the robot, and the whole-arm motion planning.
 The contribution of this work is the grasping algorithm itself, which is a preplanned sequence of robot curvatures.
-In light of the whole arm motion planner in [12], this contribution seems minor when adding in a (circular) object.
+In light of the whole arm motion planner in  \cite{marchese2014whole}, this contribution seems minor when adding in a (circular) object.
 The algorithm itself is implemented as a state-machine method, and with 4 or 5 states and seems trivial.
@@
 For example, proprioceptive sensors within the segments could solve this issue partially. 
-A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in reference [9].
+A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in reference \cite{homberg2015haptic}.
 %
@@
 \subsection{Contribution 1}
-\textit{Section 1.2 Contribution 1 seems entirely described in [12] and [13].
-Contribution 4 seems obvious that force sensing nor accurate positioning is required to manipulate objects (as discussed in [21]).}
+\textit{Section 1.2 Contribution 1 seems entirely described in \cite{marchese2014whole} and \cite{marchese2015recipe}.
+Contribution 4 seems obvious that force sensing nor accurate positioning is required to manipulate objects.}
 %
-Contribution 1 is different than the contributions listed in references [12] and [13].
-Reference [12] only presents a 6 segment soft arm that can move on a plane, not interaction or manipulation capabilities with objects are shown.
+Contribution 1 is different to previous contributions: Reference \cite{marchese2014whole} only presents a 6 segment soft arm that can move on a plane, not interaction or manipulation capabilities with objects are shown.
 The paper deals with the changing body shape of the soft arm when moving it around on a plane.
-Reference [13] discusses fundamental actuator morphologies and presents recipes on combining those morphologies, but an actually controllable 7 DOF arm is not detailed in that work.
+Reference \cite{marchese2015recipe} discusses fundamental actuator morphologies and presents recipes on combining those morphologies, but an actually controllable 7 DOF arm is not detailed in that work.
 In this manuscript, we plan for an enveloping grasp of an unknown object in the plane and demonstrate pick-and-place from uncertain locations.
@@
 \subsection{Fabrication Steps Detailing}
-\textit{Section 3.1-3.2 These sections are completely described in [13] and comes off as a recipe to make the manipulator, which is the contribution of [13], and therefore should not be reproduced in the main text.
+\textit{Section 3.1-3.2 These sections are completely described in \cite{marchese2015recipe}  and comes off as a recipe to make the manipulator, which is the contribution of \cite{marchese2015recipe}, and therefore should not be reproduced in the main text.
 Figure 4 and Table 1.
-Pulled from [13] seem unnecessary.
+Pulled from \cite{marchese2015recipe} seem unnecessary.
 Furthermore Table 1 does not fit the column.}
@@
 \subsection{Algorithm Difference}
-\textit{I also find it difficult to see exactly the difference between the algorithm presented here and the one in [12].
+\textit{I also find it difficult to see exactly the difference between the algorithm presented here and the one in \cite{marchese2014whole}.
 While grasping is indeed is one objective, that seems to be realized by a curvature objective.}
-
+%
 We thank the reviewer for this comment.
-We revised the exposition to highlight the differences between the two approaches.
-The algorithm in [12] is about planning the motion of a soft arm without a gripper through a maze at a centerline while taking the arms bulging shape as a trapezoidal into account.
-The approach does not work for approaching objects with the manipulator including a gripper, because a tip trajectory for successfully moving towards the object is not known, but needs to be generated.
+We revised the exposition within the "existing procedures section" to highlight the differences between the two approaches.
+The algorithm in \cite{marchese2014whole} is about planning the motion of a soft arm without a gripper through a maze at a centerline while taking the arms bulging shape as a trapezoidal into account.
+The approach does not work for approaching and grasping objects, because a tip trajectory for successfully moving towards the object is not known, but needs to be generated by posing and solving a new optimization problem.
 That trajectory needs to avoid pushing the object away with the manipulator trunk when approaching it with the soft gripper at its end.
@@
 The non-linear optimization is finding tangent poses along these lines using non-linear optimization and then follows down those concentric lines, which implicitly guarantees the arms pose to stay convex – since the circles are convex themselves.
-
+%
 \subsection{Optimization Constraints}
 \textit{Section 4.2 Is the optimization function over or underconstrained? Will you always find a solution? What happens if you don’t find a solution?}
-
-The optimization function is only over-constrained if we have to achieve a pose outside of the reachable workspace.
-Otherwise it is well-constrained.
-The system optimizes for the quadratic cost of having high curvatures.
-A solution is not found only if the target object pose is not within the reachable workspace of the arm, that means of the object was placed by the user outside of the workspace.
-The arm’s workspace can easily be calculated and added this formula to the paper.
-This workspace check is performed before doing any further calculations.
-
+%
+We added to the manuscript: "The optimization only becomes over-constrained if it has to find an arm pose outside of the arm's reachable workspace.
+That occurs if the object was user-placed outside the workspace.
+Before performing the optimization, a feasability check is performed using the arm's forward kinematics."
+%
 \subsection{Solver Details}
@@
 %
-Figure 3’s point 1 and c were modified according to your suggestion and more descriptive note were added to the fabricationg figure and the description in the paper.
+Figure 3’s point 1 and c were modified according to your suggestion and more descriptive notes were added to the fabrication figure and the description in the paper.
 %
@@
 Proprioceptive sensors within the segments can solve this issue.
-A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in reference [9]."
+A first step towards proprioceptive sensing was done for three soft fingers arranged as a hand in reference \cite{homberg2015haptic}."
 %
@@
 "Using six segments, the $\pm 60^\circ$ joint limit does not prohibit the robot to reach its own base.
-Calculating the forward kinematics, see \texttt{forwKin()} in Algorithm~\ref{alg:planGrasp}, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl."
+Calculating the forward kinematics, see \texttt{forwKin()} procedure in Algorithm 1, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl."
 %

### 2015-10-12 processing_control.tex
final comments

@@
 
-The planning algorithm presented in \cite{marchese2014whole} was developed to plan the motion of a soft arm  without gripper through a confined environment. 
-The optimization constraints and state machine setup in that work is significantly different and not applicable to the grasping shown here. 
-Therefore, a new planner is presented in the following section.
+\rkk{The algorithm presented in \cite{marchese2014whole} is about planning the motion of a soft arm without a gripper through a maze at a centerline while taking the arms bulging shape into account.
+The approach does not work for approaching and grasping objects, since a tip trajectory for successfully moving towards the object is not known, but needs to be generated by posing and solving a new optimization problem.
+This tip trajectory has to avoid that the manipulator trunk pushes the object prematurely away when approaching it.
+Therefore, a new planner had to be developed and is presented in the following section.}
 
@@
 \rkk{Furthermore,} this \rkk{procedure} leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced \rkk{in the last section} of Algorithm~\ref{alg:planGrasp} for convenience.
+\rkk{The optimization only becomes over-constrained if it has to find an arm pose outside of the arm's reachable workspace.
+That occurs if the object was user-placed outside the workspace.
+Before performing the optimization, a feasability check is performed using the arm's forward kinematics.}
 

### 2015-10-15 abstract.tex
all changes to the intro based on daniela's input.

@@
-This paper presents the development of an autonomous motion planning algorithm for a soft planar grasping manipulator capable of grasp-and-place operations by encapsulation.
+This paper presents the development of an autonomous motion planning algorithm for a soft planar grasping manipulator capable of grasp-and-place operations by encapsulation
+\dr{under uncertainty in the position and shape of the object.}
 The gripping end of the soft manipulator is fabricated without weakening seams using lost-wax casting instead of the commonly used multi-layer lamination process.
@@
 The autonomous planning system leverages the compliance and continuum bending of the soft grasping manipulator to achieve repeatable grasps in the presence of uncertainty.
-Modeling uncertainties arise from a simplifying constant-curvature assumption, unrepresented manipulator dynamics, stick-slip friction, and  non-linear fluidic control. 
-These uncertainties are compensated by the inherent compliance of the soft gripper design and the motion planning strategy.
-Additionally, when fully actuated, the manipulator remains compliant allowing it to conform to un-modeled object geometries.
 A suite of experiments is presented that demonstrates the system's capabilities.

### 2015-10-15 conclusion.tex
all changes to the intro based on daniela's input.

@@
 \rkk{To foster those assumptions, future work could investigate the dexterity of the arm when approaching same object poses in various ways, just by changing the constraints and cost function when optimizing for the inverse kinematics solution.
-Integrating proprioceptive sensing within a multi-segment soft actuator will further improve the use of these manipualtors in occluded environments.}
+Integrating proprioceptive sensing \dr{\cite{homberg2015haptic}} within a multi-segment soft actuator will further improve the use of these manipulators in occluded environments.}
+%The gripper was used as a manually actuated single finger with a bend sensor as part of a 3-fingered-hand in \cite{homberg2015haptic}.

### 2015-10-15 introduction.tex
all changes to the intro based on daniela's input.

--- 2015-10-11 introduction.tex
@@
 
-Our goal is to develop a soft planar fluid-powered gripper and a motion planning algorithm that leverages a soft morphology to robustly grasp, drag and place objects. 
+Our goal is to develop a soft planar fluid-powered gripper and a motion planning algorithm that leverages a soft morphology to robustly grasp, drag and place objects \dr{of unknown geometry}. 
 %By utilizing softness in the design of our robot, we gain the ability to adapt to environmental variation \cite{mcmahan2006field}, harmlessly collide with the environment \cite{marchese2014whole}, and build resilience to unexpected external loads \cite{tolley2014resilient};
@@
 \centering
-   \includegraphics[width=0.9\columnwidth]{Figures/experimental_results/egg_approach/egg_approach_sequence}
+   \includegraphics[width=0.99\columnwidth]{Figures/experimental_results/egg_approach/egg_approach_sequence_brighter}
    \caption{The soft manipulator is grasping an egg. The robot repeatably approached, grasped and moved this delicate object without breaking it.}
@@
 %Challenges 
-Our manipulator is highly compliant and its motion is not as precise as more traditional rigid-bodied robots. 
-The control of its configuration is not only limited by the compliance of its low-pressure actuation, but also by its inherent elasticity.
+%Our manipulator is highly compliant and its motion is not as precise as more traditional rigid-bodied robots. 
+%The control of its configuration is not only limited by the compliance of its low-pressure actuation, but also by its inherent elasticity.
 %Additionally, the manipulator's compliant nature complicates the process of determining and sensing the forward kinematics.
-Despite the constraints on accurate positioning introduced by the softness of the arm, we can still robustly execute autonomous grasping tasks.
+%Despite the constraints on accurate positioning introduced by the softness of the arm, we can still robustly execute autonomous grasping tasks.
 
@@
 %The gripper can conform due to his compliance to variations in object geometry, allowing it to successfully grasp.
-The design of the gripper itself is inspired by work of Polygerinos et al.~\cite{polygerinos2013towards}
+The design of the gripper itself is inspired by the work of Polygerinos et al.~\cite{polygerinos2013towards}
 The design is advantageous for grasping, because it exhibits high curvature, minimal radial expansion, and remains compliant during actuation. 
-We can repeatably fabricate the gripper using a lost-wax casting process instead of the commonly used soft lithography technique, a multi-layer lamination process.
+We can repeatably fabricate the gripper using a lost-wax casting process instead of the commonly used soft lithography technique.%, a multi-layer lamination process.
 Without weakening seams, the gripper is not prone to de-lamination under high deformations. 
 By abandoning the need for a lamination process, arbitrary shaped internal channels can be achieved.
-The gripper was used as a manually actuated single finger with a bend sensor as part of a 3-fingered-hand in \cite{homberg2015haptic}.
 
@@
 %and actuation of the gripper and manipulator is driven by an external fluidic cylinder array.
-We present a planning algorithm that advances the arm through all necessary states of the grasp-and-place operation.
-A minimal strain, collision-free approach to the object of interest is found by posing the plan as a series of constrained nonlinear optimization problems.
+\dr{Modeling uncertainties arise from a simplifying constant-curvature assumption, unrepresented manipulator dynamics, stick-slip friction, and non-linear fluidic control. 
+These uncertainties are compensated by the inherent compliance of our soft gripper design and our motion planning strategy.}
+The motion planning algorithm advances the arm through all the necessary states of the grasp-and-place operation.
+A minimal strain, collision-free \dr{movement towards} the object of interest is found by posing the plan as a series of constrained nonlinear optimization problems.
 The system first plans concentric approach circles shrinking from the initial end-effector pose down to the object diameter.
@@
 After successfully approaching the object, the gripper encapsulates it.
-We experimentally validate the system's ability to repeatably and autonomously grasp-and-place a randomly placed object.
+\dr{Even when the arm and gripper are fully actuated, they remain compliant allowing it to conform to un-modeled object geometries.}
+We experimentally validate the system's ability to repeatably and autonomously grasp-and-place randomly placed objects.
 
 \subsection{Related Work}
-There are several examples of soft grippers described in recent literature, we will mainly focus on fluidic-based systems. 
+\dr{An overview of soft robotics is presented in Rus and Tolley \cite{rus2015design}. We will cover in the following the relevant works in fabrication, grippers and control of soft robots.}
+
+Several manufacturing processes for soft biomimetic robots were reviewed by Cho et al. \cite{cho2009review}. 
+The vast majority of soft elastomer robots rely on the processes of soft lithography \cite{xia1998soft} and/or shape deposition manufacturing \cite{cham2002fast}. 
+Especially noteworthy is the use of wax for fabricating jammable skin chambers, which stiffens by vacuuming\cite{steltz2009soft}. 
+The gripper presented in this work also uses a lost-wax molding technique, but with a different type of actuation in mind: the obtained cavity structures are inflated to cause the gripper to bend.
+
+%\rkk{Volder et al. \cite{volder2010pneumatic} provides a detailed review of both pneumatic and hydraulic microactuators.} 
+There are several hardware examples for soft grippers described in recent literature, we will mainly focus on fluidic-based systems.
 Deimel and Brock \cite{deimel2013compliant} developed a pneumatically actuated three-fingered hand made of reinforced silicone that is mounted to a hard robot and capable of grasping.
@@
 Ilievski et al. \cite{ilievski2011soft} create through a soft-lithography fabrication a pneumatic starfish-like gripper composed of an array of silicone chambers and a PDMS membrane. 
-
 The gripper is hanging on a string and grasps objects like an egg or a mouse in an open-loop controlled manner. 
-
-Stokes et al. \cite{Stokes2014hybrid} use a soft elastomer quadrupedal robot to grasp objects in a hard-soft hybrid robotic platform. 
+Stokes et al. \cite{Stokes2014hybrid} use a soft elastomer quadrupedal robot attached to a wheeled robot to grip and retrieve objects. 
 A puncture resistant soft pneumatic gripper is developed by Shepherd et al. in \cite{shepherd2013soft}. 
 An alternative to positive pressure actuated soft grippers is a robotic gripper that makes use of granular material jamming developed by Brown et al. and detailed in \cite{brown2010universal}.
+\rkk{Ikuta and Suzuki \cite{ikuta2002safety} showed a multiple-segment micro-hydraulic actuator for entering blood vessels.}
 The soft octopus-inspired arms developed in \cite{calisti2010study} and \cite{calisti2011octopus} are not fluidic powered, but instead use cables to pull rigid fixtures embedded within an elastomer body.
@@
 
-Cho et al. \cite{cho2009review} review several manufacturing processes for soft biomimetic robots. 
-The vast majority of soft elastomer robots rely on the processes of soft lithography \cite{xia1998soft} and/or shape deposition manufacturing \cite{cham2002fast}. 
-Especially noteworthy is the use of lost-wax fabrication for jammable skin chambers, which get vacuumed to stiffen up \cite{steltz2009soft}. 
-The gripper presented here also uses a lost-wax molding technique, but with a different type of actuation in mind: the obtained cavity structures are inflated to cause the gripper to bend.
-
+%talk about control
+\rkk{Simulation results of an online motion planner for a planar continuum manipulators were presented by Xiao and Vatcha\cite{xiao2010realtime}.}
+\rkk{This work was extended by Li and Xiao \cite{li2015general} to present a more general formulation to constrained, continuum manipulation.}
 %More generally, the literature has several examples of soft pneumatic elastomer robots. 
@@
 %There are soft legged pneumatic walkers \cite{shepherd2011multigait, tolley2014resilient}, explosive jumpers \cite{shepherd2013using}, and 
-More recently, Marchese et al.
-demonstrated closed-loop position control of multi-segment soft planar fluidic elastomer manipulators in free space \cite{marchese2014design} and in confined spaces \cite{marchese2014whole}.
+Marchese et al. \cite{marchese2014design}  \cite{marchese2014whole} demonstrated closed-loop position control of multi-segment soft planar fluidic elastomer manipulators in free and confined space. 
 Positioning is achieved using forward and inverse kinematic models and real-time camera measurements. 
-The manipulator curvatures are controlled in real-time using a curvature-volume cascaded control law.
-The work presented in this paper builds on top of this system and expands its capabilities.
-The previous version was only suitable for contactless motions in space, that would be suitable for mere inspection.
-The work presented here is capable of autonomous object manipulation on a plane. 
-Furthermore, this work shows that combining two different soft actuator types can leverage the strength of each and together achieve a more complicated task of manipulating objects.
-The control of the arm is improved from the previous version by using a more robust vision tracking approach. 
-Previously, there were only single markers along the arm, which worked for a limited motion range, but was prone to fail if the markers go out of sight or another object is introduced to the environment.
-Also, many trial runs were needed to arrive at the various final positions in the maze.
-%, so the previous system was no repeatable and robust.
+%The manipulator curvatures are controlled in real-time using a curvature-volume cascaded control law.
+The previous version \rkk{was only suitable for inspection tasks by moving the manipulator through a constrained environment without object interaction or manipulation.}
+%Previously, there were only single markers along the arm, which worked for a limited motion range, but was prone to fail if the markers go out of sight or another object is introduced to the environment.
+%Also, previously many trials were needed to successfully arrive at a final position.
+
+\rkk{The work presented here builds on the previous system.
+We now combine two soft actuator types to leverage their strengths in a manipulation task.
+A new control method demonstrates the capabilities of this new soft manipulator to actually do autonomous manipulations under uncertainties.}
+%The control of the arm is improved from the previous version by using a more robust vision tracking approach.
 
 \subsection{Contributions}
-This work differs from the previous work in that we \rkk{create an entirely soft and autonomously controlled \emph{grasping} manipulation system. 
-We} do not attach a novel soft gripper to a hard arm nor do we move the gripper around manually, but we rather take on the challenge of grasping-and-placing objects with a seven degrees of freedom planar arm made entirely from soft rubber.
+We take on the challenge of grasping-and-placing objects with a seven degrees of freedom planar arm made entirely from soft rubber. 
+Our work differs from the previous work in that we \rkk{create an entirely soft and autonomously controlled \emph{grasping} manipulation system.} 
+\dr{Our planning and control method successfully copes with uncertainties in the object geometries, object placement and manipulator modeling.}
+%We do not attach a novel soft gripper to a hard arm nor do we move the gripper around manually, 
 We provide in this work the following contribution to soft robotics:
 \begin{itemize}
-  \item A \rkk{controllable} soft manipulator consisting of a multi-segment arm with a gripper to enable fully compliant planar grasping.
   \item A planning algorithm to grasp-and-place randomly positioned objects on a planar surface using a 7 DOF soft manipulator.  
+  \item \rkk{Proper autonomous manipulation of various objects} \dr{of unknown geometry placed randomly in the working space of a soft manipulator} \rkk{without requiring force sensing or accurate positioning.}
    \item Repeatable successful grasping demonstrations with a physical prototype and a \rkk{qualitative} experimental characterization of the uncertainty regions that can be tolerated by the soft gripper.
   %\item End-effector control of the grasping manipulator attached to a soft arm using a motion tracking system.
-  \item \rkk{Demonstrating that soft robots allow for proper autonomous manipulation of delicate objects without requiring force sensing or accurate positioning.} 
+%\item A \rkk{controllable} soft manipulator consisting of a multi-segment arm with a gripper to enable fully compliant planar grasping.
 \end{itemize}

### 2015-10-15 system_overview.tex
shortened system overview

--- 2015-07-07 system_overview.tex
@@
 \section{System Overview}
-\label{sec:System_Overview}
-The aggregate system is shown in Figure \ref{fig:sys_overview} and consists of a manipulator, a gripper, an object, a tracking system, control computers, a fluidic drive array and a rigid frame.
-The planar six segment soft rubber manipulator consists of twelve distributed elastomer actuators. This manipulator moves with minimal friction on a level plane.
-A soft rubber gripper is fixed to the tip of the manipulator.
-An object is randomly placed within the reachable envelop of the manipulator. 
-A motion capture system provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
-The grasp motion planning algorithm as well as the curvature controller run on the control computers and take the tracking information as input.
+The soft grasping manipulator shown in Figure \ref{fig:egg_approach_sequence} has six bidirectional segments with cylindrical cavities forming the arm and a single soft gripper with a pleated shape as the end effector.
+All 13 cavities of the manipulator are pneumatically controlled by fluidic drive cylinders \cite{marchese2014design} and move with minimal friction on a level plane.
+An object of feasible size but unknown geometry is randomly placed within the reachable envelop of the manipulator.  
+The location of the manipulator and the object is determined with an external localization system. 
+The motion planning algorithm as well as the curvature controller run on the control computers and take the location information as input.
 The curvature controller then provides continuous closed-loop adjustment of the fluidic drive cylinder array.
-The cylinder array directly actuates the manipulator and gripper.
-A rigid frame holds all the subsystems together providing reliable and consistent hardware experiments.
 
-\begin{figure}[htbp]
-\begin{centering}
-  \includegraphics[width=2.0in]{Figures/system_overview/sys_overview_smaller}\\
-  \caption{System Overview.
-The system is composed of a motion capture system (A), rigid frame (B), soft six segment planar manipulator (C), an object within the grasp envelope (D), a soft gripper fixed to the manipulator (E), a fluidic drive cylinder array to control actuation (F), and computers for real-time processing and control (G).} \label{fig:sys_overview}
-\end{centering}
-\end{figure}
+%The manipulation system consists of a manipulator, a gripper, an object, a tracking system, control computers, a fluidic drive array and a rigid frame.
+%The planar six segment soft rubber manipulator consists of twelve distributed elastomer actuators. 
+%A soft rubber gripper is fixed to the tip of the manipulator.
+%An object is randomly placed within the reachable envelop of the manipulator. 
+%A motion capture system provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
+%\rkk{We used the motion capture system OptiTrack Flex 3 by Natural Point, Inc.}
+%The cylinder array directly actuates the manipulator and gripper.
+%A rigid frame holds all the subsystems together providing reliable and consistent hardware experiments. 
+%\rkk{The frame serves also as a mobile presentation platform that keeps the complete system together and holds the tracking cameras rigidly in place, not requiring recalibration after moving the system around.}

### 2015-10-15 experimental_results.tex
moved system overview section to experimental section

@@
 We discuss the grasping of delicate objects and cylindrical objects as well as the repeatability and success rate of the autonomous system.
+
+\subsection{Aggregate System}
+\label{sec:aggregate_system}
+The aggregate \dr{soft manipulation} system is shown in Figure~\ref{fig:sys_overview}.
+%The planar six segment soft rubber manipulator consists of twelve distributed elastomer actuators. This manipulator moves with minimal friction on a level plane.
+%A soft rubber gripper is fixed to the tip of the manipulator.
+As our localization system, the OptiTrack Flex 3 by Natural Point provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
+A rigid frame holds all the subsystems \rkk{as a mobile presentation platform} together providing reliable and consistent hardware experiments without the need for recalibration.
+
+\begin{figure}[htbp]
+\begin{centering}
+  \includegraphics[width=2.0in]{Figures/system_overview/sys_overview_smaller}\\
+  \caption{System Overview.
+The system is composed of (\textbf{A}) a motion capture system, (\textbf{B}) rigid frame, (\textbf{C}) soft six segment planar manipulator, (\textbf{D}) an object within the grasp envelope, (\textbf{E}) a soft gripper fixed to the manipulator, (\textbf{F}) a fluidic drive cylinder array to control actuation, and (\textbf{F}) computers for real-time processing and control.} \label{fig:sys_overview}
+\end{centering}
+\end{figure}
 

### 2015-10-15 processing_control.tex
implements proposed changes by Daniela about the processing section

@@
 This section covers our approach to preplanning motion waypoints for the soft robot and controlling the manipulator along those points. 
-We cover existing procedures reused within the system, and detail the system's new architecture of for performing autonomous grasp-and-place tasks, including its main component, the Grasp Object Planner.
+%We cover existing procedures reused within the system, and detail the system's new architecture for performing autonomous grasp-and-place tasks, including its main component, the Grasp Object Planner.
 
-\subsection{Existing Procedures}
-The forward kinematics algorithm \texttt{forwKin()}, which we employ in this work, assumes piece-wise constant curvature according to \cite{webster2010design}. 
-This algorithm was experimentally validated for the soft planar arm in \cite{marchese2014design}.
-In order to uniquely fit a configuration representation to measured endpoint data in real-time, we use a previously developed single segment inverse kinematics algorithm \cite{marchese2014design} and refer to it in this work as \texttt{singSegInvKin()}.
+\subsection{Kinematic Control}
+The forward kinematics algorithm \texttt{forwKin()} assumes piece-wise constant curvature according to \cite{webster2010design} and \cite{marchese2014design}. 
+%This algorithm was experimentally validated for the soft planar arm in \cite{marchese2014design}.
+In order to uniquely fit a configuration representation to measured endpoint data in real-time, we use a previously developed single segment inverse kinematics algorithm \texttt{singSegInvKin()} \cite{marchese2014design}.
 The inputs to this block are the start and endpoint measurements in $\mathbb{R}^2$: $\mathbf{E}_n \; \forall n  = 1..N$, where $N$ is the number of segments composing the arm.
-The outputs from this block are the representations of the measured manipulator configuration: $\boldsymbol{\kappa}_{\textrm{meas}}$ and $\mathbf{L}_{\textrm{meas}}$.
-\rkk{Each segment of the manipulator is described by its measured curvature $\kappa_{\textrm{meas}}$ and its segment length $L_{\textrm{meas}}$}.
-This work expands on the previously developed cascaded closed-loop curvature controller, whose input is target curvatures $\boldsymbol{\kappa}_{\textrm{target}}$ and whose output is the controlled adjustment of a fluidic drive cylinder array to resolve the error between $\boldsymbol{\kappa}_{\textrm{target}}$ and $\boldsymbol{\kappa}_{\textrm{meas}}$.
-In this work we refer to it as the \texttt{curvatureController()}.
+The outputs from this block are the representations of the measured manipulator configuration: \rkk{measured curvature} $\boldsymbol{\kappa}_{\textrm{meas}}$ and \rkk{segment length} $\mathbf{L}_{\textrm{meas}}$.
+%\rkk{Each segment of the manipulator is described by its measured curvature $\kappa_{\textrm{meas}}$ and its segment length $L_{\textrm{meas}}$}.
+A cascaded closed-loop curvature controller \texttt{curvatureController()} takes the target curvatures $\boldsymbol{\kappa}_{\textrm{target}}$ as its input and resolves the error between $\boldsymbol{\kappa}_{\textrm{target}}$ and $\boldsymbol{\kappa}_{\textrm{meas}}$ by continuously adjusting the fluidic drive cylinder array.
 
-\rkk{The algorithm presented in \cite{marchese2014whole} is about planning the motion of a soft arm without a gripper through a maze at a centerline while taking the arms bulging shape into account.
+\rkk{We build on the path planning algorithm presented in \cite{marchese2014whole}.
+This prior work plans the motion of a soft arm without a gripper through a maze at a centerline while taking the arms bulging shape into account.
 The approach does not work for approaching and grasping objects, since a tip trajectory for successfully moving towards the object is not known, but needs to be generated by posing and solving a new optimization problem.
@@
 A state flow diagram describing its sensing, planning and executions states is given in Fig. \ref{fig:grasp-and-place-planner}. 
-A motion tracker constantly captures the position of the object and passes it along to a routine, which checks for the object to settle.
-\rkk{We consider the object to have settled if it has not moved by more than a small $\epsilon$ for 2\unit{s}}.
-After it has settled, the Grasp Object Planner receives the coordinates and radius of the settled object and together with the current curvature values of the arm and gripper, it solves a series of constrained nonlinear optimization problems to generate end-effector poses approaching the object.
-Those end-effector poses are essentially waypoints for an optimized path the robot arm should take to get to the final position without the risk of pushing away the object before the gripper arrives there.
-Forcing the arm controller to follow those intermediate waypoints ensures that the arm moves to the object while its null space maintains a convex shape, \rkk{always} bending away from the object. 
-\rkk{This is a conservative approach requiring minimal computation to solve the planning problem of not prematurely colliding with the object.} 
-Furthermore, \rkk{this approach} allows the arm to move in smaller portions, decreasing the risk of large overshoots due to slip-stick friction between the roller supports and the ground.
+A motion tracker constantly captures the position of the object.
+%and passes it along to a routine, which checks for the object to settle.
+%\rkk{We consider the object to have settled if it has not moved by more than a small $\epsilon$ for 2\unit{s}}.
+%After it has settled,
+The Grasp Object Planner receives the coordinates and radius of the object and together with the current curvature values of the arm and gripper, it solves a series of constrained nonlinear optimization problems to generate end-effector poses approaching the object.
+Those end-effector poses are waypoints for an optimized path the robot arm should take to get to the final position without the risk of moving the object before the gripper grasps it. 
+The intermediate waypoints ensure that the arm moves to the object while its null space maintains a convex shape, \rkk{always} bending away from the object. 
+\rkk{This is a conservative approach for
+%requiring minimal computation to solve the planning problem of 
+not prematurely colliding with the object.} 
+Furthermore, \rkk{this approach} allows the arm to move in smaller steps, decreasing the risk of large overshoots due to slip-stick friction between the roller supports and the ground.
 This planner is described in more detail in Section~\ref{subsec:grasp_planner}.
@@
 The Grasp Object Planner passes the approach configurations $\boldsymbol{\kappa}_i^*$ of the arm to the \texttt{curvatureController()} for execution in real-time.
-The controller receives measured curvatures $\boldsymbol{\kappa}_{meas}$ and lengths $\boldsymbol{L}_{meas}$ at an update rate of $100\unit{Hz}$ from the recursively called \texttt{singSegInvKin()} and uses these to successively control the arm to every intermediate configuration $\boldsymbol{\kappa}_i^*$.
+The controller receives measured curvatures $\boldsymbol{\kappa}_{meas}$ and lengths $\boldsymbol{L}_{meas}$ at an update rate of $100\unit{Hz}$ from the recursively called \texttt{singSegInvKin()} and uses them to successively control the arm to every intermediate configuration $\boldsymbol{\kappa}_i^*$.
 During the arm initialization, the new curvature controller performs a pre-pressurization of both lateral channels. 
@@
 To allow for smoother transitions between each configuration $\boldsymbol{\kappa}_i^*$, we also added a trajectory generation procedure \texttt{trajGen()} to the new curvature controller.
-It generates in real-time for each individual degree-of-freedom velocity profiles with acceleration and velocity constraints.
-These profiles allow real-time interpolation between the approach configurations of the arm and avoid overshooting at the next target configuration.
-When the arm has arrived at the object, the curvature controller initiates \texttt{graspObject()}.
+It generates in real-time velocity profiles with acceleration and velocity constraints for each individual degree-of-freedom.
+These profiles allow real-time interpolation between the approach configurations of the arm while avoiding overshooting at the next target configuration.
+When the arm has arrived at the desired pose next to the object, the curvature controller initiates \texttt{graspObject()}.
 After encapsulating the object, \texttt{moveToBin()} requests \texttt{trajGen()} for another trajectory from the current pose to a pre-defined bin location.
@@
 A fundamental component of the grasp-and-place system is its ability to plan a feasible approach motion to the object.
-That is, given the location $\left(x_o, \, y_o\right)$ and radius $r_o$ of a round object as well as the manipulator's current configuration $\boldsymbol{\kappa}_{\textrm{meas}}$ \rkk{and segment lengths $\mathbf{L}_{\textrm{meas}}$}, we determine a series of locally optimal manipulator configurations $\boldsymbol{\kappa}_i^* \; \forall i \, = 1..
+That is, given the location $\left(x_o, \, y_o\right)$ and radius $r_o$ of a cylinder enclosing the object as well as the manipulator's current configuration $\boldsymbol{\kappa}_{\textrm{meas}}$ \rkk{and segment lengths $\mathbf{L}_{\textrm{meas}}$}, we determine a series of locally optimal manipulator configurations called approach configurations $\boldsymbol{\kappa}_i^* \; \forall i \, = 1..
 numMoves$ that will, if sequentially achieved, bring the manipulator gradually closer to the object while any part of the arm is not touching the object.
 
-We refer to these as approach configurations.
-The process for determining these approach configurations is detailed in the \texttt{planGrasp()} procedure within the Grasp Object Planner, see Algorithm \ref{alg:planGrasp}.
+The process for determining the approach configurations is detailed in the \texttt{planGrasp()} procedure within the Grasp Object Planner, see Algorithm \ref{alg:planGrasp}.
 The planner is visualized in Figure \ref{fig:planGrasp}.
 In short, we define a series of approach radii $r_{a_i} \;  \forall i\, = 1..
-numMoves$ that define concentric \rkk{green} circles shrinking from the manipulator's starting tip pose towards the center of the object.
-Given actuator limits, we then search for a series of feasible manipulator configurations $\boldsymbol{\kappa}_i^*$ that will place the robot's end-effector on these \rkk{green} circles, parameterized by $r_a$ and $\phi$, while minimizing manipulator deformation.
+numMoves$ that define concentric circles shrinking from the manipulator's starting tip pose towards the center of the object.
+Given actuator limits, we then search for a series of feasible manipulator configurations $\boldsymbol{\kappa}_i^*$ that will place the robot's end-effector on the approach circles, parameterized by $r_a$ and $\phi$, while minimizing manipulator deformation.
 \rkk{Minimized manipulator deformation is chosen as the optimization criterion, because it is proportional to the energy consumed by the fluidic drive cylinders and it also minimizes the strain to the soft actuators.}
@@
    \caption{Visualization of the Grasp Object Planner.
-Concentric approach circles are shown in \emph{green} and are centered about the object shown in \emph{cyan}.
-The locally optimal approach configurations are shown in \emph{blue} and the gripper is shown in \emph{red}.
-The initially measured manipulator configuration is shown in black.}
+Concentric approach circles are centered about the object.
+The locally optimal approach configurations of the arm are shown as curved dashed lines with a straight gripper at the end.
+The initially measured manipulator configuration is shown as a long and dashed straight line on the right.}
    \label{fig:planGrasp}
@@
 \rkk{The arc length input to the arm's forward kinematics is the $N$-th element of the segment lengths $\mathbf{L}_{\textrm{meas}}$.}
-\rkk{The end effector offset $\mathbf{w}_{\textrm{off}}$ describes the distance from the root of the gripper, to an offset point close to the lower end of the gripper's palm.
+\rkk{The end effector offset $\mathbf{w}_{\textrm{off}}$ describes the distance from the root of the gripper to an offset point close to the lower end of the gripper's palm.
 It is visualized in the top left corner of Fig.~\ref{fig:grasp-and-place-planner}.}

### 2015-10-15 conclusion.tex
implemented all remaining changes for experimental, and conclusion section

@@
 \label{sec:conclusion}
-This work introduced a new manufacturing approach for a soft manipulator and demonstrated its capabilities through autonomously grasping-and-placing a randomly positioned object.
-To produce the complete soft manipulator used, an entirely soft gripper was designed and fabricated and then combined with a previously developed soft robotic arm.
+This work describes a planar soft manipulator capable of pick-and-place operations under high uncertainty in the position and shape of the object. 
+%introduced a new manufacturing approach for a soft manipulator and demonstrated its capabilities through autonomously grasping-and-placing a randomly positioned object.
+%To produce the complete soft manipulator used, an entirely 
+A soft gripper was designed, fabricated, and combined with a previously developed soft robotic arm.
 It was then shown that a minimal strain and collision-free approach to an object of interest can be achieved by posing the grasp motion plan as a series of constrained nonlinear optimization problems.
@@
 In a human-centric environment, soft arm grasping manipulation may enable soft robots to interact safely with humans.
-Furthermore, in a surgical setting, highly compliant soft robots with grippers may assist with operations in sensitive environments during tasks where no high level of precision is required.
-\rkk{To foster those assumptions, future work could investigate the dexterity of the arm when approaching same object poses in various ways, just by changing the constraints and cost function when optimizing for the inverse kinematics solution.
-Integrating proprioceptive sensing \dr{\cite{homberg2015haptic}} within a multi-segment soft actuator will further improve the use of these manipulators in occluded environments.}
+%Furthermore, in a surgical setting, highly compliant soft robots with grippers may assist with operations in sensitive environments during tasks where no high level of precision is required.
+\rkk{Future work will investigate the dexterity of the arm when approaching same object poses in various ways, just by changing the constraints and cost function when optimizing for the inverse kinematics solution.
+Integrating proprioceptive sensing within a multi-segment soft actuator will further improve the use of these manipulators in occluded environments.}
 %The gripper was used as a manually actuated single finger with a bend sensor as part of a 3-fingered-hand in \cite{homberg2015haptic}.

### 2015-10-15 experimental_results.tex
implemented all remaining changes for experimental, and conclusion section

@@
 \label{sec:experimental_results}
-In the following section summarizes the results from experiments with the soft manipulator.
-We discuss the grasping of delicate objects and cylindrical objects as well as the repeatability and success rate of the autonomous system.
+%In the following section summarizes the results from experiments with the soft manipulator. 
+We now discuss the grasping of objects as well as the repeatability and success rate of the autonomous system.
 
@@
 %A soft rubber gripper is fixed to the tip of the manipulator.
-As our localization system, the OptiTrack Flex 3 by Natural Point provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
-A rigid frame holds all the subsystems \rkk{as a mobile presentation platform} together providing reliable and consistent hardware experiments without the need for recalibration.
+Each arm segment is 6.27\unit{cm} and the soft gripper is 10.6\unit{cm} long.
+The localization system OptiTrack Flex 3 by Natural Point provides real-time measurements of marked points both along the inextensible back of the manipulator and on top of the object. 
+A rigid frame holds all the subsystems \rkk{as a mobile presentation platform} together providing reliable hardware experiments without the need for recalibration.
 
@@
 
-\subsection{Grasping Delicate Objects}
-\rkk{It was shown in \cite{marchese2015recipe} that pleated grippers of similar dimensions like the one used in this work can be contiuously actuated in a pressure range of 0-60\unit{kPa} and create blocking forces in the range of 0-2\unit{N}.
+%\subsection{Grasping Delicate Objects}
+%\rkk{It was shown in \cite{marchese2015recipe} that pleated grippers of similar dimensions like the one used in this work can be contiuously actuated in a pressure range of 0-60\unit{kPa} and create blocking forces in the range of 0-2\unit{N}.
 This fine actuation range and the fact that soft manipulators easily conform to shapes implies that grasping delicate objects should be possible.}
-The manipulator in fact picks up delicate objects \rkk{such as eggs, shuttlecocks or bakery items} without \rkk{squishing} or breaking those. 
-Figure~\ref{fig:egg_approach_sequence} shows \rkk{for example} how the manipulator approaches and grasps an egg.
-Delicate objects can be manipulated without requiring a shape or a force sensor within its structure, since the compliant gripper body conforms to the object.
-Rigid-bodied grippers usually rely on force sensing or another type of sensory feedback to avoid damage caused to the object.
+%The manipulator in fact picks up delicate objects \rkk{such as eggs, shuttlecocks or bakery items} without \rkk{squishing} or breaking those. 
+%Figure~\ref{fig:egg_approach_sequence} shows \rkk{for example} how the manipulator approaches and grasps an egg.
+%Delicate objects can be manipulated without requiring a shape or a force sensor within its structure, since the compliant gripper body conforms to the object.
+%Rigid-bodied grippers usually rely on force sensing or another type of sensory feedback to avoid damage caused to the object.
 
@@
 \subsection{Repeated Grasp Experiments}
-We performed 25 experimental grasp-and-place trials at various positions to demonstrate the capabilities and repeatability of our system.
-The results of all the trials are shown in Figure~\ref{fig:allTestsOverlaid}.
+We performed over 200 experimental grasp-and-place trials at various positions to demonstrate the capabilities and repeatability of our system.
+We picked up various objects such as eggs, shuttlecocks, bakery items, cups, light bulbs, and tape holders. 
+The objects had an enclosing diameter in the range of 2-5\unit{cm}. 
+The results of a subset of those experimental trials are shown in Figure~\ref{fig:allTestsOverlaid}.
 One representative approach, grasp, and retract move is shown in Figure~\ref{fig:oneTrialVsTime}.
-In 23 of 25 experimental trials, the manipulator successfully achieved the task of grasping an object and bringing it to a bin location shown in red.
+In 23 of 25 experimental trials shown, the manipulator successfully achieved the task of grasping an object and placing it at a bin location shown in red.
 \rkk{The test object has a weight of 18\unit{g} and a diameter of 3.3\unit{cm}.}
@@
 Our kinematic modeling does not account for this non-linear behavior, which acts as a disturbance and can lead to failure to arrive at the next waypoint.
-To be more specific, in one of the trials, the robot slowed down too much before it almost reached its next waypoint and because of friction the arm halted to a full stop. 
-The proportional gain of the curvature controller was not able to compensate for that small positional delta and since the relatively low saturation level of the integrator portion of the controller was saturated, the arm did not move to the next waypoint pose.
-It is to note, that the saturation level for the integrator is defined by a safety limit on the maximal inflation of the robotic arm.
-In the other unsuccessful trial, the stick-slip friction also caused the arm to halt before a waypoint.
+%To be more specific, in one of the trials, the robot slowed down too much before it almost reached its next waypoint and because of friction the arm halted to a full stop. 
+%The proportional gain of the curvature controller was not able to compensate for that small positional delta and since the relatively low saturation level of the integrator portion of the controller was saturated, the arm did not move to the next waypoint pose.
+%It is to note, that the saturation level for the integrator is defined by a safety limit on the maximal inflation of the robotic arm.
+%In the other unsuccessful trial, the stick-slip friction also caused the arm to halt before a waypoint.
 The controller built up enough forcing due to inflation, so that the arm slipped over the close waypoint without having all of its single arm segment curvature within an acceptable epsilon.
-The controller then tried to swing back to fulfill the missed waypoint, missed it again and that finally caused the whole arm to oscillate back-and-forth and eventually push the object off the table.
-In one of the other trials, the grasp and return was successfully performed, but a small overshoot over the final bin location at the end of the return caused the arm to drop off the table, which could have been avoided if the table would have not been too small towards the right.
-This outlier is shown in Figure~\ref{fig:allTestsOverlaid}.
-Overall, the experiments show that the system was repeatably able to autonomously locate a randomly placed object within its workspace, plan the arm motions, and perform the task of grasping and placing the object.
+%The controller then tried to swing back to fulfill the missed waypoint, missed it again and that finally caused the whole arm to oscillate back-and-forth and eventually push the object off the table.
+In one of the trials shown in Figure~\ref{fig:allTestsOverlaid}, the grasp and return was successfully performed, but an overshoot over the final bin location caused the arm to drop off the relatively small table.
+%, which could have been avoided if the table would have not been too small towards the right.
+%This outlier is shown in Figure~\ref{fig:allTestsOverlaid}.
 
 \subsection{Experimental Insights and Limitations}
+Overall, the experiments show that the system was repeatably able to autonomously locate a randomly placed object within its workspace, plan the arm motions, and perform the task of grasping and placing the object.
 The system can drag payloads of less than 40\unit{g}, higher payloads cause the cylindrical arm segments to stall and possibly lift off the table without moving the payload.
@@
 As the length of the arm increases, more workspace can be reached while less payload can be manipulated. 
-Most of the payload capability is already used up by the attached gripper itself.
-A smaller gripper would allow for larger payloads to get picked up, but consequently only smaller objects can be grasped.
-The workspace of the manipulator is limited to the top and left by the maximal extension length of the arm, and to the bottom by the maximum bending curvature, which the arm can achieve without over-actuating a single segment.
-\rkk{The gripper presented can not only pick up a round object, but also more arbitrarily shaped objects of similar size, for example a star-shaped object, a tape holder, a shuttlecock or an egg.}
-Objects were only grasped within the left quadrant of the arm, because of the gripper orientation and an upright initial starting pose.
+%Most of the payload capability is already used up by the attached gripper itself.
+%A smaller gripper would allow for larger payloads to get picked up, but consequently only smaller objects can be grasped.
+%The workspace of the manipulator is limited to the top and left by the maximal extension length of the arm, and to the bottom by the maximum bending curvature, which the arm can achieve without over-actuating a single segment.
+%\rkk{The gripper presented did not only pick up round objects, but also more arbitrarily shaped objects of similar size, for example a star-shaped object, a tape holder, a shuttlecock or an egg.}
+%Objects were only grasped within the left quadrant of the arm, because of the gripper orientation and an upright initial starting pose.
 \rkk{A smoothing of the complete trajectory with several intermediate waypoints was found to be necessary.
-The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found empirically to be 5\unit{cm}, around half the length of the gripper.
-A new waypoint is sent to the controller immediately after arriving within a small delta of the previous waypoint, the controllers for each arm segment then compensate for the new delta in curvature as quickly as possible to get to the new pose $\kappa_i^*$.}
-\rkk{The instabilities observed in the unsuccessful trials could be solved by loosening the constraints on the planner.
+The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found to be about the length of one arm segment.
+%, around half the length of the gripper. 
+%A new waypoint is sent to the controller immediately after arriving within a small delta of the previous waypoint, the controllers for each arm segment then compensate for the new delta in curvature as quickly as possible to get to the new pose $\kappa_i^*$.}
+%\rkk{The instabilities observed in the unsuccessful trials could be solved by loosening the constraints on the planner.
 The planner could allow the arm controller to have the arm pass over each intermediate waypoint without having to get to a full stop within an arbitrarily chosen delta of curvature values.
 The planner could take as a measure of progress a decreasing cartesian distance of the gripper to its final target pose.}
+
 \rkk{We developed an end-to-end system that can approximately locate an object placed at an a priori unknown location and move it somewhere else.

### 2015-10-15 robotic_gripper.tex
taking away unnecessary detail and fix a citation

@@
 The design for the arm consisting of soft cylindrical segments was described in \cite{marchese2014whole}.
-\rkk{As was shown in \ref{marchese2015recipe} through the characterization of various actuator morphologies, the concatenation of soft cylindrical segments is most suitable to build up a robotic arm that can create high blocking forces per fluid energy inserted.}
+\rkk{As was shown in \cite{marchese2015recipe} through the characterization of various actuator morphologies, the concatenation of soft cylindrical segments is most suitable to build up a robotic arm that can create high blocking forces per fluid energy inserted.}
  \rkk{The cylindrical segments of the arm are fabricated through a retractable pin fabrication technique, which does not require lost wax cores because of their simple cylindrical cavities.} 
 Each cylindrical segment can only be actuated up to a bend angle of about $60^\circ$, therefore several segments have to be combined together to allow the arm to reach a large enough workspace to perform proper manipulation tasks on a plane.
-\rkk{Using six segments, the $\pm 60^\circ$ joint limit does not prohibit the robot to reach its own base.
-Calculating the forward kinematics, see \texttt{forwKin()} in Algorithm~\ref{alg:planGrasp}, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl.}
+\rkk{Using six segments, the joint limit does not prohibit the robot to reach its own base.} %Calculating the forward kinematics, see \texttt{forwKin()} in Algorithm~\ref{alg:planGrasp}, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl.}
 The cylindrical segment design with its hollow channel in the center has enough space to accommodate for pneumatic tubes to connect to all six cylindrical segments and additionally to the pleated gripper, which is attached to the tip.

### 2015-10-15 robotic_gripper.tex
changes to fab section

@@
 %Following this, 
-We describe the design, fabrication and functionality of this soft grasping manipulator. Further details on the underlying design and fabrication recipes can be found in \cite{marchese2015recipe}.
+We briefly describe the design, fabrication and functionality of this soft grasping manipulator. Further details on the design and fabrication can be found in \cite{marchese2015recipe}.
 
@@
 \centering
-   \includegraphics[width=0.90\columnwidth]{figures/robotic_gripper/design_gripper.eps}
+   \includegraphics[width=0.99\columnwidth]{figures/robotic_gripper/design_gripper.eps}
    \caption{The pleated channel designs.
@@
 
-\begin{figure}[!ht]
-\centering
-   \includegraphics[width=0.85\columnwidth]{figures/robotic_gripper/fabrication_upright.eps} %fab_pleated_process_horizontal_no_labels.eps
-      \caption{Gripper fabrication process.
+%\begin{figure}[!ht]
+%\centering
+%   \includegraphics[width=0.85\columnwidth]{figures/robotic_gripper/fabrication_upright.eps} %fab_pleated_process_horizontal_no_labels.eps
+%      \caption{Gripper fabrication process.
 (\textbf{A}) Pour and cure a rubber mold \rkk{(blue)}, (\textbf{B}) pour wax core \rkk{(yellow)} with embedded supportive rod \rkk{(brown)}, (\textbf{C}) combine bottom mold \rkk{(green)}, top mold \rkk{(grey)} and wax core using pins, (\textbf{D}) pour \rkk{softer} rubber \rkk{(light green)} into assembled mold, (\textbf{E}) pour stiffer rubber \rkk{(blue)} on top of the cured gripper \rkk{(light green)} to form a constraint layer, (\textbf{F}) remove cured gripper from mold, (\textbf{G}) using an oven melt out wax core from the gripper, and (\textbf{H}) add silicone tubing and plug using silicone sealant.
 \rkk{Reproduced from \cite{marchese2015recipe}.}}
-      \label{fig:fabrication}
-\end{figure}
+%      \label{fig:fabrication}
+%\end{figure}
 
@@
 Using this approach, the \emph{cyan} portion of the pleated gripper can be cured in a single step, avoiding any weakening seams due to lamination.
-\rkk{Fabrication techniques based on the lamination of several cast rubber pieces lead to more manufacturing inconsistencies due to slight misalignments of layers. 
-We observed that soft actuators built this way tend to rupture more easily at their weakening seams.}
+%\rkk{Fabrication techniques based on the lamination of several cast rubber pieces lead to more manufacturing inconsistencies due to slight misalignments of layers. 
+%We observed that soft actuators built this way tend to rupture more easily at their weakening seams.}
 
 \subsection{Lost Wax Fabrication for Fluidic Elastomer Actuators}
-Existing soft fluidic manipulators are produced through a multi-step lamination process, which results in weakening seams that can easily delaminate. 
+Existing soft fluidic manipulators are mostly produced through a multi-step lamination process called soft lithography, which results in weakening seams that can easily delaminate. 
 This limits their range of applications and lifetime.
 \rkk{The retractable pin fabrication for uniform lateral channels, first introduced in \cite{marchese2014whole}, does not cause weakening seams to the actuator, but it also does not allow for cavities more complicated than cylindrical shapes.}
-This is why we propose the application of lost-wax casting to the fabrication of soft fluidic actuators like a gripper.
+This is why the application of lost-wax casting to the fabrication of soft fluidic actuators like a gripper is advantageous.
 The actuated cavities of the soft gripper are achieved by using a wax core, pourable silicone rubber and 3D printed molds.
-The complete fabrication process for the soft gripper consists of eight steps that are depicted in Figure~\ref{fig:fabrication}.
-The tools and equipment used are listed in Table~\ref{tab:MachineTools} and are referred to by superscripts.
-
-In step (A), harder silicone rubber$^6$ is poured into a mold, which contains a 3D-printed model of the wax core.
-In preparation for step (B), the model is removed and the rubber mold is left inside the outer mold.
-A rigid rod is \rkk{embedded} as a supportive inlay inside the wax core.
-The rod is laid into the cavity of the rubber mold, supported on both ends by the outer mold.
-This ensures that the wax core does not break when removed from the rubber mold.
-\rkk{Mold release spray is applied to the silicone rubber mold to ease the wax core removal process.}
-The bees-wax$^{7}$ is heated up until it becomes fully liquefied.
-The assembly of rubber mold and outer mold is then heated up for a few minutes to the same temperature as the wax.
-Using a syringe, the liquid wax is injected into the assembly.
-Within a few minutes, the injected wax will start to solidify and significantly shrink in volume; this is counteracted by injecting more hot wax into the solidifying wax core during cool down.
-In step (B), the wax core is first allowed to completely cool down, then it is released from the mold.
-In step (C), the cooled down wax core is assembled together with the bottom mold, which defines the pleated structure of the gripper.
-The mold assembly is aligned with a top mold using pins. This top mold provides for additional volume to cover the wax core.
-In step (D), low elastic modulus rubber$^1$ is mixed, degassed in a vacuum$^2$, and poured to form the gripper and allowed to cure.
-In step (E), stiffer rubber$^3$ is poured on top of the cured gripper to form a constraint layer.
-In step (F), the cured gripper is removed from the mold.
-In step (G), most of the wax core is melted out by placing the gripper into an oven in an upright position.
-After this, remaining wax residues are cooked out in a boiling water bath.
-Finally, in step (H) a silicone tube$^5$ and a piece of silicone cord$^{8}$ get covered with silicone sealant$^4$ and are inserted into the front and back holes respectively.
-
-\begin{table}[h]
-\caption{Commercially Available Tools and Equipment}
-\centering
-\begin{tabular}{c l l}
-\hline
-\hline
-\# & Product Name & Company\\
-\hline
-1 & Ecoflex 0030&  Smooth-On\\
-2 & AL Cube & Abbess Instr. and Sys., Inc.\\
-3 & Mold Star 15 & Smooth-On\\
-4 & Silicone Sealant 732 & Dow Corning Corp\\
-5 & PN 51845K53 & McMaster\\
-6 & Mold Star 30 & Smooth-On\\
-7 & Beeswax & Jacquard\\
-8 & PN 9808K21& McMaster\\
-\hline
-\end{tabular}
-\label{tab:MachineTools}
-\end{table}
+The gripper fabrication process and the tools needed are fully described and depicted in Section~4.3.
+and Figure~14 of the recipes paper for soft fluidic elastomer actuators \cite{marchese2015recipe}.
+%Figure~\ref{fig:fabrication}.
+%The tools and equipment used are also listed in Table~\ref{tab:MachineTools} and are referred to by superscripts.
+%
+%In step (A), harder silicone rubber$^6$ is poured into a mold, which contains a 3D-printed model of the wax core.
+%In preparation for step (B), the model is removed and the rubber mold is left inside the outer mold.
+%A rigid rod is \rkk{embedded} as a supportive inlay inside the wax core.
+%The rod is laid into the cavity of the rubber mold, supported on both ends by the outer mold.
+%This ensures that the wax core does not break when removed from the rubber mold.
+%\rkk{Mold release spray is applied to the silicone rubber mold to ease the wax core removal process.}
+%The bees-wax$^{7}$ is heated up until it becomes fully liquefied.
+%The assembly of rubber mold and outer mold is then heated up for a few minutes to the same temperature as the wax.
+%Using a syringe, the liquid wax is injected into the assembly.
+%Within a few minutes, the injected wax will start to solidify and significantly shrink in volume; this is counteracted by injecting more hot wax into the solidifying wax core during cool down.
+%In step (B), the wax core is first allowed to completely cool down, then it is released from the mold.
+%In step (C), the cooled down wax core is assembled together with the bottom mold, which defines the pleated structure of the gripper.
+%The mold assembly is aligned with a top mold using pins. This top mold provides for additional volume to cover the wax core.
+%In step (D), low elastic modulus rubber$^1$ is mixed, degassed in a vacuum$^2$, and poured to form the gripper and allowed to cure.
+%In step (E), stiffer rubber$^3$ is poured on top of the cured gripper to form a constraint layer.
+%In step (F), the cured gripper is removed from the mold.
+%In step (G), most of the wax core is melted out by placing the gripper into an oven in an upright position.
+%After this, remaining wax residues are cooked out in a boiling water bath.
+%Finally, in step (H) a silicone tube$^5$ and a piece of silicone cord$^{8}$ get covered with silicone sealant$^4$ and are inserted into the front and back holes respectively.
+%
+%\begin{table}[h]
+%\caption{Commercially Available Tools and Equipment}
+%\centering
+%\begin{tabular}{c l l}
+%\hline
+%\hline
+%\# & Product Name & Company\\
+%\hline
+%1 & Ecoflex 0030&  Smooth-On\\
+%2 & AL Cube & Abbess Instr. and Sys., Inc.\\
+%3 & Mold Star 15 & Smooth-On\\
+%4 & Silicone Sealant 732 & Dow Corning Corp\\
+%5 & PN 51845K53 & McMaster\\
+%6 & Mold Star 30 & Smooth-On\\
+%7 & Beeswax & Jacquard\\
+%8 & PN 9808K21& McMaster\\
+%\hline
+%\end{tabular}
+%\label{tab:MachineTools}
+%\end{table}
 
@@
 Each cylindrical segment can only be actuated up to a bend angle of about $60^\circ$, therefore several segments have to be combined together to allow the arm to reach a large enough workspace to perform proper manipulation tasks on a plane.
-\rkk{Using six segments, the joint limit does not prohibit the robot to reach its own base.} %Calculating the forward kinematics, see \texttt{forwKin()} in Algorithm~\ref{alg:planGrasp}, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl.}
+\rkk{Using six segments, the joint limits do not prohibit the robot to reach with its tip its own root.} %Calculating the forward kinematics, see \texttt{forwKin()} in Algorithm~\ref{alg:planGrasp}, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl.}
 The cylindrical segment design with its hollow channel in the center has enough space to accommodate for pneumatic tubes to connect to all six cylindrical segments and additionally to the pleated gripper, which is attached to the tip.
@@
 If the arm would be moved over a non-slippery surface without rollers, the frictional effects would greatly reduce the agility of the arm and largely increase the stick-slip friction effects with the ground, rendering the arm less useful.}
-
-The independent actuation of the unidirectional gripper and each bidirectional arm segment is achieved through an array of custom fluidic drive cylinders.
-%The fluidic drive cylinders control the curvature of a bidirectional arm segment or a unidirectional gripper.
-Those cylinders are driven by a linear actuator and controlled through a motor controller, which takes its command signals from a higher-level curvature controller. 
-The design of these cylindrical actuators is given in \cite{marchese2014design}.

### 2015-10-15 system_overview.tex
changes to fab section

@@
 The soft grasping manipulator shown in Figure \ref{fig:egg_approach_sequence} has six bidirectional segments with cylindrical cavities forming the arm and a single soft gripper with a pleated shape as the end effector.
-All 13 cavities of the manipulator are pneumatically controlled by fluidic drive cylinders \cite{marchese2014design} and move with minimal friction on a level plane.
+The independent pneumatic actuation of the unidirectional gripper and each bidirectional arm segment, is achieved through an array of 13 custom fluidic drive cylinders \cite{marchese2014design}.
+%All 13 cavities of the manipulator are pneumatically controlled by fluidic drive cylinders \cite{marchese2014design} and move with minimal friction on a level plane.
 An object of feasible size but unknown geometry is randomly placed within the reachable envelop of the manipulator.  
@@
 %\rkk{The frame serves also as a mobile presentation platform that keeps the complete system together and holds the tracking cameras rigidly in place, not requiring recalibration after moving the system around.}
+
+%The fluidic drive cylinders control the curvature of a bidirectional arm segment or a unidirectional gripper.
+%Those cylinders are driven by a linear actuator and controlled through a motor controller, which takes its command signals from a higher-level curvature controller. 
+%The design of these cylindrical actuators is given in \cite{marchese2014design}.

### 2015-10-16 experimental_results.tex
missing bracket
final changes by daniela to manuscript

@@
 
-\subsection{Aggregate System}
-\label{sec:aggregate_system}
-The aggregate \dr{soft manipulation} system is shown in Figure~\ref{fig:sys_overview}.
+\subsection{Experimental Platform}
+The \dr{soft manipulation} system is shown in Figure~\ref{fig:experimental_platform}.
 %The planar six segment soft rubber manipulator consists of twelve distributed elastomer actuators. This manipulator moves with minimal friction on a level plane.
@@
   \caption{System Overview.
-The system is composed of (\textbf{A}) a motion capture system, (\textbf{B}) rigid frame, (\textbf{C}) soft six segment planar manipulator, (\textbf{D}) an object within the grasp envelope, (\textbf{E}) a soft gripper fixed to the manipulator, (\textbf{F}) a fluidic drive cylinder array to control actuation, and (\textbf{F}) computers for real-time processing and control.} \label{fig:sys_overview}
+The system is composed of (\textbf{A}) a motion capture system, (\textbf{B}) rigid frame, (\textbf{C}) soft six segment planar manipulator, (\textbf{D}) an object within the grasp envelope, (\textbf{E}) a soft gripper fixed to the manipulator, (\textbf{F}) a fluidic drive cylinder array to control actuation, and (\textbf{F}) computers for real-time processing and control.} \label{fig:experimental_platform}
 \end{centering}
@@
 
-\subsection{Repeated Grasp Experiments}
-We performed over 200 experimental grasp-and-place trials at various positions to demonstrate the capabilities and repeatability of our system.
+\subsection{Grasp Experiments}
+\rkk{Using the experimental platform in Figure~\ref{fig:experimental_platform}, we implemented the planning algorithm described in Section~\ref{sec:processing_and_control}.
+We evaluated the manipulator system for repeatability and ability to handle uncertainty.
+The experiments consisted of picking and placing several objects of unknown geometry placed at an unknown location.
+We measured the execution time and captured the location data during the experiments.
+Specifically,}
+we performed over 200 experimental grasp-and-place trials at various positions to demonstrate the capabilities and repeatability of our system.
 We picked up various objects such as eggs, shuttlecocks, bakery items, cups, light bulbs, and tape holders. 
@@
 \rkk{A smoothing of the complete trajectory with several intermediate waypoints was found to be necessary.
-The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found to be about the length of one arm segment.
+The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found to be about the length of one arm segment.}
 %, around half the length of the gripper. 

### 2015-10-16 introduction.tex
final changes by daniela to manuscript

@@
 %By utilizing softness in the design of our robot, we gain the ability to adapt to environmental variation \cite{mcmahan2006field}, harmlessly collide with the environment \cite{marchese2014whole}, and build resilience to unexpected external loads \cite{tolley2014resilient};
+\rkk{In this paper we describe a planar soft robot manipulator we developed toward this goal.
+We focus on the design, fabrication, control, and planning aspects of this soft robot.}
 
@@
 \begin{itemize}
+  \item The design and fabrication process of a soft 2D manipulator.
   \item A planning algorithm to grasp-and-place randomly positioned objects on a planar surface using a 7 DOF soft manipulator.  
-  \item \rkk{Proper autonomous manipulation of various objects} \dr{of unknown geometry placed randomly in the working space of a soft manipulator} \rkk{without requiring force sensing or accurate positioning.}
-   \item Repeatable successful grasping demonstrations with a physical prototype and a \rkk{qualitative} experimental characterization of the uncertainty regions that can be tolerated by the soft gripper.
+  \item \rkk{Autonomous manipulation experiments with various objects} \dr{of unknown geometry placed randomly in the working space of a soft manipulator} \rkk{without requiring force sensing or accurate positioning.}
+   \item Data from repeatable successful grasping demonstrations with a physical prototype and a \rkk{qualitative} experimental characterization of the uncertainty regions that can be tolerated by the soft gripper.
   %\item End-effector control of the grasping manipulator attached to a soft arm using a motion tracking system.

### 2015-10-16 processing_control.tex
final changes by daniela to manuscript

@@
 \label{subsec:grasp_planner}
-A fundamental component of the grasp-and-place system is its ability to plan a feasible approach motion to the object.
+The grasp-and-place system plans a feasible approach motion to the object.
 That is, given the location $\left(x_o, \, y_o\right)$ and radius $r_o$ of a cylinder enclosing the object as well as the manipulator's current configuration $\boldsymbol{\kappa}_{\textrm{meas}}$ \rkk{and segment lengths $\mathbf{L}_{\textrm{meas}}$}, we determine a series of locally optimal manipulator configurations called approach configurations $\boldsymbol{\kappa}_i^* \; \forall i \, = 1..
@@
 \rkk{Furthermore,} this \rkk{procedure} leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced \rkk{in the last section} of Algorithm~\ref{alg:planGrasp} for convenience.
-\rkk{The optimization only becomes over-constrained if it has to find an arm pose outside of the arm's reachable workspace.
+\rkk{The optimization becomes over-constrained only if it has to find an arm pose outside of the arm's reachable workspace.
 That occurs if the object was user-placed outside the workspace.

### 2015-10-16 abstract.tex
review comments by David implemented

@@
 This paper presents the development of an autonomous motion planning algorithm for a soft planar grasping manipulator capable of grasp-and-place operations by encapsulation
-\dr{under uncertainty in the position and shape of the object.}
-The gripping end of the soft manipulator is fabricated without weakening seams using lost-wax casting instead of the commonly used multi-layer lamination process.
+\dr{with uncertainty in the position and shape of the object.}
+The end effector of the soft manipulator is fabricated in one piece without weakening seams using lost-wax casting instead of the commonly used multi-layer lamination process.
 The soft manipulation system can grasp randomly positioned objects within its reachable envelope and move them to a desired location without human intervention.

### 2015-10-16 introduction.tex
review comments by David implemented

@@
 %High Level Vision
-Soft robots exhibit continuum body motion, large scale deformation, high compliance and adjustable impedance  compared to traditional rigid-bodied robots with high impedance \cite{trivedi2008soft}. 
+Soft robots exhibit continuum body motion, large scale deformation, high compliance, and adjustable impedance  compared to traditional rigid-bodied robots with high impedance \cite{trivedi2008soft}. 
 % whereas humans and animals have extremities with variable impedance.
@@
 
-Our goal is to develop a soft planar fluid-powered gripper and a motion planning algorithm that leverages a soft morphology to robustly grasp, drag and place objects \dr{of unknown geometry}. 
+Our goal is to develop a soft planar fluid-powered gripper and a motion planning algorithm that leverages a soft morphology to robustly grasp, drag, and place objects \dr{of unknown geometry}. 
 %By utilizing softness in the design of our robot, we gain the ability to adapt to environmental variation \cite{mcmahan2006field}, harmlessly collide with the environment \cite{marchese2014whole}, and build resilience to unexpected external loads \cite{tolley2014resilient};
@@
 We can repeatably fabricate the gripper using a lost-wax casting process instead of the commonly used soft lithography technique.%, a multi-layer lamination process.
-Without weakening seams, the gripper is not prone to de-lamination under high deformations. 
+As a homogeneous piece without weakening seams, the gripper is not prone to de-lamination under high deformations. 
 By abandoning the need for a lamination process, arbitrary shaped internal channels can be achieved.
@@
 The vast majority of soft elastomer robots rely on the processes of soft lithography \cite{xia1998soft} and/or shape deposition manufacturing \cite{cham2002fast}. 
-Especially noteworthy is the use of wax for fabricating jammable skin chambers, which stiffens by vacuuming\cite{steltz2009soft}. 
+Especially noteworthy is the use of wax for fabricating jammable skin chambers, which stiffens by vacuuming \cite{steltz2009soft}. 
 The gripper presented in this work also uses a lost-wax molding technique, but with a different type of actuation in mind: the obtained cavity structures are inflated to cause the gripper to bend.
@@
 Deimel and Brock \cite{deimel2013compliant} developed a pneumatically actuated three-fingered hand made of reinforced silicone that is mounted to a hard robot and capable of grasping.
-More recently, they have developed an anthropomorphic soft pneumatic hand capable of dexterous grasps, which is not mounted to a robot, but instead just held by a human \cite{deimel2014novel}. 
-Ilievski et al. \cite{ilievski2011soft} create through a soft-lithography fabrication a pneumatic starfish-like gripper composed of an array of silicone chambers and a PDMS membrane. 
-The gripper is hanging on a string and grasps objects like an egg or a mouse in an open-loop controlled manner. 
+More recently, they have developed an anthropomorphic soft pneumatic hand capable of dexterous grasps, which is not mounted to a robot, but instead held by a human \cite{deimel2014novel}. 
+Using a soft-lithography fabrication, Ilievski et al. \cite{ilievski2011soft} created a pneumatic starfish-like gripper composed of an array of silicone chambers and a PDMS membrane. 
+The gripper hangs on a string and grasps objects like an egg or a mouse in an open-loop controlled manner. 
 Stokes et al. \cite{Stokes2014hybrid} use a soft elastomer quadrupedal robot attached to a wheeled robot to grip and retrieve objects. 
@@
 An alternative to positive pressure actuated soft grippers is a robotic gripper that makes use of granular material jamming developed by Brown et al. and detailed in \cite{brown2010universal}.
-\rkk{Ikuta and Suzuki \cite{ikuta2002safety} showed a multiple-segment micro-hydraulic actuator for entering blood vessels.}
+\rkk{Ikuta and Suzuki \cite{ikuta2002safety} demonstrated a multiple-segment micro-hydraulic actuator for entering blood vessels.}
 The soft octopus-inspired arms developed in \cite{calisti2010study} and \cite{calisti2011octopus} are not fluidic powered, but instead use cables to pull rigid fixtures embedded within an elastomer body.
@@
 %talk about control
-\rkk{Simulation results of an online motion planner for a planar continuum manipulators were presented by Xiao and Vatcha\cite{xiao2010realtime}.}
+\rkk{Simulation results using an online motion planner for a planar continuum manipulators were presented by Xiao and Vatcha\cite{xiao2010realtime}.}
 \rkk{This work was extended by Li and Xiao \cite{li2015general} to present a more general formulation to constrained, continuum manipulation.}
@@
 %There are soft legged pneumatic walkers \cite{shepherd2011multigait, tolley2014resilient}, explosive jumpers \cite{shepherd2013using}, and 
-Marchese et al. \cite{marchese2014design}  \cite{marchese2014whole} demonstrated closed-loop position control of multi-segment soft planar fluidic elastomer manipulators in free and confined space. 
-Positioning is achieved using forward and inverse kinematic models and real-time camera measurements. 
+Marchese et al. \cite{marchese2014design} demonstrated closed-loop position control of a multi-segment soft planar fluidic elastomer manipulator in free space. 
+%Positioning is achieved using forward and inverse kinematic models and real-time camera measurements. 
 %The manipulator curvatures are controlled in real-time using a curvature-volume cascaded control law.
-The previous version \rkk{was only suitable for inspection tasks by moving the manipulator through a constrained environment without object interaction or manipulation.}
+\rkk{The soft manipulator presented in \cite{marchese2014whole} is only suitable for inspection tasks by moving through a constrained environment without object interaction or manipulation.}
 %Previously, there were only single markers along the arm, which worked for a limited motion range, but was prone to fail if the markers go out of sight or another object is introduced to the environment.
@@
 
-\rkk{The work presented here builds on the previous system.
-We now combine two soft actuator types to leverage their strengths in a manipulation task.
-A new control method demonstrates the capabilities of this new soft manipulator to actually do autonomous manipulations under uncertainties.}
+\rkk{The work presented here combines two soft actuator types to leverage their strengths in a planar manipulation task.
+A new control method described here demonstrates the capabilities of this new soft manipulator to perform autonomous manipulations with uncertainties.}
 %The control of the arm is improved from the previous version by using a more robust vision tracking approach.

### 2015-10-16 katzschmann2015autonomous.tex
remove old /rkk comments
all changes to the intro based on daniela's input.
changes to fab section
review comments by David implemented

@@
 \newcommand{\unit}[1]{\ensuremath{\, \mathrm{#1}}} %Use this macro to tell \LaTeX that you don’t want your units slanted in math mode.
-%\newcommand{\rkk}[1]{{\color{blue}#1}} 
-\newcommand{\rkk}[1]{#1}
+\newcommand{\rkk}[1]{{\color{blue}#1}} 
+%\newcommand{\rkk}[1]{#1} 
+\newcommand{\dr}[1]{{\color{blue}#1}} 
+%\newcommand{\dr}[1]{#1}
 
@@
 Marchese, and Daniela Rus are with the Computer Science and Artificial Intelligence Laboratory, Massachusetts Institute of Technology, 32 Vassar St.
-Cambridge, MA 02139, USA, {\tt\small \{rkk, andy, rus\}@csail.mit.edu}}%
+Cambridge, MA 02139, USA, {\tt\small rkk@csail.mit.edu}}%
 }
@@
     \begin{abstract}
-	\textbf{
-      	\input{abstract}
-	}
+\textbf{\input{abstract}}
     \end{abstract}
@@
 \section*{ACKNOWLEDGMENTS}
-This research was conducted in the Distributed Robotics Laboratory at MIT with support from the National Science Foundation, grant numbers NSF 1117178, NSF IIS1226883 and NSF CCF1138967, and National Science Foundation Graduate Research Fellowship Program, primary award number 1122374.
+This research was conducted in the Distributed Robotics Laboratory at MIT with support from the National Science Foundation, grant numbers NSF 1117178, NSF IIS1226883, NSF CCF1138967, and National Science Foundation Graduate Research Fellowship Program, primary award number 1122374.
 We are grateful for this support.

### 2015-10-16 processing_control.tex
review comments by David implemented

@@
 \subsection{Kinematic Control}
-The forward kinematics algorithm \texttt{forwKin()} assumes piece-wise constant curvature according to \cite{webster2010design} and \cite{marchese2014design}. 
+The forward kinematics algorithm \texttt{forwKin()} assumes piece-wise constant curvature \cite{webster2010design}. 
 %This algorithm was experimentally validated for the soft planar arm in \cite{marchese2014design}.
@@
 The approach does not work for approaching and grasping objects, since a tip trajectory for successfully moving towards the object is not known, but needs to be generated by posing and solving a new optimization problem.
-This tip trajectory has to avoid that the manipulator trunk pushes the object prematurely away when approaching it.
+The manipulator trunk should not push the object away when approaching it.
 Therefore, a new planner had to be developed and is presented in the following section.}
@@
    \includegraphics[width=0.95\columnwidth]{Figures/processing_control/grasp_place_planner.eps}
-   \caption{State flow diagram of the grasp-and-place planner developed for the autonomous grasp-and-place operation of the manipulator.
+   \caption{State flow diagram of the planner developed for the autonomous grasp-and-place operation of the manipulator.
 This diagram describes essentially the flow of information from the motion tracking system to the discrete hardware.}
@@
 The Grasp Object Planner passes the approach configurations $\boldsymbol{\kappa}_i^*$ of the arm to the \texttt{curvatureController()} for execution in real-time.
-The controller receives measured curvatures $\boldsymbol{\kappa}_{meas}$ and lengths $\boldsymbol{L}_{meas}$ at an update rate of $100\unit{Hz}$ from the recursively called \texttt{singSegInvKin()} and uses them to successively control the arm to every intermediate configuration $\boldsymbol{\kappa}_i^*$.
+The controller receives measured curvatures $\boldsymbol{\kappa}_{\textrm{meas}}$ and lengths $\mathbf{L}_{meas}$ at an update rate of $100\unit{Hz}$ from the recursively called \texttt{singSegInvKin()} and uses them to successively control the arm to every intermediate configuration $\boldsymbol{\kappa}_i^*$.
 During the arm initialization, the new curvature controller performs a pre-pressurization of both lateral channels. 
@@
   \Repeat{$i$ = $numMoves$}{
-    $i$ = $i \, + \, 1$ \;
+    $i$ = $i \, + \, 1$. \;
     $r_{a_i} \gets d_1 \, - \, i\,\frac{d_2}{numMoves}$. \;
-    $\boldsymbol{\kappa}_i^* \gets$ \findOptimalConfig{$r_{a_i}$}\;
+    $\boldsymbol{\kappa}_i^* \gets$ \findOptimalConfig{$r_{a_i}$}.\;
   }
@@
 
-\rkk{The nonlinear optimization problem was implemented using Matlab’s Optimization Toolbox with the function calls \emph{fmincon}, which finds the minimum of a constrained nonlinear multivariable function.
-Sequential Quadratic Programming was used as the solver with a relative upper bound of $2 \times 10^{-3}$ on the magnitude of the constraint functions.
+\rkk{The nonlinear optimization problem is implemented on a PC using Sequential Quadratic Programming, which finds iteratively the minimum of a constrained nonlinear multivariable function.
+The solver is run with a relative upper bound of $2 \times 10^{-3}$ on the magnitude of the constraint functions.
 The lower bound on the size of a step was given by $1 \times 10^{-6}$.
-The solver takes about 1\unit{s} on a regular PC to solve for all waypoints from start to finish.}
+The solver takes about 1\unit{s} to solve for all waypoints from start to finish.}

### 2015-10-16 system_overview.tex
review comments by David implemented

@@
 \section{System Overview}
-The soft grasping manipulator shown in Figure \ref{fig:egg_approach_sequence} has six bidirectional segments with cylindrical cavities forming the arm and a single soft gripper with a pleated shape as the end effector.
-The independent pneumatic actuation of the unidirectional gripper and each bidirectional arm segment, is achieved through an array of 13 custom fluidic drive cylinders \cite{marchese2014design}.
+The soft grasping manipulator shown in Figure \ref{fig:egg_approach_sequence} has six bidirectional segments with cylindrical cavities forming the arm and a single soft gripper with a pleated shape (Figure~\ref{fig:design}) as the end effector.
+The independent pneumatic actuation of the unidirectional soft gripper and each bidirectional arm segment, is achieved through an array of 13 custom fluidic drive cylinders \cite{marchese2014design}.
 %All 13 cavities of the manipulator are pneumatically controlled by fluidic drive cylinders \cite{marchese2014design} and move with minimal friction on a level plane.

### 2015-10-16 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex
submitting revision

@@
 The original reviewer comments are shown in italics, our answers are given underneath.
-The changes to the manuscript are all indicated by blue color.
+%The changes to the manuscript are all indicated by blue color.
 
@@
 The gripper can pick up arbitrarily shaped objects (compatible with the size of the gripper) placed at arbitrary locations on the work space.
-We revised the introduction section to make the main contribution clear.
+We revised the contribution subsection within the subsection to make the main contribution clear.
 We also adjusted the text to highlight the extensive experiments.
@@
 The paper deals with the changing body shape of the soft arm when moving it around on a plane.
-Reference \cite{marchese2015recipe} discusses fundamental actuator morphologies and presents recipes on combining those morphologies, but an actually controllable 7 DOF arm is not detailed in that work.
+Reference \cite{marchese2015recipe} discusses fundamental actuator morphologies and presents recipes on combining those morphologies, but how to make a 7 DOF arm controllable is not detailed in that work.
 In this manuscript, we plan for an enveloping grasp of an unknown object in the plane and demonstrate pick-and-place from uncertain locations.
@@
 We moved the labels on the figure.
-Also, we added to the paper why the physical frame is important to have a mobile presentation platform that can keep the system together, hold the tracking cameras rigidly in place, and does not require recalibration of the tracking cameras.
+Also, we added to the paper in the experimental section why the physical frame is important to have a mobile presentation platform that can keep the system together, hold the tracking cameras rigidly in place, and does not require recalibration of the tracking cameras.
 %
@@
 Reference 13 includes some description of the fabrication steps, mainly to depict the more generic pleated fabrication process.
-The process described in that paper is not complete to allow the reader to reproduce this particular manipulation system.
-We added further clarification to the text.
-We also fixed the Table 1 formatting.
+The process described in that paper is not complete to allow the reader to reproduce a controllable manipulation system.
+We added further clarification to the text, removed unnecessary fabrication portions and set the focus on what is new.
+We removed Table 1.
 %
@@
 \textit{Section 4.2 par 1., Which motion tracker was used?}
-We used the commercially available The OptiTrack Flex 3 System by Natural Point, Inc. We revised the text to add this information.
+We used the commercially available The OptiTrack Flex 3 System by Natural Point, Inc. We revised the text in the experimental section to add this information.
 %
@@
 All parameters are introduced as inputs to the algorithm.
-We revised the manuscript to clarify this point and make it easier to find the optimization equation.
+We revised the manuscript to clarify this point and make it easier to find the optimization equation within the algorithm environment.
 %
@@
 We thank the reviewer for this comment.
-We revised the exposition within the "existing procedures section" to highlight the differences between the two approaches.
+In section 4, we revised the exposition to highlight the differences between the two approaches.
 The algorithm in \cite{marchese2014whole} is about planning the motion of a soft arm without a gripper through a maze at a centerline while taking the arms bulging shape as a trapezoidal into account.
@@
 %
-We added to the manuscript: "The optimization only becomes over-constrained if it has to find an arm pose outside of the arm's reachable workspace.
+The optimization only becomes over-constrained if it has to find an arm pose outside of the arm's reachable workspace.
 That occurs if the object was user-placed outside the workspace.
-Before performing the optimization, a feasability check is performed using the arm's forward kinematics."
+Before performing the optimization, a feasibility check is performed using the arm's forward kinematics.
 %
@@
 The solver takes about 1\unit{s} on a regular PC to solve for all waypoints from start to finish.
-We included this information in the paper.
+We included this information in abbreviated form in the manuscript.
 %
@@
 The way the algorithmic environment was set up in this document, it is not trivial to add line numbering to it.
-Instead we clarified the description of the algorithmic steps within the manuscript better, it should not require the line numbers anymore.
+Instead we clarified the description of the algorithmic steps within the manuscript better, it should not require line numbers now to understand the exposition.
 %
@@
 %
-The object has a weight of 18\unit{g} and a diameter of 3.3\unit{cm}. We added this info to the manuscript.
+The object has a weight of 18\unit{g} and a diameter of 3.3\unit{cm}.
 %
@@
 %
-Thank you for your comments, we added these references to the introduction section of the paper.
+Thank you for your comments, we added the appropriate references to the introduction section of the paper.
 %
@@
 %
-Thank you for this observation, we added the missing details to the paper.
-We rewrote the Grasping delicate objects section to provide more detail on what delicate objects have been successfully grasped, pointing out that the egg is just one example.
-We also describe how blocking force and pressures have been analyzed for the gripper and how the small range .
+Thank you for this observation, we did not intend to draw focus on the delicate object manipulation and therefore changed that part of the experiments section to provide more details on what kind of objects have been successfully grasped.
+The egg is just one example.
 %
@@
 %
-Figure 3’s point 1 and c were modified according to your suggestion and more descriptive notes were added to the fabrication figure and the description in the paper.
+Thank you for this comment.
+We adjusted the contributions section accordingly, refer to citations where necessary and shortened the hardware design/fabrication section to focus on what is new and what were challenges for the 7 dof design and fabrication.
 %
@@
 %
-We revised the exposition to clarify this point. We added to the Lost Wax Fabrication section theses sentences:
-"The retractable pin fabrication for uniform lateral channels, first introduced in reference [12], does not cause weakening seams to the actuator, but it also does not allow for cavities more complicated than cylindrical shapes.
-This is why we propose the application of lost-wax casting to the fabrication of soft fluidic actuators like a gripper."
-Later in the multi-segment arm section, we also added:
-"The cylindrical segments of the arm are fabricated through a retractable pin fabrication technique, which does not require lost wax cores because of their simple cylindrical cavities."
+We revised the exposition to clarify this point.
+The retractable pin fabrication for uniform lateral channels, first introduced in reference [12], does not cause weakening seams to the actuator, but it also does not allow for cavities more complicated than cylindrical shapes.
+This is why we propose the application of lost-wax casting to the fabrication of soft fluidic actuators like a gripper.
+The cylindrical segments of the arm are fabricated through a retractable pin fabrication technique, which does not require lost wax cores because of their simple cylindrical cavities.
 %
@@
 We added:
-"It is worth mentioning that the exteroceptive tracking system has the disadvantage that a full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment.
+"The exteroceptive tracking system has the disadvantage that a full occlusion of one or more markers can cause the tracking system to temporarily loose track of a measured arm segment.
 In that case, the control loop can not function properly until the occlusion disappears.
@@
 %
-Thank you for this observation. The focus of the paper is planar manipulation. Scaling to a 3-dimensional task is not considered in this paper. Our current work will consider the 3D case.
-We revised the text to clarify this point, we added in the multi-segment arm section: 
-"As was shown in [13] through the characterization of various actuator morphologies, the concatenation of soft cylindrical segments is most suitable to build up a robot arm that can create high blocking forces per fluid energy inserted."
-We also added to the same section:
-"Using six segments, the $\pm 60^\circ$ joint limit does not prohibit the robot to reach its own base.
-Calculating the forward kinematics, see \texttt{forwKin()} procedure in Algorithm 1, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl."
+Thank you for this observation. The focus of the paper is planar manipulation. Scaling to a 3-dimensional task is not considered in this paper. Our future work will consider the 3D case.
+We revised the text to clarify this point.
+As was shown in [13] through the characterization of various actuator morphologies, the concatenation of soft cylindrical segments is most suitable to build up a robot arm that can create high blocking forces per fluid energy inserted.
+Using six segments, the $\pm 60^\circ$ joint limit does not prohibit the robot to reach its own base.
+Calculating the forward kinematics, see \texttt{forwKin()} procedure in Algorithm 1, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl.
 %
@@
 %
-Thank you for this comment, we added to the multi segment arm section:
-"The complete multi-segment arm is supported off the ground with two roller supports per segment. 
+Thank you for this comment. The complete multi-segment arm is supported off the ground with two roller supports per segment. 
 The rollers minimize frictional forces to the surface. 
-If the arm would be moved over a non-slippery surface without rollers, the frictional effects would greatly reduce the agility of the arm and largely increase the stick-slip friction effects with the ground, rendering the arm less useful."
+If the arm would be moved over a non-slippery surface without rollers, the frictional effects would greatly reduce the agility of the arm and largely increase the stick-slip friction effects with the ground, rendering the arm less useful.
 %
@@
 %
-Replaced by: "Demonstrating that soft robots allow for proper autonomous manipulation of delicate objects without requiring force sensing or accurate positioning."
+We changed the sentence.
 %
@@
 %
-Replaced by: "Fabrication techniques based on the lamination of several cast rubber pieces lead to more manufacturing inconsistencies due to slight misalignments of layers. 
-We observed that soft actuators built this way tend to rupture more easily at their weakening seams."
+We fixed this sentence.
 %
@@
 %
-Replaced by: " The user's placing accuracy is not important to the algorithm, since the tracking system newly registers the position of the object every time it is placed."
+Sentence was changed.
 %
@@
 %
-We adjusted the formatting accordingly.
+We ended uo removing the table completely since it was not providing necessary information to bring across the key message of the paper.
 %
@@
 %
-$\kappa_{off}$  is now better defined by: "measured manipulator configuration at start". We also clarified the meaning of the \emph{green} circles in the text.
+$\kappa_{off}$  is now better defined by: "measured manipulator configuration at start". We also clarified the meaning of the circles in the text.
 %
@@
 %
-To address this question, we added to the "Experimental Insights and Limitations section" this sentence: 
 The amount of intermediate waypoints is determined by the variable $\Delta d$, which we found empirically to be 5\unit{cm}, around half the length of the gripper.
@@
 %
-We consider the object to have settled if it has not moved for 2\unit{s}. We added this sentence to the manuscript.
+We consider the object to have settled if it has not moved for 2\unit{s}.
 %
@@
 %
-Picking up eggs is just as one example for a delicate manipulation the gripper actually performed. We revised the text to make this clear:
-The soft manipulator picks up delicate objects such as eggs, shuttlecocks or bakery items without squishing or breaking those. 
-We also addressed the point of the gripping forces by adding:
+Picking up eggs is just as one example for a delicate manipulation the gripper actually performed.
+The soft manipulator picks up delicate and normal objects such as eggs, shuttlecocks or bakery items, tape rollers without squishing or breaking those.
+Regarding the gripping forces:
 It was shown in \cite{marchese2015recipe} that pleated grippers of similar dimensions like the one used in this work can exert a continuous spectrum of blocking force in the range of 0-2\unit{N} at a pressure range of 0-60\unit{kPa}.
@@
 The grid paper and fine markings on all four sides of the round object ensure that the placement by the user is accurate within $\pm$1\unit{mm} in relation to the discrete placement locations.
-This test serves as a qualitative measure to show a relation between object size to gripper size to area of successful grasp..
-We added this explanation to the manuscript.
+This test serves as a qualitative measure to show a relation between object size to gripper size to area of successful grasp.
 %
@@
 %
-We added an explanation in the "Repeated Grasp Experiments" section: For these experiments, we focus on showing the capability of picking up objects at various places and moving them around, there is no emphasis set on having to drop off the object at a specific pose.
+We added an explanation in the "Grasp Experiments" section: For these experiments, we focus on showing the capability of picking up objects at various places and moving them around, there is no emphasis set on having to drop off the object at a specific pose.
 To indicate that the arm can move the object after grasping, the arm was controlled to go back to the fully straight pose.
@@
 %
-We revised the manuscript to provide more detail.
-Specifically, a smoothing of the complete trajectory with several intermediate waypoints was found to be necessary.
+A smoothing of the complete trajectory with several intermediate waypoints was found to be necessary.
 The amount of intermediate waypoints is determined by the variable $\delta d$, which we found empirically to be 5\unit{cm}, around half the length of the gripper.

### 2015-11-09 system_overview.tex
soro review

@@
 \section{System Overview}
-The soft grasping manipulator shown in Figure \ref{fig:egg_approach_sequence} has six bidirectional segments with cylindrical cavities forming the arm and a single soft gripper with a pleated shape (Figure~\ref{fig:design}) as the end effector.
+\rkk{The soft grasping manipulator shown in Figure \ref{fig:egg_approach_sequence} has six bidirectional segments with cylindrical cavities forming the arm and a single soft gripper with a pleated shape (Figure~\ref{fig:design}) as the end effector.
 The independent pneumatic actuation of the unidirectional soft gripper and each bidirectional arm segment, is achieved through an array of 13 custom fluidic drive cylinders \cite{marchese2014design}.
@@
 The motion planning algorithm as well as the curvature controller run on the control computers and take the location information as input.
-The curvature controller then provides continuous closed-loop adjustment of the fluidic drive cylinder array.
+The curvature controller then provides continuous closed-loop adjustment of the fluidic drive cylinder array.}
 

### 2018-04-08 experimental_results.tex
blacn and white

@@
 \subsection{Experimental Platform}
-The \dr{soft manipulation} system is shown in Figure~\ref{fig:experimental_platform}.
+The \dr{soft manipulation} system we developed for this work is shown in Figure~\ref{fig:experimental_platform}.
 %The planar six segment soft rubber manipulator consists of twelve distributed elastomer actuators. This manipulator moves with minimal friction on a level plane.
@@
 \begin{centering}
-  \includegraphics[width=2.0in]{Figures/system_overview/sys_overview_smaller}\\
+  \includegraphics[width=2.0in]{Figures/system_overview/sys_overview_smaller_bw.jpg}\\
   \caption{System Overview.
-The system is composed of (\textbf{A}) a motion capture system, (\textbf{B}) rigid frame, (\textbf{C}) soft six segment planar manipulator, (\textbf{D}) an object within the grasp envelope, (\textbf{E}) a soft gripper fixed to the manipulator, (\textbf{F}) a fluidic drive cylinder array to control actuation, and (\textbf{F}) computers for real-time processing and control.} \label{fig:experimental_platform}
+The system is composed of (\textbf{A}) a motion capture system, (\textbf{B}) rigid frame, (\textbf{C}) soft six segment planar manipulator, (\textbf{D}) an object within the grasp envelope, (\textbf{E}) a soft gripper fixed to the manipulator, (\textbf{F}) a fluidic drive cylinder array to control actuation, and (\textbf{G}) computers for real-time processing and control.} \label{fig:experimental_platform}
 \end{centering}
@@
 \centering
-   \includegraphics[width=0.8\columnwidth]{Figures/experimental_results/uncertainty}
-   \caption{Experimental characterization of the gripper's capture region: the allowable positioning uncertainty is determined through repeated placements of the center of a cylindrical object at different points on a grid relative to the gripper.
+   \includegraphics[width=0.8\columnwidth]{Figures/experimental_results/uncertainty_bw}
+   \caption{Experimental characterization of the gripper's capture region: the allowable positioning uncertainty is determined through repeated placements of the center of a cylindrical object at different points on a 5\unit{mm} grid relative to the gripper.
 Blue dots indicate all object center positions for which a grasp could be performed successfully, red crosses show the positions where a grasp failed.
@@
 Specifically,}
-we performed over 200 experimental grasp-and-place trials at various positions to demonstrate the capabilities and repeatability of our system.
-We picked up various objects such as eggs, shuttlecocks, bakery items, cups, light bulbs, and tape holders. 
+we performed over 200 experimental grasp-and-place trials at randomly chosen positions within the reachable workspace to demonstrate the capabilities and repeatability of our system.
+We successfully picked up various objects such as eggs, shuttlecocks, bakery items, cups, light bulbs, and tape holders. 
 The objects had an enclosing diameter in the range of 2-5\unit{cm}. 
@@
 The markers only serve as a reference point for the user to place the object roughly at the same point at every repetition.
-The user's placing accuracy is not important to the algorithm, \rkk{since the tracking system newly registers the position of the object every time it is placed.}
+The user's placing accuracy is not important to the algorithm, \rkk{since the tracking system re-registers the position of the object every time it is placed.}
 The five points were chosen to approximately represent the major portion of the manipulator's reachable workspace.
 As long as the root of the gripper stops so that the object is located within the capture region, the gripper will pick it up through its sweeping closing motion.
-The capture region is shown in grey in Figure~\ref{fig:grasp_uncertainty}.
+The capture region is outlined in grey in Figure~\ref{fig:grasp_uncertainty}.
 
@@
 This test serves as a qualitative measure to show qualitatively a relation between object size to gripper size to area of successful grasp.}
-\rkk{This characterization was repeated two times, resulting always in the same capture region.}
+\rkk{This characterization was repeated two times, resulting in nearly identical capture regions.}
 Despite positioning inaccuracies of the soft manipulator, the gripper can nevertheless successfully perform a grasp of an object. 
+\rkk{The successful capture region can be characterized by about half a gripper length in diameter.}
 
 When the arm reaches \rkk{its straight pose within a relatively large delta}, it drops the object.
-\rkk{For these experiments, we focus on showing the capability of picking up objects at various places and moving them around, there is no emphasis set on having to drop off the object at a specific pose.
+\rkk{For these experiments, we focus on showing the capability of picking up objects at various places and moving them around, there is no emphasis set on having to drop off the object at a specific place.
 To indicate that the arm can move the object after grasping, the arm was controlled to go back to the fully straight pose.
-When it got fairly close to that final straight pose within a large allowable delta, the gripper was set to release and drop the object.
+When the arm reached the final straight pose within a 1\unit{cm} delta, the gripper was set to release and drop the object.
 It was not ensured by the planner that the arm had to first settle to zero velocity at the final straight pose.
@@
 \includegraphics[width=0.385\textwidth]{figures/experimental_results/five_grasps.jpg}
-\caption[Left: All 25 experimental grasping trials.]{Complete set of experimental grasp-and-place trials.
+\caption[Left: All 25 experimental grasping trials.]{Left: Complete set of experimental grasp-and-place trials.
 In these experiments, the arm moves from an initial straightened configuration to grasp a round object placed in one of five locations (A-E).
@@
 For each trial, a seven degrees of freedom manipulator representation is generated at both the \emph{grasped} and \emph{released} state using experimental data and is shown in blue.
-The corresponding 1 degree-of-freedom end-effector representation is shown in black.
+The corresponding 1 DOF end-effector representation is shown in black.
 The round object's measured position at each state is shown in green.
+In one of the trials, the grasp and return was successfully performed, but an overshoot over the final bin location caused the gripper to drop off the small table it is moving on.
 Right: Overlaid photographs of the manipulator grasping an object placed at each of the five locations.
@@
 %The controller then tried to swing back to fulfill the missed waypoint, missed it again and that finally caused the whole arm to oscillate back-and-forth and eventually push the object off the table.
-In one of the trials shown in Figure~\ref{fig:allTestsOverlaid}, the grasp and return was successfully performed, but an overshoot over the final bin location caused the arm to drop off the relatively small table.
 %, which could have been avoided if the table would have not been too small towards the right.
@@
 
-\rkk{We developed an end-to-end system that can approximately locate an object placed at an a priori unknown location and move it somewhere else.
+\rkk{We developed an end-to-end system that can approximately locate an object placed at an a priori unknown location and move it to a desired location.
 The external localization system is a convenient way to approximately identify the location of the object and to track how the object is moved around.
@@
 \includegraphics[width=0.31\textwidth]{figures/experimental_results/exp5a-4_sweep_to_bin.jpg}
-  \caption{Left: A time series representation of an experimental grasp-and-place trial for an object located at point E.
+  \caption{Left: A time series representation of an experimental grasp-and-place trial for an object located at point E (Figure~\ref{fig:allTestsOverlaid}).
 Here, the locally optimal planned manipulator configurations as well as planned sequential approach circles are shown as black dotted curves.
@@
 The cyan configurations represent the manipulator prior to grasping the object, that is moving from its initial configuration to the object's location.
-\rkk{Depending on where the object is placed, the arm takes between 17-35\unit{s} to approach it.} The magenta configurations represent the manipulator after grasping the object, that is moving from the object's location back to the bin location shown in red.
-\rkk{This task of moving back to the bin takes between 10-20\unit{s}.} Right: A photograph of the arm moving from its initial pose to the object and from the object to the release location, respectively.}
+\rkk{Depending on where the object is placed, the manipulator takes between 17-35\unit{s} to approach it.} After grasping the object, the magenta configurations represent the manipulator moving from the object's location back to the bin location shown in red.
+\rkk{This task of moving back to the bin takes between 10-20\unit{s}.} Right: Overlaid photographs of the manipulator moving from its initial pose to the object and from the object to the release location, respectively.}
 \label{fig:oneTrialVsTime}
@@
 \rkk{The experiments were performed for picking up objects on the left quadrant of the manipulator.
-Grasping objects on both sides of the manipulator could be achieved in various ways by 
+Grasping objects on both sides of the manipulator could be achieved in various ways including 
 \begin{enumerate}

### 2018-04-08 robotic_gripper.tex
blacn and white

@@
 %Following this, 
-We briefly describe the design, fabrication and functionality of this soft grasping manipulator. Further details on the design and fabrication can be found in \cite{marchese2015recipe}.
+We briefly describe the design, fabrication and functionality of this soft grasping manipulator in this paper. Further details on the design and fabrication can be found in \cite{marchese2015recipe}.
 
@@
 \centering
-   \includegraphics[width=0.99\columnwidth]{figures/robotic_gripper/design_gripper.eps}
+   \includegraphics[width=0.99\columnwidth]{figures/robotic_gripper/design_gripper_detailed_bw.eps}
    \caption{The pleated channel designs.
+The design consists of a channel inlet (a), an almost inextensible constraint layer (b), uniform pleats (d) separated by even gaps (c), and internal channels within each pleat (e).
 (\textbf{A}) depicts the segment in an unactuated state and (\textbf{B}) shows the segment in an actuated and therefore bent state.
@@
 \subsection{Lost Wax Fabrication for Fluidic Elastomer Actuators}
-Existing soft fluidic manipulators are mostly produced through a multi-step lamination process called soft lithography, which results in weakening seams that can easily delaminate. 
+Existing soft fluidic manipulators are mostly produced through a multi-step lamination process called \emph{soft lithography}, which results in weakening seams that can easily delaminate. 
 This limits their range of applications and lifetime.
-\rkk{The retractable pin fabrication for uniform lateral channels, first introduced in \cite{marchese2014whole}, does not cause weakening seams to the actuator, but it also does not allow for cavities more complicated than cylindrical shapes.}
+\rkk{The retractable pin fabrication for uniform lateral channels, first introduced in \cite{marchese2014whole},
+limits the complexity of the cavities to cylindrical shapes but does not cause weakening seams to the actuator.}
+%does not cause weakening seams to the actuator, but it also does not allow for cavities more complicated than cylindrical shapes.}
 This is why the application of lost-wax casting to the fabrication of soft fluidic actuators like a gripper is advantageous.
-The actuated cavities of the soft gripper are achieved by using a wax core, pourable silicone rubber and 3D printed molds.
-The gripper fabrication process and the tools needed are fully described and depicted in Section~4.3.
-and Figure~14 of the recipes paper for soft fluidic elastomer actuators \cite{marchese2015recipe}.
-%Figure~\ref{fig:fabrication}.
+The actuated cavities of the soft gripper are achieved using a wax core, pourable silicone rubber and 3D printed molds.
+The gripper fabrication process and the tools needed are fully described and depicted in Section~4.3. and Figure~14 in \cite{marchese2015recipe}. %Figure~\ref{fig:fabrication}.
 %The tools and equipment used are also listed in Table~\ref{tab:MachineTools} and are referred to by superscripts.
@@
 
-The design for the arm consisting of soft cylindrical segments was described in \cite{marchese2014whole}.
-\rkk{As was shown in \cite{marchese2015recipe} through the characterization of various actuator morphologies, the concatenation of soft cylindrical segments is most suitable to build up a robotic arm that can create high blocking forces per fluid energy inserted.}
- \rkk{The cylindrical segments of the arm are fabricated through a retractable pin fabrication technique, which does not require lost wax cores because of their simple cylindrical cavities.} 
-Each cylindrical segment can only be actuated up to a bend angle of about $60^\circ$, therefore several segments have to be combined together to allow the arm to reach a large enough workspace to perform proper manipulation tasks on a plane.
-\rkk{Using six segments, the joint limits do not prohibit the robot to reach with its tip its own root.} %Calculating the forward kinematics, see \texttt{forwKin()} in Algorithm~\ref{alg:planGrasp}, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl.}
+The design for the arm consisting of soft cylindrical segments is described in \cite{marchese2014whole}.
+\rkk{As is shown in \cite{marchese2015recipe} through the characterization of various actuator morphologies, the concatenation of soft cylindrical segments is most suitable to build up a robotic arm that can create high blocking forces per fluid energy inserted.}
+ \rkk{The cylindrical segments of the arm are fabricated through a retractable pin fabrication technique \cite{marchese2014whole}, which does not require lost wax cores because of their simple cylindrical cavities.}
+Each cylindrical segment can be actuated up to a bend angle of about $60^\circ$, this requires several segments to be combined together to allow the arm to reach a large enough workspace to perform proper manipulation tasks on a plane.
+\rkk{Using six segments, the robot is able to touch its tip to its base without interference from the individual joint limits.}
+%the joint limits do not prohibit the robot to reach with its tip its own root.} %Calculating the forward kinematics, see \texttt{forwKin()} in Algorithm~\ref{alg:planGrasp}, for the 6 DOF arm with a segment length of 6.27\unit{cm} and an extreme curvature of $\kappa = \frac{60/180 \pi}{0.0627\unit{m}} = 16.7\frac{1}{\unit{m}}$ shows that the tip of the robot can reach its root at a full curl.}
 The cylindrical segment design with its hollow channel in the center has enough space to accommodate for pneumatic tubes to connect to all six cylindrical segments and additionally to the pleated gripper, which is attached to the tip.

### 2018-04-08 SoRo reviewer comments/2darmgripper source file resubmission/abstract.tex
submission files

--- 2015-10-15 abstract.tex
@@
 This paper presents the development of an autonomous motion planning algorithm for a soft planar grasping manipulator capable of grasp-and-place operations by encapsulation
-\dr{under uncertainty in the position and shape of the object.}
-The gripping end of the soft manipulator is fabricated without weakening seams using lost-wax casting instead of the commonly used multi-layer lamination process.
+with uncertainty in the position and shape of the object.
+The end effector of the soft manipulator is fabricated in one piece without weakening seams using lost-wax casting instead of the commonly used multi-layer lamination process.
 The soft manipulation system can grasp randomly positioned objects within its reachable envelope and move them to a desired location without human intervention.
